### 2020-10-22 Paper/main.tex
More paper stuff

\documentclass[conf]{new-aiaa}
%\documentclass[journal]{new-aiaa} for journal papers
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\setlength\LTleft{0pt}

\title{Computation and comparison of the stable Northeastern US marine boundary layer}

\author{Lawrence C. Cheung\footnote{Principal member of technical staff, Thermal/Fluid Science \& Engineering, AIAA member}}
\affil{Sandia National Laboratories, Livermore, CA 94550}

\author{
  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Matthew J. Churchfield\footnote{SOME JOB TITLE, AIAA Member}, \\
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
  Shashank Yellapantula\footnote{SOME JOB TITLE, AIAA Member}
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

\author{Nathaniel B. deVelder\footnote{Postdoctoral appointee, AIAA member} and
  Alan S. Hsieh.\footnote{Postdoctoral appointee, Wind Energy Technologies Department, AIAA member}}
\affil{Sandia National Laboratories, Albuquerque, NM 87185}

\begin{document}

\maketitle

\begin{abstract}
Put abstract here
\end{abstract}

\section{Nomenclature}

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$\alpha$  & Wind shear exponent  \\
$L$       & Obukhov length scale \\
$u_\tau$   & Friction velocity    \\
$TI$      & Turbulence intensity 
\end{longtable*}}

\section{Introduction}
\lettrine{P}{ut} the introduction here.

The planned installation of several offshore wind energy plants in the
United States has highlighted the need to properly understand the wind
resource and atmospheric characteristics of the US Atlantic Coast.
Several atmospheric phenomena particular to this region, such as
coastal low-level jets or seasonal Nor’easters, have the potential to
substantially impact the operation and power production of offshore
wind plants.  Of particular interest to the current study is the
atmospheric stability of the marine boundary layer in the Northeastern
US.

Atmospheric stability plays a large role in determining the power
production of wind plants because it directly affects the vertical
distribution of momentum and turbulent energy in the atmospheric
boundary layer (ABL).  The differences between the stable, neutral, or
unstable stratified ABL can lead to large changes in wind speed or
turbulence profiles, and ultimately change the operation of wind
turbines.  Atmospheric stability may also play a role in the formation
of low-level jets \cite{nunalee2014mesoscale} and cause increased
fatigue loads on offshore wind turbines.

Several recent measurement campaigns have provided data to understand
the ABL and wind characteristics for potential offshore wind farms in
the Northeastern US.  Pichugina et al. \cite{pichugina2017properties}
measured the wind profiles and vertical shear profiles in the Gulf of
Maine using a ship-borne lidar approach.  Analysis of measured data
sets from Nantucket Sound by Archer et
al. \cite{archer2016predominance} showed a predominance of low-shear,
unstable conditions at the site.  However, strong seasonal variations
and stratification changes due to diurnal variation were also
observed.

In addition to these measurements, large eddy simulations (LES) have
also been used to study ABL stability characteristics.  Recent work by
Kaul et al. \cite{kaul2020large} has shown that LES computations using
Nalu-Wind can capture the neutrally and convectively unstable onshore
ABL.  Previous simulations by Cheung et al. \cite{cheung2020large}
successfully replicated the unstable and neutral ABL corresponding to
the Cape Wind meteorological tower measurements
\cite{archer2016predominance} and showed the effects of surface
heating on atmospheric stratification.  Additional LES computations
\cite{sullivan2016turbulent} have also previously explored stable
conditions of onshore boundary layers, such as the GABLS1 boundary
layer \cite{beare2006intercomparison}.  However, a complete comparison
including offshore stable ABL conditions has yet to be completed.

\section{Methodology}
Write something about Nalu-Wind and AMR-Wind.

\section{Results}
Write something about Nalu-Wind and AMR-Wind.

\section{Conclusion}
Put conclusion here.

\section*{Appendix}

An Appendix, if needed, should appear before the acknowledgments.

\section*{Acknowledgments}
This research was supported by the Wind Energy Technologies Office of
the US Department of Energy Office of Energy Efficiency and Renewable
Energy.  Sandia National Laboratories is a multimission laboratory
managed and operated by National Technology \& Engineering Solutions
of Sandia, LLC, a wholly owned subsidiary of Honeywell International
Inc., for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-NA0003525. The views expressed in the
article do not necessarily represent the views of the U.S. Department
of Energy or the United States Government.

% \bibliography{sample}
\bibliography{references}

\end{document}

### 2020-10-24 Paper/methodology.tex
Added paper files

\section{Methodology}
Write something about what we're comparing with, the codes we're
using, and how we set up the simulations.

\subsection{Measured offshore conditions}
\fxnote{Lawrence write this part}

Write something about Cape Wind measurements from \cite{archer2016predominance}.

\subsection{LES Codes}
Provide a general description of the LES codes that we use.

\subsubsection{Nalu-Wind}
Describe Nalu-Wind

\subsubsection{AMR-Wind}
\fxnote{Mike write this part}\\
Describe AMR-Wind

\subsection{Computational set up}
\fxnote{Lawrence write this part}\\
Domains, grids, boundary conditions

\subsubsection{Lower wall model BC}
\fxnote{Ganesh write this part}\\
What we implemented in terms of the lower boundary condition.

\subsubsection{Simulation workflow}
Describe the process to hit target conditions.

### 2020-10-24 Paper/results.tex
Added paper files

\section{Results}
\fxnote{This should be a collaborative section}

\subsection{ABL integrated quantities}
Describe integrated quantities

\subsection{Horizontally averaged profiles}

\subsection{Wind spectra and turbulence statistics}

### 2020-10-26 Postprocessing/utilities/load_alldata.py
Added both AMR fine and coarse comparisons

@@ -156,8 +156,8 @@ class AMRWindStats(ABLStats):
 
 class AMRWind2Stats(ABLStats):
   """ABLStats class specific to AMRWind output using netcdf"""
-  def __init__(self,dir_name):
-    a = pd.read_csv(dir_name+'/line_average_data.csv')
+  def __init__(self,dir_name, lineavgfilename='line_average_data.csv'):
+    a = pd.read_csv(dir_name+'/'+lineavgfilename)
     self.z = a['z'].values
     self.u = a['u'].values
     self.v = a['v'].values

### 2020-10-30 Paper/main.tex
Added paper files
Update paper stuff

@@
 \usepackage{longtable,tabularx}
+\usepackage{fixme}
 \setlength\LTleft{0pt}
+
+% Setup fixme env for collaborative notes
+\fxsetup{status=draft, layout=inline, theme=color}
 
@@
   Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
-  Matthew J. Churchfield\footnote{SOME JOB TITLE, AIAA Member}, \\
   Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
@@
 \section{Introduction}
+\fxnote{This is the introduction from the abstract.  Update with real
+  introduction.}
+
 \lettrine{P}{ut} the introduction here.
@@
 
-\section{Methodology}
-Write something about Nalu-Wind and AMR-Wind.
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% SECTION 2: METHODOLOGY
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{methodology}
 
-\section{Results}
-Write something about Nalu-Wind and AMR-Wind.
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% SECTION 3: RESULTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{results}
 
@@
 \section*{Acknowledgments}
+\fxnote{Acknowledge Matt for work on BC}
+
 This research was supported by the Wind Energy Technologies Office of
@@
 
+\fxnote{ADD ANY NREL ACKNOWLEDGEMENTS NECESSARY HERE}
+
 % \bibliography{sample}

### 2020-11-02 Postprocessing/utilities/NaluWindAvg.py
Added results and comparison for Nalu-Wind neutral 05ms_iter07.fine

@@ -37,9 +37,10 @@ runlist=[
     #['stable 15m/s', 'stable/15ms/15ms_iter01',     [15000, 20000],  'abl_stable15ms_iter01_run1.yaml', {'ablfile':'abl_statistics.nc','color':'b', 'lw':2, 'pngimage':'HHplane_0014000_0_plane0.png'}],
     #['stable 15m/s', 'stable/15ms/15ms_iter02',     [15000, 20000],  'abl_stable15ms_iter02_run1.yaml', {'ablfile':'abl_statistics.nc','color':'b', 'lw':2, 'pngimage':'HHplane_0014000_0_plane0.png'}],
     #['stable  5m/s', 'stable/05ms/05ms_iter02',     [15000, 20000],  'abl_stable05ms_iter02_run1.yaml', {'ablfile':'abl_statistics.nc','color':'b', 'lw':2, 'pngimage':'HHplane_0014000_0_plane0.png'}],
-    ['stable  5m/s', 'stable/05ms/05ms_iter02',     [10000, 15000],  'abl_stable05ms_iter02_run1.yaml', {'ablfile':'abl_statistics.nc','color':'b', 'lw':2, 'savedir':'../../NaluWindRuns/stable/05ms/05ms_iter02/10k_15k'}],
+    #['stable  5m/s', 'stable/05ms/05ms_iter02',     [10000, 15000],  'abl_stable05ms_iter02_run1.yaml', {'ablfile':'abl_statistics.nc','color':'b', 'lw':2, 'savedir':'../../NaluWindRuns/stable/05ms/05ms_iter02/10k_15k'}],
     
-   # # -- Neutral runs --
+    # -- Neutral runs --
+    ['neutral 5m/s',  'neutral/05ms/mini05_iter07.fine',  [15000, 20000], 'abl_neut05ms_iter07_run1.yaml', {'ablfile':'abl_statistics.nc', 'color':'g', 'lstyle':'-', 'lw':2.5, 'savedir':'../../NaluWindRuns/neutral/05ms/05ms_iter07.fine'}],
    # ['neutral 5m/s',  'neutral/05ms/05ms_iter07',  [15000, 20000], 'abl_neut05ms_iter07_run1.yaml', {'ablfile':'abl_statistics.nc', 'color':'g', 'lstyle':'-', 'lw':2.5, 'pngimage':'HHplane_0030000_0_plane0.png'}],
[…]

### 2020-11-02 Postprocessing/utilities/load_alldata.py

@@ -173,7 +173,10 @@ class AMRWind2Stats(ABLStats):
       "<w'w'>" : a["w'w'_r"],
       "<w'w'w'>": a["w'w'w'_r"]
     }
-    self.istats = yaml.load(open(dir_name+'/istats.yaml'),Loader=yaml.BaseLoader)
+    try:
+      self.istats = yaml.load(open(dir_name+'/istats.yaml'),Loader=yaml.BaseLoader)
+    except:
+      self.istats = {}
     if (len(glob.glob(dir_name+'/avg_spectra.nc'))>0):
       with Dataset(dir_name+'/avg_spectra.nc') as d:
         self.ps_data = {

### 2020-11-24 AMRWindRuns/stable/05ms/sim_dx2.5/average.py
added line average data to all amrwind stable cases

@@ -1,0 +1,91 @@
+import matplotlib 
+matplotlib.use('Agg')
+import itertools, windspectra, postproamrwind, glob, yaml
+import pandas as pd
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+import numpy as np
+from mpi4py import MPI
+from netCDF4 import Dataset
+from multiprocessing import Pool
+
+
+def calc_average_profile_last_hour():
+  a = Dataset(sorted(glob.glob('post_processing/abl_statistics60000.nc'))[-1])
+  tstart_idx = np.searchsorted(a.variables['time'][:],15000.0)
+  tend_idx = np.searchsorted(a.variables['time'][:],20000.0)
+
+  print(tstart_idx)
+  mean_profiles = a.groups['mean_profiles']
+  vars = list(mean_profiles.variables)[1:]
+  b = pd.DataFrame({ v: np.average(mean_profiles[v][tstart_idx:tend_idx,:],axis=0) for v in vars})
+  b['z'] = mean_profiles['h'][:]
+  b.to_csv('line_average_data.csv')
+
+def calc_average_istats_last_hour():
+  a = Dataset(sorted(glob.glob('post_processing/abl_statistics60000.nc'))[-1])
+  vars = list(a.variables.keys())[1:]
+  tstart_idx = np.searchsorted(a.variables['time'][:],15000.0)
+  tend_idx = np.searchsorted(a.variables['time'][:],20000.0)
+  i_stats = { v: float(np.average( a.variables[v][tstart_idx:tend_idx])) for v in vars}
+  yaml.dump( i_stats, open('istats.yaml','w'), default_flow_style=False)
+
+  
+def calc_average_spectra_last_hour():
+  comm = MPI.COMM_WORLD
+  rank = comm.Get_rank()
+  nprocs = comm.Get_size()
+  
+  a = Dataset(sorted(glob.glob('post_processing/*nc'))[-1])
+  z = a.groups['l_v11'].variables['coordinates'][:100,2]
+  nz = np.size(z)
+  tttime = a.variables["time"][:]
+  start_idx = np.searchsorted(tttime, 15000)
+  time = tttime[start_idx:]
+  l_groups = ['l_v11','l_v12','l_v13','l_v21','l_v22','l_v23','l_v31','l_v32','l_v33']
+
+  #Figure out levels on which the current proc will operate
[…]

### 2020-11-24 AMRWindRuns/stable/10ms/sim_dx2.5/average.py

@@ -1,0 +1,91 @@
+import matplotlib 
+matplotlib.use('Agg')
+import itertools, windspectra, postproamrwind, glob, yaml
+import pandas as pd
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+import numpy as np
+from mpi4py import MPI
+from netCDF4 import Dataset
+from multiprocessing import Pool
+
+
+def calc_average_profile_last_hour():
+  a = Dataset(sorted(glob.glob('post_processing/abl_statistics120000.nc'))[-1])
+  tstart_idx = np.searchsorted(a.variables['time'][:],15000.0)
+  tend_idx = np.searchsorted(a.variables['time'][:],20000.0)
+
+  print(tstart_idx)
+  mean_profiles = a.groups['mean_profiles']
+  vars = list(mean_profiles.variables)[1:]
+  b = pd.DataFrame({ v: np.average(mean_profiles[v][tstart_idx:tend_idx,:],axis=0) for v in vars})
+  b['z'] = mean_profiles['h'][:]
+  b.to_csv('line_average_data.csv')
+
+def calc_average_istats_last_hour():
+  a = Dataset(sorted(glob.glob('post_processing/abl_statistics120000.nc'))[-1])
+  vars = list(a.variables.keys())[1:]
+  tstart_idx = np.searchsorted(a.variables['time'][:],15000.0)
+  tend_idx = np.searchsorted(a.variables['time'][:],20000.0)
+  i_stats = { v: float(np.average( a.variables[v][tstart_idx:tend_idx])) for v in vars}
+  yaml.dump( i_stats, open('istats.yaml','w'), default_flow_style=False)
+
+  
+def calc_average_spectra_last_hour():
+  comm = MPI.COMM_WORLD
+  rank = comm.Get_rank()
+  nprocs = comm.Get_size()
+  
+  a = Dataset(sorted(glob.glob('post_processing/*nc'))[-1])
+  z = a.groups['l_v11'].variables['coordinates'][:100,2]
+  nz = np.size(z)
+  tttime = a.variables["time"][:]
+  start_idx = np.searchsorted(tttime, 15000)
+  time = tttime[start_idx:]
+  l_groups = ['l_v11','l_v12','l_v13','l_v21','l_v22','l_v23','l_v31','l_v32','l_v33']
+
+  #Figure out levels on which the current proc will operate
[…]

### 2020-11-24 AMRWindRuns/stable/10ms/sim_dx2.5/windspectra.py

@@ -1,0 +1,175 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+import os
+
+# Defaults
+defaultwindow = {'choice':'tukey','alpha':0.1}
+uKaimalconst  = {'a':105.0, 'b':33.0, 'alphaExp':1.0,'betaExp':5.0/3.0}
+vKaimalconst  = {'a':17.0,  'b':9.5,  'alphaExp':1.0,'betaExp':5.0/3.0}
+wKaimalconst  = {'a':2.1,   'b':5.3,  'alphaExp':5.0/3.0,'betaExp':1.0}
+
+# The Tukey window
+# see https://en.wikipedia.org/wiki/Window_function#Tukey_window
+def tukeyWindow(N, params={'alpha':0.1}):
+    alpha = params['alpha']
+    w = np.zeros(N)
+    L = N+1
+    for n in range(0, int(N/2) + 1):
+        if ((0 <= n) and (n < 0.5*alpha*L)):
+            w[n] = 0.5*(1.0 - np.cos(2*np.pi*n/(alpha*L)))
+        elif ((0.5*alpha*L <= n) and (n <= N/2)):
+            w[n] = 1.0
+        else:
+            print("Something wrong happened at n = ",n)
+        if (n != 0): w[N-n] = w[n]
+    return w
+
+# FFT's a signal, returns 1-sided frequency and spectra (non-normalized)
+def getFFT(t, y):
+    n    = len(y)
+    k    = np.arange(n)
+    dt   = np.mean(np.diff(t))
+    frq  = k/(n*dt)
+    FFTy = np.fft.fft(y) # /(len(y))
+    
+    # Take the one sided version of it
+    freq = frq[range(int(n/2))]
+    FFTy = FFTy[range(int(n/2))]
+    return freq, FFTy
+
+# Takes a wind speed signal ws and returns the spectra
+#  Be sure to look at 
+#  https://www.nwpsaf.eu/publications/tech_reports/nwpsaf-kn-tr-008.pdf
+#  for normalization!
+def getWindSpectra(t, ws, window=defaultwindow):
+    N      = len(ws)
+    dt     = np.mean(np.diff(t))
+    # Get the window
+    if window['choice']=='tukey':    w = tukeyWindow(N, params=window)
+    else:                            w = 1 
+    # FFT to get the coefficients
[…]

### 2020-11-24 AMRWindRuns/stable/15ms/sim_dx2.5/average.py

@@ -1,0 +1,91 @@
+import matplotlib 
+matplotlib.use('Agg')
+import itertools, windspectra, postproamrwind, glob, yaml
+import pandas as pd
+from matplotlib.backends.backend_pdf import PdfPages
+import matplotlib.pyplot as plt
+import numpy as np
+from mpi4py import MPI
+from netCDF4 import Dataset
+from multiprocessing import Pool
+
+
+def calc_average_profile_last_hour():
+  a = Dataset(sorted(glob.glob('post_processing/abl_statistics240000.nc'))[-1])
+  tstart_idx = np.searchsorted(a.variables['time'][:],15000.0)
+  tend_idx = np.searchsorted(a.variables['time'][:],20000.0)
+
+  print(tstart_idx)
+  mean_profiles = a.groups['mean_profiles']
+  vars = list(mean_profiles.variables)[1:]
+  b = pd.DataFrame({ v: np.average(mean_profiles[v][tstart_idx:tend_idx,:],axis=0) for v in vars})
+  b['z'] = mean_profiles['h'][:]
+  b.to_csv('line_average_data.csv')
+
+def calc_average_istats_last_hour():
+  a = Dataset(sorted(glob.glob('post_processing/abl_statistics240000.nc'))[-1])
+  vars = list(a.variables.keys())[1:]
+  tstart_idx = np.searchsorted(a.variables['time'][:],15000.0)
+  tend_idx = np.searchsorted(a.variables['time'][:],20000.0)
+  i_stats = { v: float(np.average( a.variables[v][tstart_idx:tend_idx])) for v in vars}
+  yaml.dump( i_stats, open('istats.yaml','w'), default_flow_style=False)
+
+  
+def calc_average_spectra_last_hour():
+  comm = MPI.COMM_WORLD
+  rank = comm.Get_rank()
+  nprocs = comm.Get_size()
+  
+  a = Dataset(sorted(glob.glob('post_processing/*nc'))[-1])
+  z = a.groups['l_v11'].variables['coordinates'][:100,2]
+  nz = np.size(z)
+  tttime = a.variables["time"][:]
+  start_idx = np.searchsorted(tttime, 15000)
+  time = tttime[start_idx:]
+  l_groups = ['l_v11','l_v12','l_v13','l_v21','l_v22','l_v23','l_v31','l_v32','l_v33']
+
+  #Figure out levels on which the current proc will operate
[…]

### 2020-11-24 Postprocessing/utilities/correlate.py
update correlate.py and extractTimeSeries.py for netcdf files

@@ -13,27 +13,27 @@ try:
 except:
     netCDF4loaded = False
 
-def avgNCPlane(ncfilename, tindices, filename, verbose=False):
+def avgNCPlane(ncfilename, tindices, filename, group='p_f', verbose=False):
     """    
     Average the netcdf data over tindices and optionally save to file
     """
     if (not netCDF4loaded): Exception("netCDF4 not loaded") 
     ncdat  = Dataset(ncfilename, 'r')
 
-    allvx  = ncdat['p_h'].variables['velocityx']
-    allvy  = ncdat['p_h'].variables['velocityy']
-    allvz  = ncdat['p_h'].variables['velocityz']
-    allT   = ncdat['p_h'].variables['temperature']
+    allvx  = ncdat[group].variables['velocityx']
+    allvy  = ncdat[group].variables['velocityy']
+    allvz  = ncdat[group].variables['velocityz']
+    allT   = ncdat[group].variables['temperature']
         
     # Get coordinates
     # -- Zindex of all planes matching z --
-    #zind = (ncdat['p_h'].variables['coordinates'][:,2]==zplane)
-    allx = ncdat['p_h'].variables['coordinates'][:,0]
-    ally = ncdat['p_h'].variables['coordinates'][:,1]
-    allz = ncdat['p_h'].variables['coordinates'][:,2]
+    #zind = (ncdat[group].variables['coordinates'][:,2]==zplane)
+    allx = ncdat[group].variables['coordinates'][:,0]
+    ally = ncdat[group].variables['coordinates'][:,1]
+    allz = ncdat[group].variables['coordinates'][:,2]
     # -- Get the i,j indices ---
-    #ji=np.array([[j, i] for j in range(ncdat['p_h'].ijk_dims[1]) for i in range(ncdat['p_h'].ijk_dims[0])])
-    kji=np.array([[k, j, i] for k in range(ncdat['p_h'].ijk_dims[2]) for j in range(ncdat['p_h'].ijk_dims[1]) for i in range(ncdat['p_h'].ijk_dims[0])])
+    #ji=np.array([[j, i] for j in range(ncdat[group].ijk_dims[1]) for i in range(ncdat[group].ijk_dims[0])])
+    kji=np.array([[k, j, i] for k in range(ncdat[group].ijk_dims[2]) for j in range(ncdat[group].ijk_dims[1]) for i in range(ncdat[group].ijk_dims[0])])
     
     # Get the means 
[…]

### 2020-11-24 Postprocessing/utilities/extractTimeSeries.py

@@ -11,34 +11,54 @@ def findMatchingPt(ptlist, p, eps):
     # Error out
     raise Exception("error in findMatchingPt") 
         
-def writeTimeSeries(ncdat, xvec, yvec, zvec, savestring, verbose=True):
+def writeTimeSeries(ncdat, xvec, yvec, zvec, savestring, 
+                    group='p_h', useindices=False, verbose=True):
     """
     Average the spectra over multiple x, y, z locations
     """
-    Nt     = ncdat.dimensions['num_time_steps'].size
-    Npts   = ncdat['p_h'].dimensions['num_points'].size
-    allpts = ncdat['p_h'].variables['coordinates']
-    
+    #Nt     = ncdat.dimensions['num_time_steps'].size
+    Npts   = ncdat[group].dimensions['num_points'].size
+    allpts = ncdat[group].variables['coordinates']
+
     t      = ncdat['time'][:]
-    allvx  = ncdat['p_h'].variables['velocityx']
-    allvy  = ncdat['p_h'].variables['velocityy']
-    allvz  = ncdat['p_h'].variables['velocityz']
+    allvx  = ncdat[group].variables['velocityx']
+    allvy  = ncdat[group].variables['velocityy']
+    allvz  = ncdat[group].variables['velocityz']
     Navg   = 0
     zerocol = np.zeros(len(t))
     all_ulongavgs = []
     for x in xvec:
         for y in yvec:
             for z in zvec:
-                xyzpt = np.array([x,y,z])
-                ipt   = findMatchingPt(allpts, xyzpt, 1.0E-6)
+                if useindices:
+                    Nijk   = ncdat[group].ijk_dims
+                    Ni     = Nijk[0]
+                    Nj     = Nijk[1]
+                    ipt    = int(x) + int(y)*Ni + int(z)*Ni*Nj
+                    xyzpt = np.array([allpts[ipt, 0], 
+                                      allpts[ipt, 1], 
+                                      allpts[ipt, 2]])
+                    icol   = x*np.ones(len(t))
+                    jcol   = y*np.ones(len(t))
+                    kcol   = z*np.ones(len(t))
+                else:
+                    xyzpt = np.array([x,y,z])
+                    ipt   = findMatchingPt(allpts, xyzpt, 1.0E-6)
+                    icol  = zerocol
+                    jcol  = zerocol
+                    kcol  = zerocol
+
                 #print(allpts[ipt, :])
                 u = allvx[:,ipt]
[…]

### 2020-11-26 AMRWindRuns/stable/05ms/sim_dx2.5/pulltimeseries.sh
Update figures and postprocessing

@@ -1,12 +1,20 @@
 #!/bin/sh
 
-NCFILE=post_processing/sampling60000.nc
+#NCFILE=post_processing/sampling60000.nc
+NCFILE=post_processing_dx2.5/sampling60000.nc
+OUTFILE=spectra/HHplane_plane0/HHplane_%05.0f_%05.0f_%05.0f.dat
 
-#python extractTimeSeries.py $NCFILE -x `seq 0 100 900` -y `seq   0 100 200` -z 20 -o spectra/HHplane_plane0/HHplane_%05.0f_%05.0f_%05.0f.dat  &
-#python extractTimeSeries.py $NCFILE -x `seq 0 100 900` -y `seq 300 100 500` -z 20 -o spectra/HHplane_plane0/HHplane_%05.0f_%05.0f_%05.0f.dat  &
-#python extractTimeSeries.py $NCFILE -x `seq 0 100 900` -y `seq 600 100 900` -z 20 -o spectra/HHplane_plane0/HHplane_%05.0f_%05.0f_%05.0f.dat  &
+#python extractTimeSeries.py $NCFILE -x `seq 0 50 550` -y `seq   0  50 150` -z 0\
+# -i -g 'p_f' -o $OUTFILE  &
+#python extractTimeSeries.py $NCFILE -x `seq 0 50 550` -y `seq 200  50 350` -z 0\
+# -i -g 'p_f' -o $OUTFILE  &
+#python extractTimeSeries.py $NCFILE -x `seq 0 50 550` -y `seq 400  50 550` -z 0\
+# -i -g 'p_f' -o $OUTFILE  &
 
-python extractTimeSeries.py $NCFILE -x `seq 0 100 900` -y `seq   0 100 200` -z 40 -o spectra/HHplane_plane1/HHplane_%05.0f_%05.0f_%05.0f.dat  &
-python extractTimeSeries.py $NCFILE -x `seq 0 100 900` -y `seq 300 100 500` -z 40 -o spectra/HHplane_plane1/HHplane_%05.0f_%05.0f_%05.0f.dat  &
-python extractTimeSeries.py $NCFILE -x `seq 0 100 900` -y `seq 600 100 900` -z 40 -o spectra/HHplane_plane1/HHplane_%05.0f_%05.0f_%05.0f.dat  &
+python extractTimeSeries.py $NCFILE -x `seq 0 50 550` -y 450 550 -z 0\
[…]

### 2020-11-27 Paper/main.tex
Updating paper latex files

@@
   Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
-  Shashank Yellapantula\footnote{SOME JOB TITLE, AIAA Member}
 }
@@
 
-\author{Nathaniel B. deVelder\footnote{Postdoctoral appointee, AIAA member} and
-  Alan S. Hsieh.\footnote{Postdoctoral appointee, Wind Energy Technologies Department, AIAA member}}
-\affil{Sandia National Laboratories, Albuquerque, NM 87185}
+\author{Nathaniel B. deVelder\footnote{Postdoctoral appointee, Wind
+    Energy Technologies Department, AIAA member} and Alan
+  S. Hsieh.\footnote{Postdoctoral appointee, Wind Energy Technologies
+    Department, AIAA member}} \affil{Sandia National Laboratories,
+  Albuquerque, NM 87185}
 
@@
 $u_\tau$   & Friction velocity    \\
+$R_{ij}$   & Two point correlation tensor \\
 $TI$      & Turbulence intensity 
@@
 \section{Introduction}
-\fxnote{This is the introduction from the abstract.  Update with real
-  introduction.}
+\fxnote{Update this introduction.}
 
-\lettrine{P}{ut} the introduction here.
-
-The planned installation of several offshore wind energy plants in the
-United States has highlighted the need to properly understand the wind
-resource and atmospheric characteristics of the US Atlantic Coast.
-Several atmospheric phenomena particular to this region, such as
-coastal low-level jets or seasonal Nor’easters, have the potential to
-substantially impact the operation and power production of offshore
-wind plants.  Of particular interest to the current study is the
-atmospheric stability of the marine boundary layer in the Northeastern
-US.
+\lettrine{T}he planned installation of several offshore wind energy
+plants in the United States has highlighted the need to properly
+understand the wind resource and atmospheric characteristics of the US
+Atlantic Coast.  Several atmospheric phenomena particular to this
+region, such as coastal low-level jets or seasonal Nor’easters, have
+the potential to substantially impact the operation and power
+production of offshore wind plants.  Of particular interest to the
+current study is the atmospheric stability of the marine boundary
+layer in the Northeastern US.
 
@@
 
+\fxnote{Mention study by \cite{wurps2020grid}.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section*{Acknowledgments}
-\fxnote{Acknowledge Matt for work on BC}
+\fxnote{Acknowledge Matt for work on BC} \\
+\fxnote{Acknowledge Shashank for work on BC}
 
@@
 
-\fxnote{ADD ANY NREL ACKNOWLEDGEMENTS NECESSARY HERE}
+This work was authored in part by the National Renewable Energy
+Laboratory, operated by Alliance for Sustainable Energy, LLC, for the
+U.S. Department of Energy (DOE) under Contract No. DE-AC36-
+08GO28308. M. Brazell was partially funded by the Exascale Computing
+Project (17-SC-20-SC), a collaborative effort of two DOE organizations
+(Office of Science and the National Nuclear Security Administration).
 
-% \bibliography{sample}
+A portion of the research was performed using computational
+resources sponsored by the Department of Energy's Office of Energy
+Efficiency and Renewable Energy and located at the National Renewable
+Energy Laboratory.
+
 \bibliography{references}

### 2020-11-27 Paper/methodology.tex
Update paper stuff
Updating paper latex files

@@
 
-Write something about Cape Wind measurements from \cite{archer2016predominance}.
+Following the work of Cheung et al \cite{cheung2020large}, we use
+measurements of the offshore coastal marine boundary layer, collected
+by the Cape Wind meteorological tower in Nantucket Sound, as the basis
+for this computational study.  The Cape Wind platform collected wind
+measurements at 20m, 41m, and 60m above the mean water level, along
+with temperature and barometric measurements from the years 2003-2011.
+From the observations, Archer et al.\cite{archer2016predominance}
+found that the marine boundary layer is predominantly unstable, with
+61\% of conditions classified as unstable, versus 21\% neutral and
+18\% stable.  The stratification of the marine boundary layer, as
+determined by the Obukhov length, also had a large impact on the wind
+speed profile, with flatter, non-logarithmic profiles seen during
+unstable conditions.
 
-\subsection{LES Codes}
+From the measured distribution of atmospheric stabilities, turbulent
+kinetic energies (TKE), and wind speeds from the Cape Wind platform, a
+specific set of conditions were chosen as targets for this
+computational study.  A summary of the conditions for all stability
+classes is given table \ref{tab:CapeWindMeasurements}. In this work we
+focus on the three stable atmospheric conditions at wind speeds of
+5m/s, 10m/s, and 15m/s, while the neutral and unstable conditions
+where studied in previous work \cite{cheung2020large}.
+
+To maintain consistency with the measured data, the turbulence
+intensity (TI) is calculated using the TKE as
+\begin{equation}
+  \textrm{TI} =
+  \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
+  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u' + v'v' + w'w'}
+      \right)}}{\overline{U}_{horiz}}
+\end{equation}
+The averaged wind speeds were enforced at the measurement height of
+20m, and the wind directions...
+
+\begin{table}
+\caption{\label{tab:CapeWindMeasurements} Measured conditions at Cape
+  Wind.  The stable atmospheric conditions used in this study are
+  highlighted in bold below.} \centering
+\begin{tabular}{cccc}
+  \hline
+  Stability    & Wind speed [m/s] & Wind dir [deg] & Turbulence intensity \\
+  \hline
+  Neutral      & 5                & 225            & 0.055           \\
+  Neutral      & 10               & 225            & 0.055           \\
+  Neutral      & 15               & 225            & 0.065           \\
+  Unstable     & 5                & 315            & 0.080           \\
+  Unstable     & 10               & 315            & 0.075           \\
+  Unstable     & 15               & 315            & 0.090           \\
+  \bf{Stable}  & \bf{5}           & \bf{225}       & \bf{0.045}      \\
+  \bf{Stable}  & \bf{10}          & \bf{225}       & \bf{0.050}      \\
+  \bf{Stable}  & \bf{15}          & \bf{225}       & \bf{0.060}      \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Computational methodlogy}
 Provide a general description of the LES codes that we use.
 
+\subsection{LES formulation}
+
+\subsubsection{Governing equations}
+
+\subsubsection{Lower wall model BC}
+\fxnote{Ganesh write this part}\\
+What we implemented in terms of the lower boundary condition.
+
 \subsubsection{Nalu-Wind}
+\fxnote{Shreyas write this part}\\
 Describe Nalu-Wind
@@
 
-\subsubsection{Lower wall model BC}
-\fxnote{Ganesh write this part}\\
-What we implemented in terms of the lower boundary condition.
+\begin{table}
+\caption{\label{tab:Computational parameters} LES parameters for stable conditions}
+\centering
+\begin{tabular}{cccc}
+  \hline
+  Stability    & Wind speed  & Surface roughness $z_0$ & Temperature gradient \\
+  \hline
+  Stable       & 5  m/s           & 0.0005 m       & -0.32 K/hr      \\
+  Stable       & 10 m/s           & 0.0005 m       & -1.40 K/hr      \\
+  Stable       & 15 m/s           & 0.0005 m       & -1.50 K/hr      \\
+\hline
+\end{tabular}
+\end{table}
 
 \subsubsection{Simulation workflow}
+\fxnote{Lawrence write this part}\\
 Describe the process to hit target conditions.

### 2020-11-27 Paper/results.tex
Updating paper latex files

@@
 
-\subsection{ABL integrated quantities}
+\subsection{Domain and grid resolution study}
+
+%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
+\begin{tabular}{ccccc}
+  \hline
+  Case              & dx [m] & dy [m] & dz [m] \\
+  \hline
+  Nalu-wind coarse  &  10.0  & 10.0   & 2.5   \\
+  Nalu-wind medium  &   5.0  &  5.0   & 2.5   \\
+  Nalu-wind fine    &   2.5  &  2.5   & 2.5   \\
+  AMR-wind fine     &   2.5  &  2.5   & 2.5   \\
+\hline
+\end{tabular}
+\end{table}
+
+The maximum resolvable frequency on a mesh with grid size $\Delta$ and
+average horizontal wind speed $\bar{U}_{horiz}$ can be estimated as
+\begin{equation}
+  \label{eq:fmax}
+  f_{max} = \frac{0.6\bar{U}_{horiz}}{N\Delta}.
+\end{equation}
+Here, equation \ref{eq:fmax} assumes that the turbulent eddies convect
+with a velocity of $0.6\bar{U}_{horiz}$ and $N=8$ is chosen for the
+purposes of this study.  Due to the alignment of the flow with the
+mesh directions, the grid size $\Delta = \sqrt{2}\cdot \textrm{dx}$.
+
+The wind spectra
+\begin{equation}
+  \int_0^\infty S_i(f) \textrm{d}f = \sigma_i^2
+\end{equation}
+
+%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/GridStudy/GridStudy_Spectra.ipynb
+\begin{figure}[hbt!]
+  \label{fig:GridStudySpectra}
+  \centering
+  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
+  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sv.png}
+  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sw.png}
+  \caption{Calculation of the wind spectra $S_i$ for LES of stable
+    5m/s case with different resolutions.  The gray vertical lines
+    correspond to the maximum resolvable frequency according to
+    equation (\ref{eq:fmax}). }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The two-point correlation tensor defined as
+\begin{equation}
+  \label{eq:Rij}
+  R_{ij}({\mathbf x},\boldsymbol{\xi}) = 
+  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
+       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
+\end{equation}
+where the velocity fluctuations $u'_i$ are defined as 
+\begin{equation}
+  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
+\end{equation}
+
+The horizontally averaged correlation coefficient $\langle
+R_{ij}(\boldsymbol{\xi})\rangle$ is computed from
+$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ by sampling over ...
+
+%%%%%%%%%%% Grid resolution correlation figure %%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
+\begin{figure}[hbt!]
+  \label{fig:GridStudyRij}
+  \centering
+  \includegraphics[width=3in]{figures/GridStudy_Rij_Longitudinal.png}
+  \includegraphics[width=3in]{figures/GridStudy_Rij_Lateral.png}
+  \caption{Calculation of the averaged longitudinal and lateral
+    $R_{ij}(\xi)$ coefficient at $z$=20m for LES of stable 5m/s case
+    with different resolutions.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The turbulent integral lengthscale can be calculated from $\langle
+R_{ij}(\xi) \rangle$ via
+\begin{equation}
+  L = \int_0^\infty \langle R_{ij}(\xi) \rangle \: {\textrm d}\xi
+\end{equation}
+
+%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:GridStudyLscale} The calculated turbulent integral
+  lengthscale for each of the grid resolutions} \centering
+\begin{tabular}{ccccc}
+  \hline
+  Case              & dx [m] & Longitudinal L [m] & Lateral L [m] \\
+  \hline
+  Nalu-wind coarse  &  10.0  & 36.433999          & 0.0        \\
+  Nalu-wind medium  &   5.0  & 21.485711          & 4.519247   \\
+  AMR-wind fine     &   2.5  & 27.689340          & 9.332672   \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Comparison of AMR-Wind vs Nalu-Wind}
+
+\subsection{ABL Physics}
+
+\subsubsection{ABL integrated quantities}
 Describe integrated quantities
 
-\subsection{Horizontally averaged profiles}
+\subsubsection{Horizontally averaged profiles}
 
-\subsection{Wind spectra and turbulence statistics}
+\subsubsection{Wind spectra and turbulence statistics}
+
+The Kaimal model for spectra \cite{kaimal1973turbulence, cheynet2017spectral}
+\begin{equation}
+  \label{eq:kaimal}
+  \frac{fS_i}{u_\tau^2} = \frac{a_i(fz/\bar{U})}{\left(1+b_i(fz/\bar{U})^{\alpha_i}\right)^{\beta_i}}
+\end{equation}
+
+%%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
+\centering
+\begin{tabular}{ccccc}
+  \hline
+  Velocity & $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
+  \hline
+  $u$      & 105.0 & 33.0  & 1           & 5/3  \\
+  $v$      &  17.0 &  9.5  & 1           & 5/3  \\
+  $w$      &   2.1 &  5.3  & 5/3         &   1  \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsubsection{Comparison with neutral and unstable conditions}
+
+%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
+% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
+\begin{figure}[hbt!]
+  \label{fig:AllStabilityRij}
+  \centering
+  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
+  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
+  \caption{Calculation of the averaged longitudinal and lateral
+    $R_{ij}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-11-30 Postprocessing/utilities/correlate.py
Added postprocessing files and plots

@@ -325,7 +325,10 @@ def plotprobes(allplist, dat, headers, verbose=False, skip=1):
     plt.plot(xlines, ylines, 'b-')
     # plot the probe points
     for ilist, plist in enumerate(allplist):
-        if (verbose): print("On %i of %i"%(ilist, len(allplist)))
+        #if (verbose): print("On %i of %i"%(ilist, len(allplist)))
+        if (verbose):
+            sys.stdout.write("\r%d%%" % int((ilist+1)*100.0/len(allplist)))
+            sys.stdout.flush()
         for ip, pt in enumerate(plist[::skip]):
             pts   = sanitizepoint(pt, Ni, Nj, Nplanes)
             i1    = getplaneindex(pts[0], pts[1], pts[2], Ni, Nj)
@@ -335,7 +338,7 @@ def plotprobes(allplist, dat, headers, verbose=False, skip=1):
             if (ip==0): 
                 ms = 10
                 color='g'
-            if (i1>=Ni*Nj): 
+            if (i1>=Ni*Nj*(pts[2]+1)): 
                 ms = 10
                 color='r'
             plt.plot(xyz1[0], xyz1[1], '.', color=color, markersize=ms)

### 2020-11-30 Paper/methodology.tex
Writing more sections of the paper

@@
 \subsection{Measured offshore conditions}
-\fxnote{Lawrence write this part}
+% \fxnote{Lawrence write this part}
 
@@
 From the measured distribution of atmospheric stabilities, turbulent
-kinetic energies (TKE), and wind speeds from the Cape Wind platform, a
-specific set of conditions were chosen as targets for this
+kinetic energies (TKE), and wind speeds from the Cape Wind platform at
+z=20m, a stable set of conditions were chosen as targets for this
 computational study.  A summary of the conditions for all stability
@@
 The averaged wind speeds were enforced at the measurement height of
-20m, and the wind directions...
+20m, and the applied wind directions were consistent with the
+predominant stable direction of 225 degrees southwest.
 
@@
 
-\subsection{Computational methodlogy}
+\subsection{Computational methodology}
 Provide a general description of the LES codes that we use.
@@
 
-\subsubsection{Lower wall model BC}
+\subsubsection{\label{sec:wallmodelBC}Lower wall model BC}
 \fxnote{Ganesh write this part}\\
@@
 
-\subsection{Computational set up}
-\fxnote{Lawrence write this part}\\
-Domains, grids, boundary conditions
+\subsection{Computational setup}
+% \fxnote{Domains, grids, boundary conditions}
 
 \begin{table}
-\caption{\label{tab:Computational parameters} LES parameters for stable conditions}
+\caption{\label{tab:z0tempparam} LES parameters for stable ABL conditions}
 \centering
-\begin{tabular}{cccc}
+\begin{tabular}{ccccc}
   \hline
-  Stability    & Wind speed  & Surface roughness $z_0$ & Temperature gradient \\
+  Stability & Wind speed & Surface roughness $z_0$ & Surface
+  temperature change & timestep\\
   \hline
-  Stable       & 5  m/s           & 0.0005 m       & -0.32 K/hr      \\
-  Stable       & 10 m/s           & 0.0005 m       & -1.40 K/hr      \\
-  Stable       & 15 m/s           & 0.0005 m       & -1.50 K/hr      \\
+  Stable       & 5  m/s           & 0.0005 m       & -0.32 K/hr   & 0.25 sec   \\
+  Stable       & 10 m/s           & 0.0005 m       & -1.40 K/hr   & 0.125 sec  \\
+  Stable       & 15 m/s           & 0.0005 m       & -1.50 K/hr   & 0.0625 sec \\
 \hline
@@
 
-\subsubsection{Simulation workflow}
-\fxnote{Lawrence write this part}\\
-Describe the process to hit target conditions.
+The computational methodology for the AMR-Wind and Nalu-Wind LES codes
+follows practices similar to the previous offshore ABL study, with
+some modifications to handle the stable stratification.  As in
+\cite{cheung2020large}, the domain was a square prism geometry, with
+the $x$ and $y$ coordinates aligned in the East and North directions,
+respectively.  The domain size and mesh requirements were determined
+through a numerical grid study.  As discussed in section
+\ref{sec:gridstudy}, the horizontal dimensions of 750m $\times$ 750m
+were found to be sufficient to capture any large scale structures in
+the boundary layer, and in all cases the vertical dimension of 1000m
+was also used.  The grid study in section \ref{sec:gridstudy} also
+showed that the stable stratification required greater mesh refinement
+to capture the smaller turbulent scales, and a uniform cell size of
+2.5m was adopted for the offshore LES computations across both codes.
+
+Momentum source terms were included in Nalu-Wind and AMR-Wind to
+ensure that the horizontally averaged velocity matched the targeted
+wind speed at the z=20 m height.  These source terms are based on the
+difference between the desired wind velocity and the instantaneous
+horizontally averaged velocity, and are only a function of time and
+height z.  Coriolis forcing matching the Cape Wind latitude was
+included to capture the effect of wind change with elevation.
+
+\subsubsection{Boundary and initial conditions}
+In both horizontal directions of the computational domain, periodic
+boundary conditions were applied.  At the lower boundary, we chose to
+represent the air/ocean interface using flat boundary with small
+amount of surface roughness.  This allowed the wall model discussed in
+section \ref{sec:wallmodelBC} to be applied.  Monin-Obukhov similarity
+theory was used to determine the velocity and temperature profiles
+near the lower surface given a surface roughness height $z_0$ and the
+prescribed surface temperature as a function of time.  At the upper
+surface of the domain, a potential flow based boundary condition is
+applied along with a normal temperature gradient of 0.003 K/m.
+
+The initial temperature profile in all cases was a constant 300K until
+the specified inversion height of 650m.  The inversion layer thickness
+was 100m, and above this, the temperature linearly increased until it
+reached 308.75K at the upper boundary.  The initial mean velocity
+profile was uniform throughout the domain with superimposed sinusoidal
+velocity perturbations of magnitude 1 m/s to promote the development
+of turbulence.
+
+\subsubsection{Determination of surface roughness and prescribed temperature }
+To match the measured TI conditions given in table
+\ref{tab:CapeWindMeasurements}, the surface roughness and prescribed
+surface temperature change were adjusted through an initial
+trial-and-error process.  The final surface roughness of $z_0$=0.0005m
+used the stable offshore conditions (see table \ref{tab:z0tempparam})
+matched the roughness used in the neutral 15m/s and unstable 5m/s and
+10m/s cases from the previous study \cite{cheung2020large}.  This
+value of surface roughness is consistent with the measurements from
+the North Sea \cite{taylor2001dependence}, which found values of $z_0$
+ranging from $5 \times 10^{-5}$m to $5\times 10^{-3}$m.
+
+The values of the prescribed temperature change at the ocean surface
+is also given in table \ref{tab:CapeWindMeasurements}.  As the wind
+speed increases, a larger temperature decrease was used to maintain
+similar levels of stable stratification, as expected from
+Monin-Obukhov similarity theory.

### 2020-11-30 Paper/results.tex
Writing more sections of the paper

@@
 
-\subsection{Domain and grid resolution study}
+\subsection{\label{sec:gridstudy}Domain and grid resolution study}
 
-%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
-\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
-\begin{tabular}{ccccc}
-  \hline
-  Case              & dx [m] & dy [m] & dz [m] \\
-  \hline
-  Nalu-wind coarse  &  10.0  & 10.0   & 2.5   \\
-  Nalu-wind medium  &   5.0  &  5.0   & 2.5   \\
-  Nalu-wind fine    &   2.5  &  2.5   & 2.5   \\
-  AMR-wind fine     &   2.5  &  2.5   & 2.5   \\
-\hline
-\end{tabular}
-\end{table}
+In order to ensure that the large and small turbulence scales were
+properly resolved in the offshore LES simulations, the appropriate
+domain size and mesh resolution needed to be determined.
+Under-resolved meshes or domain sizes which are too small may miss the
+smaller turbulence scales or remove the larger structures required for
+proper ABL development.  However, over-resolved meshes or
+unnecessarily large domains might lead to excessive computational
+requirements to complete the simulations.
+
+The appopriateness of these meshes and domain sizes were determined
+based on wind spectra and integral length scale they were able to capture.
 
@@
 mesh directions, the grid size $\Delta = \sqrt{2}\cdot \textrm{dx}$.
+
+%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
+\begin{tabular}{ccccc}
+  \hline
+  Case              & dx [m] & dy [m] & dz [m] & Domain size \\
+  \hline
+  Nalu-wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km x 1.5km x 1.0km  \\
+  Nalu-wind medium  &   5.0  &  5.0   & 2.5 & 1.5km x 1.5km x 1.0km  \\
+  Nalu-wind fine    &   2.5  &  2.5   & 2.5 & 0.0 \\
+  AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     5m/s case with different resolutions.  The gray vertical lines
-    correspond to the maximum resolvable frequency according to
-    equation (\ref{eq:fmax}). }
+    correspond to the maximum resolvable frequency $f_{max}$ according
+    to equation (\ref{eq:fmax}). }
 \end{figure}
@@
 
-%%%%%%%%%%% Grid resolution correlation figure %%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%% Grid resolution Rij correlation figure %%%%%%%%%%%%%%%%%%%%
 % Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
@@
   Nalu-wind medium  &   5.0  & 21.485711          & 4.519247   \\
+  Nalu-wind fine    &   2.5  & 25.250568          & 5.919645   \\
   AMR-wind fine     &   2.5  & 27.689340          & 9.332672   \\
@@
 \subsection{Comparison of AMR-Wind vs Nalu-Wind}
+\fxnote{COMPARE AMR-WIND VS NALU-WIND HERE}
+
+%%%%%%%%%%%%%%% Compare Nalu/AMR integrated quantities %%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and Nalu-Wind} \centering
+\begin{tabular}{ccccc}
+  \hline
+  Case          & TI        &  $\alpha$  &   $u_\tau$ &       L \\
+  \hline
+  naluwind 5m/s &  0.048106 &  0.165277 &  0.163342 & 94.970836 \\
+  amrwind 5m/s  &  0.048255 &  0.165552 &  0.157399 & 52.512434 \\
+  \hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%% Compare Nalu/AMR profiles %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5.ipynb
+\begin{figure}[hbt!]
+  \label{fig:CompareAMRvsNaluProfiles}
+  \centering
+  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}\\
+  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
+  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
+  \caption{Comparison of AMR-Wind and Nalu-Wind profiles. }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%% Compare Nalu/AMR spectra %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Postprocessing/ABLSpectra/AMRWind_NaluWind_Spectra_Stable.ipynb
+\begin{figure}[hbt!]
+  \label{fig:CompareAMRvsNaluSpectra}
+  \centering
+  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Spectra_Stable_z20.png}
+
+  \caption{Comparison of AMR-Wind and Nalu-Wind wind spectra at
+    z=20m. }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%% Compare Nalu/AMR lengthscale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
+\begin{figure}[hbt!]
+  \label{fig:CompareAMRvsNaluRij}
+  \centering
+  \fxnote{UPDATE THIS FIGURE}\\
+  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Longitudinal.png}
+  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Lateral.png}
+
+  \caption{Comparison of AMR-Wind and Nalu-Wind $\langle R_{ij}
+    \rangle$ correlation at z=20m. }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The Kaimal model for spectra \cite{kaimal1973turbulence, cheynet2017spectral}
+The Kaimal model for spectra \cite{kaimal1973turbulence,
+  cheynet2017spectral} for neutral atmospheric conditions:
 \begin{equation}
@@
 
+%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
+\begin{figure}[hbt!]
+  \label{fig:ABLSpectra_AllZ}
+  \centering
+  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
+  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
+  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
+  \caption{Calculation of the wind spectra $S_i$ for LES of stable
+    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
+    vertical lines correspond to the maximum resolvable frequency
+    $f_{max}$ according to equation (\ref{eq:fmax}). }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsubsection{Comparison with neutral and unstable conditions}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:StabilityStudyLscale} The calculated turbulent
+  integral lengthscale for each of atmospheric stabilities} \centering
+\begin{tabular}{ccccc}
+  \hline
+  Stability   & Wind speed & Longitudinal L [m] & Lateral L [m] \\
+  \hline
+  Stable      &   5 m/s  & 0.0           & 0.0        \\
+  Stable      &  10 m/s  & 0.0           & 0.0        \\
+  Stable      &  15 m/s  & 0.0           & 0.0        \\
+  Neutral     &   5 m/s  & 110.435741    & 15.245327  \\
+  Neutral     &  10 m/s  & 165.398368    & 20.634052  \\
+  Neutral     &  15 m/s  & 184.081967    & 22.961169  \\
+  Unstable    &   5 m/s  & 187.868710    & 270.538753 \\
+  Unstable    &  10 m/s  & 177.457502    & 215.027457 \\
+  Unstable    &  15 m/s  & 263.475309    & 67.999898  \\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-01 Paper/main.tex
Writing more sections of the paper
Add more to paper latex files

@@
 $\alpha$  & Wind shear exponent  \\
-$L$       & Obukhov length scale \\
+$f$       & Frequency \\
+$L$       & Turbulent integral length scale \\
 $u_\tau$   & Friction velocity    \\
 $R_{ij}$   & Two point correlation tensor \\
-$TI$      & Turbulence intensity 
+$TI$      & Turbulence intensity \\
+$TKE$     & Turbulent kinetic energy 
 \end{longtable*}}
@@
 
-\fxnote{Mention study by \cite{wurps2020grid}.}
+\fxnote{Mention study by \cite{wurps2020grid}.  Nate's piece goes here.}
 
@@
 \section*{Acknowledgments}
-\fxnote{Acknowledge Matt for work on BC} \\
-\fxnote{Acknowledge Shashank for work on BC}
+
+The authors wish to acknowlege the contributions from M. Churchfield
+and S. Yellapantula for their development of the LES boundary
+conditions and for their efforts in validating the ExaWind codes.
 

### 2020-12-01 Paper/methodology.tex
Add more to paper latex files

@@
 \subsubsection{Governing equations}
+\fxnote{Shreyas write this part.  Currently placeholder equations below.}\\
+
+The low-Mach number equations:
+\begin{align}
+  \frac{\partial \rho} {\partial t} + \frac{\partial \rho u_j}{\partial x_j} & = 0, \\
+\frac{\partial \rho u_i}{\partial t} + \frac{\partial \rho u_j u_i}{\partial x_j}
++ \frac{\partial P}{\partial x_i} & = \frac{\partial \tau_{ij}}{\partial x_j}
++ \left( \rho - \rho_{\circ} \right) g_i, \\
+\frac{\partial \rho h}{\partial t} + \frac{\partial \rho u_j h}{\partial x_j} & =
+- \frac{\partial q_j}{\partial x_j} + \frac{\partial P_{th}}{\partial t},
+\end{align}
 
@@
 Monin-Obukhov similarity theory.
+
+Once the appropriate surface roughness and prescribed temperature were
+determined, and the correct mesh requirements known from the study in
+section \ref{sec:gridstudy}, the LES computations for the stable 5m/s,
+10m/s, and 15m/s ABL cases could be set up and run.  Each of the cases
+was run for 15,000 seconds before collecting statistics for another
+5,000 seconds.  To maintain a CFL number less than unity during these
+runs, a smaller timestep was used for the higher wind speeds (see
+table \ref{tab:z0tempparam}).

### 2020-12-01 Paper/results.tex
Add more to paper latex files

@@
 \section{Results}
-\fxnote{This should be a collaborative section}
 
@@
 
-The appopriateness of these meshes and domain sizes were determined
-based on wind spectra and integral length scale they were able to capture.
+To determine the appropriate mesh size and resolution, a grid study
+was conducted using the stable 5m/s ABL case and the Nalu-Wind code.
+A number of cases were set up using the surface roughness and
+prescribed temperature decreases listed in table
+\ref{tab:z0tempparam}, but with varying grid resolutions and
+conservative estimates for the domain size required.  As shown in
+table \ref{tab:GridStudySetup}, the horizontal resolutions varied from
+10m to 2.5m cells for the coarse and fine cases, respectively.  All
+simulations for the grid study also used a vertical resolution of
+dz=2.5m and the same vertical extent of 1km.
 
-The maximum resolvable frequency on a mesh with grid size $\Delta$ and
-average horizontal wind speed $\bar{U}_{horiz}$ can be estimated as
+%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
+\begin{tabular}{ccccc}
+  \hline
+  Case              & dx [m] & dy [m] & dz [m] & Domain size \\
+  \hline
+  Nalu-wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
+  Nalu-wind medium  &   5.0  &  5.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
+  Nalu-wind fine    &   2.5  &  2.5   & 2.5 & 1.0km $\times$ 1.0km $\times$ 1.0km  \\
+% AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The suitability of these meshes and domain sizes were determined based
+on the resulting wind spectra and turbulent correlation metrics from
+the simulated ABL. The wind spectra $S_i(f)$ is defined as a function
+of the frequency $f$
+\begin{equation}
+  \int_0^\infty S_i(f) \textrm{d}f = \sigma_i^2
+\end{equation}
+where $\sigma_i$ is the wind speed variance and the index $i=u,v,w$
+denotes the longitudinal, lateral, or vertical velocity, respectively.
+For the LES simulations in this study, we desire that that the mesh
+resolution be sufficiently fine to capture the high frequency
+components of the spectra past the spectral peak.  This helps ensure
+that the unsteady characteristics in the boundary layer are resolved.
+
+%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/GridStudy/GridStudy_Spectra.ipynb
+\begin{figure}%[hbt!]
+  \centering
+  \fxnote{remove AMR-Wind results from graphs}\\
+  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
+  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sv.png}
+  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sw.png}
+  \caption{   \label{fig:GridStudySpectra} 
+    Calculation of the wind spectra $S_i$ for LES of stable
+    5m/s case with different resolutions.  The gray vertical lines
+    correspond to the maximum resolvable frequency $f_{max}$ according
+    to equation (\ref{eq:fmax}). }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Two numerical constraints limit the maximum resolvable frequency in
+the current ABL computations.  First, the Nyquist frequency $f_{Ny}$
+limits the highest resolved frequency to half the sampling frequency, or
+
+\begin{equation}
+  f_{Ny} = \frac{1}{2\times \textrm{dt}}
+\end{equation}
+Secondly, the maximum resolvable frequency of convecting fine scale
+eddies on a mesh with grid size $\Delta$ and average horizontal wind
+speed $\bar{U}_{horiz}$ can be estimated as
 \begin{equation}
@@
 mesh directions, the grid size $\Delta = \sqrt{2}\cdot \textrm{dx}$.
+In all cases considered here, $f_{max} < f_{Ny}$, so the limiting
+constraint for resolving the high frequency components was the mesh
+resolution.
 
-%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
-\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
-\begin{tabular}{ccccc}
-  \hline
-  Case              & dx [m] & dy [m] & dz [m] & Domain size \\
-  \hline
-  Nalu-wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km x 1.5km x 1.0km  \\
-  Nalu-wind medium  &   5.0  &  5.0   & 2.5 & 1.5km x 1.5km x 1.0km  \\
-  Nalu-wind fine    &   2.5  &  2.5   & 2.5 & 0.0 \\
-  AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The comparison of the wind spectra and maximum resolvable frequency
+$f_{max}$ for the different mesh resolutions is shown in figure
+\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20m
+height and averaged using 1/3 octave-bins to enchance clarity. For the
+$S_u$ and $S_w$ spectra, there noticeable shifts in the peak
+amplitude, while the peak amplitudes for $S_v$ remained fairly
+constant between cases.  In all cases, the peak frequency of $S_i(f)$
+also increased as the resolution increased. While the mesh resolution
+was sufficient to capture the peak frequency for $S_u$, the fine
+resolution with 2.5m mesh cells was required to capture the spectral
+peaks in the lateral and vertical directions.
 
-The wind spectra
-\begin{equation}
-  \int_0^\infty S_i(f) \textrm{d}f = \sigma_i^2
-\end{equation}
-
-%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
-% Created in Postprocessing/GridStudy/GridStudy_Spectra.ipynb
-\begin{figure}[hbt!]
-  \label{fig:GridStudySpectra}
-  \centering
-  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
-  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sv.png}
-  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sw.png}
-  \caption{Calculation of the wind spectra $S_i$ for LES of stable
-    5m/s case with different resolutions.  The gray vertical lines
-    correspond to the maximum resolvable frequency $f_{max}$ according
-    to equation (\ref{eq:fmax}). }
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The two-point correlation tensor defined as
+The second metric for determining the appropriate grid size and mesh
+resolution is through the correlation tensor and turbulence integral
+length scale.  The two-point correlation tensor
+$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
+separation vector $\boldsymbol{\xi}$ is defined as
 \begin{equation}
@@
 \end{equation}
-
-The horizontally averaged correlation coefficient $\langle
-R_{ij}(\boldsymbol{\xi})\rangle$ is computed from
-$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ by sampling over ...
+and the overbar operator $\overline{(\bullet)}$ denotes time
+averaging.  In the current study, we compute the horizontally averaged
+correlation coefficient $\langle R_{ij}(\boldsymbol{\xi})\rangle$ by
+sampling over multiple points at the $z$=20m height, typically 100-150
+points, and averaging the result.  The longitudinal $\langle
+R_{ij}(\boldsymbol{\xi})\rangle$ was calculated by looking at
+separation vectors $\boldsymbol{\xi}$ in the streamwise direction
+while the lateral $\langle R_{ij}(\boldsymbol{\xi})\rangle$ used
+separation distances $\boldsymbol{\xi}$ which were orthogonal to the
+wind direction on the same horizontal plane.
 
@@
 % Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
-\begin{figure}[hbt!]
-  \label{fig:GridStudyRij}
+\begin{figure}%[hbt!]
   \centering
-  \includegraphics[width=3in]{figures/GridStudy_Rij_Longitudinal.png}
-  \includegraphics[width=3in]{figures/GridStudy_Rij_Lateral.png}
-  \caption{Calculation of the averaged longitudinal and lateral
-    $R_{ij}(\xi)$ coefficient at $z$=20m for LES of stable 5m/s case
-    with different resolutions.}
+  \fxnote{remove AMR-Wind results from graphs}\\
+  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
+  \includegraphics[width=2.5in]{figures/GridStudy_Rij_Lateral.png}
+  \caption{\label{fig:GridStudyRij} Calculation of the averaged
+    longitudinal and lateral $\langle R_{ij}(\boldsymbol{\xi})
+    \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
+    different resolutions.}
 \end{figure}
@@
 
-The turbulent integral lengthscale can be calculated from $\langle
-R_{ij}(\xi) \rangle$ via
+The results shown in figure \ref{fig:GridStudyRij} show that the
+finest resolution is required to resolve both the longitudinal and the
+lateral length scale.  In contrast to the neutral and unstable ABL
+cases, the turbulent structures decorrelate rapidly and are noticeably
+finer in the lateral direction compared to the longitudinal direction.
+While 2.5m resolution is adequate to resolve the longitudinal
+turbulent structures, the lateral direction may require even finer
+resolution to fully resolve.  This may be an important consideration
+in situations where turbulence in a stable boundary layer interacts
+with turbine features, such as blade motions or downstream wakes.
+However, the additional refinement requires careful balancing against
+the additional computational expense in the simulation.
+
+Similar conclusions can be drawn by examining the turbulent integral
+length scale $L$.  This lengthscale can be calculated from $\langle
+R_{ij}(\boldsymbol{\xi}) \rangle$ via
 \begin{equation}
@@
 \end{equation}
+and the results are shown in table \ref{tab:GridStudyLscale}.  With a
+resolution of 2.5m, the ratio of the longitudinal length scale to the
+grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
+$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
+required to capture the lateral scales.  Based on this longitudinal
+length scale, we also determined the overall domain size necessary for
+stable ABL calculations.  A minimum domain of 750m $\times$ 750m in
+the horizontal directions was used in all Nalu-Wind and AMR-Wind LES
+calculations, which provided sufficient space for the largest
+turbulent structures to develop and evolve without interference from
+the boundaries or other structures.
 
 %%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
+\begin{table}[h!]
 \caption{\label{tab:GridStudyLscale} The calculated turbulent integral
@@
   \hline
-  Case              & dx [m] & Longitudinal L [m] & Lateral L [m] \\
+  Case              & dx [m] & Longitudinal L  & Lateral L \\
   \hline
-  Nalu-wind coarse  &  10.0  & 36.433999          & 0.0        \\
-  Nalu-wind medium  &   5.0  & 21.485711          & 4.519247   \\
-  Nalu-wind fine    &   2.5  & 25.250568          & 5.919645   \\
-  AMR-wind fine     &   2.5  & 27.689340          & 9.332672   \\
+  Nalu-wind coarse  &  10.0  & 36.43 m         & 0.0 m     \\
+  Nalu-wind medium  &   5.0  & 21.49 m         & 4.52 m    \\
+  Nalu-wind fine    &   2.5  & 25.25 m         & 5.92 m    \\
+% AMR-wind fine     &   2.5  & 27.689340 m     & 9.332672   \\
 \hline
@@
 \subsection{Comparison of AMR-Wind vs Nalu-Wind}
-\fxnote{COMPARE AMR-WIND VS NALU-WIND HERE}
 
@@
 \caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and Nalu-Wind} \centering
-\begin{tabular}{ccccc}
+\begin{tabular}{cccccc}
   \hline
-  Case          & TI        &  $\alpha$  &   $u_\tau$ &       L \\
+  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$ \\ %&       L \\
   \hline
-  naluwind 5m/s &  0.048106 &  0.165277 &  0.163342 & 94.970836 \\
-  amrwind 5m/s  &  0.048255 &  0.165552 &  0.157399 & 52.512434 \\
+  Nalu-Wind & 5 m/s &  0.0481 &  0.165     &  0.163 m/s \\ %& 94.970836 \\
+  AMR-Wind  & 5 m/s &  0.0483 &  0.166     &  0.157 m/s \\ %& 52.512434 \\
   \hline
@@
 
-%%%%%%%%%%% Compare Nalu/AMR profiles %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5.ipynb
-\begin{figure}[hbt!]
-  \label{fig:CompareAMRvsNaluProfiles}
+Before examining the behavior the offshore ABL across all wind speeds,
+we first compare the results for a single case using both LES codes.
+In this section, we consider the stable 5m/s case, calculated in the
+same manner using both AMR-Wind and Nalu-Wind.  Both LES codes used a
+mesh resolution of 2.5m based on the guidance from section
+\ref{sec:gridstudy} and the computational resources available.
+
+After running each case for 15,000 seconds, the boundary layer
+statistics and horizontally averaged profiles were averaged for
+another 5,000 seconds.  In table \ref{tab:CompareAMRvsNalu}, some mean
+statistics are given for both cases, including the friction velocity
+$u_\tau$, the turbulence intensity TI at z=20m, and local shear
+exponent $\alpha$ at z=20m, defined as
+$$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
+$$ AMR-Wind and Nalu-Wind produced nearly identical values for the
+TI=0.048, which is close to measured target of 4.5\%, and similar
+agreement was found for the shear exponent $\alpha$.  A minor
+descrepancy was found in the friction velocity $u_\tau$, with AMR-Wind
+resulting in a value slightly lower than Nalu-Wind.
+
+The comparison of the horizontally averaged wind profiles is shown in
+figure \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
+z=20m, the wind speed and wind shear match are close to an exact match
+between the two LES codes.  The horizontal wind speeds continue to
+agree well for $z$<100m, beyond which a relatively constant velocity
+difference is observed.   For both AMR-Wind and Nalu-Wind, an
+approximately linear veer profile was observed until $z\approx$ 250m,
+at which point the wind direction remained constant until the
+inversion layer height.
+
+The computed TI and temperature profiles were observed to agree
+remarkably well between the LES codes. As shown in figure
+\ref{fig:CompareAMRvsNaluWind_TTI}, the stable ABL computed using
+AMR-Wind and Nalu-Wind both show a similar decay of turbulent kinetic
+energy with altitude $z$, and there is also little difference between
+the two temperature profiles $T(z)$.
+
+%%%%%%%%%%% Compare Nalu/AMR WS/WDir profiles %%%%%%%%%%%%%%%%%%%%%%%
+% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
+\begin{figure} %[hbt!]
   \centering
-  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}\\
-  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
-  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
-  \caption{Comparison of AMR-Wind and Nalu-Wind profiles. }
+  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_WS.png}
+  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_Wdir.png}\\
+  \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
+    AMR-Wind and Nalu-Wind velocity profiles.  The dashed horizontal
+    line corresponds to the measurement height z=20m. }
 \end{figure}
@@
 
+%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
+% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
+\begin{figure} %[hbt!]
+  \centering
+  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
+  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
+  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
+    and Nalu-Wind turbulence intensity and temperature profiles. The
+    dashed horizontal line corresponds to the measurement height
+    z=20m.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection*{Wind spectra and turbulent correlation}
+
+A comparison of the computed wind spectra $S_i(f)$ is shown in figure
+\ref{fig:CompareAMRvsNaluSpectra}.
+
+A comparison of the $R_{ij}$ correlation is shown in figure
+\ref{fig:CompareAMRvsNaluRij}.
+
 %%%%%%%%%%% Compare Nalu/AMR spectra %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Postprocessing/ABLSpectra/AMRWind_NaluWind_Spectra_Stable.ipynb
-\begin{figure}[hbt!]
-  \label{fig:CompareAMRvsNaluSpectra}
+\begin{figure} %[hbt!]
   \centering
-  \includegraphics[width=6.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Spectra_Stable_z20.png}
+  \includegraphics[width=7.0in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Spectra_Stable_z20.png}
 
-  \caption{Comparison of AMR-Wind and Nalu-Wind wind spectra at
-    z=20m. }
+  \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
+    and Nalu-Wind wind spectra at z=20m. }
 \end{figure}
@@
 % Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
-\begin{figure}[hbt!]
-  \label{fig:CompareAMRvsNaluRij}
+\begin{figure} %[hbt!]
   \centering
@@
 
-  \caption{Comparison of AMR-Wind and Nalu-Wind $\langle R_{ij}
+  \caption{\label{fig:CompareAMRvsNaluRij}
+    Comparison of AMR-Wind and Nalu-Wind $\langle R_{ij}
     \rangle$ correlation at z=20m. }
@@
 
-\subsection{ABL Physics}
+\subsubsection*{Computational efficiency}
+How much faster is AMR-Wind compared to Nalu-Wind?  \\
+\fxnote{PUT SOME NUMBERS HERE FROM MIKE}
+
+\subsection{Comparison of stable offshore ABL for different wind speeds and stabilities}
 
@@
 %%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
+\begin{table}[h]
 \caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
@@
   \hline
-  Velocity & $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
+  Index $i$& $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
   \hline

### 2020-12-01 Paper/methodology.tex
added an amrwind section

@@
 \subsubsection{AMR-Wind}
-\fxnote{Mike write this part}\\
-Describe AMR-Wind
+
+\fxnote{Do we want a github link reference for amr-wind? exawind?}\\
+
+As part of a suite of physics codes within the open-source project called ExaWind, 
+AMR-Wind enables more efficient and scalable simulations of wind power plants. 
+This is because it is built on top of the AMReX software framework which contains 
+all of the functionality needed to develop massively parallel, block-structured 
+adaptive mesh refinement (AMR) applications \cite{AMReX_JOSS}.
+Since AMR-Wind is limited to Cartesian block-structured grids it is specialized
+to handle atmospheric boundary layer physics and wind turbine wakes. 
+The block-structured grids enable more efficient algorithms such as 
+Multi-Level Multi-Grid (MLMG) \cite{AMReX_JOSS}
+and are well suited for next generation supercomputers that use GPU's.
+
+AMR-Wind solves the incompressible Navier-Stokes equations and is generalized to
+handle variable density and viscosity. Additionally scalar transport equations can be 
+solved such as potential temperature or turbulence models. The discretization in AMR-Wind
+is based on the approximate projection method used in IAMR \cite{almgren1998conservative} 
+and incflo \cite{sverdrup2018highly}. It is a semi-staggered scheme where the velocity and scalar 
+variables are located at cell centers and pressure is located at nodes. Pressure is also staggered
+in time so that pressure and the pressure gradient (located at cell centers) are at time $n+1/2$. 
+The time discretization is handled with a Crank Nicholson approach where the right hand side 
+of the system of equations is evaluated at time $n+1/2$. The advection term is handled explicitly
+using an upwind finite-volume method. There are multiple options
+within AMR-Wind, but in this paper only the high-order Godunov Piecewise Parabolic 
+method (PPM) is used \cite{Colella1984}. The advection terms are projected to face 
+centers at $n+1/2$ and are corrected using an exact MAC projection \cite{almgren1998conservative}
+which guarantees a divergence free flow. The diffusion terms can be handled explicitly, semi-implicitly, 
+or fully implicit and are the discretized using a second-order central difference formula. 
+For the simulations in this paper we use a fully implicit scheme as the variable viscosity 
+from the eddy viscosity may cause time step restrictions. After the scalar equations
+and the momentum equations are advanced in time a nodal projection is used to 
+approximately correct the velocity field to make it divergence free. Where the nodal projection
+is based on a node centered finite element method \cite{almgren1998conservative}.
+
+%IAMR paper \cite{almgren1998conservative}
+%AMReX \cite{AMReX_JOSS}
+%incflo \cite{sverdrup2018highly}
+%Godunov ppm \cite{Colella1984}
 

### 2020-12-01 Paper/results.tex
Adding more to paper

@@
 averaging.  In the current study, we compute the horizontally averaged
-correlation coefficient $\langle R_{ij}(\boldsymbol{\xi})\rangle$ by
+correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
 sampling over multiple points at the $z$=20m height, typically 100-150
 points, and averaging the result.  The longitudinal $\langle
-R_{ij}(\boldsymbol{\xi})\rangle$ was calculated by looking at
+R_{11}(\boldsymbol{\xi})\rangle$ was calculated by looking at
 separation vectors $\boldsymbol{\xi}$ in the streamwise direction
-while the lateral $\langle R_{ij}(\boldsymbol{\xi})\rangle$ used
+while the lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$ used
 separation distances $\boldsymbol{\xi}$ which were orthogonal to the
@@
   \caption{\label{fig:GridStudyRij} Calculation of the averaged
-    longitudinal and lateral $\langle R_{ij}(\boldsymbol{\xi})
+    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
     \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
@@
 length scale $L$.  This lengthscale can be calculated from $\langle
-R_{ij}(\boldsymbol{\xi}) \rangle$ via
+R_{11}(\boldsymbol{\xi}) \rangle$ via
 \begin{equation}
-  L = \int_0^\infty \langle R_{ij}(\xi) \rangle \: {\textrm d}\xi
+  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
 \end{equation}
@@
 \begin{table}
-\caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and Nalu-Wind} \centering
+\caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and
+  Nalu-Wind} \centering
 \begin{tabular}{cccccc}
@@
   \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
-    AMR-Wind and Nalu-Wind velocity profiles.  The dashed horizontal
-    line corresponds to the measurement height z=20m. }
+    AMR-Wind and Nalu-Wind velocity profiles for the stable 5 m/s
+    boundary layer. The dashed horizontal line corresponds to the
+    measurement height z=20m. }
 \end{figure}
@@
   \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
-    and Nalu-Wind turbulence intensity and temperature profiles. The
-    dashed horizontal line corresponds to the measurement height
-    z=20m.}
+    and Nalu-Wind turbulence intensity and temperature profiles for
+    the stable 5 m/s boundary layer. The dashed horizontal line
+    corresponds to the measurement height z=20m.}
 \end{figure}
@@
 
-\subsubsection*{Wind spectra and turbulent correlation}
+\subsubsection{Wind spectra and turbulent correlation}
 
-A comparison of the computed wind spectra $S_i(f)$ is shown in figure
-\ref{fig:CompareAMRvsNaluSpectra}.
+In addition to the mean profiles described above, we also examined the
+wind spectra and turbulent correlation statistics from both AMR-Wind
+and Nalu-Wind for the stable 5m/s case.  A comparison of the computed
+wind spectra $S_i(f)$ from both LES codes is shown in figure
+\ref{fig:CompareAMRvsNaluSpectra}.  At low frequencies, both AMR-Wind
+and Nalu-Wind predict similar spectral behavior, and both codes
+predict relatively similar spectral peaks for the $S_v$ and $S_w$
+spectra.  For the longitudinal spectra $S_u$, however, AMR-wind
+predicts a slightly lower the peak amplitude than Nalu-Wind.
 
-A comparison of the $R_{ij}$ correlation is shown in figure
+A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
+correlation coefficient is shown in figure
 \ref{fig:CompareAMRvsNaluRij}.
@@
   \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
-    and Nalu-Wind wind spectra at z=20m. }
+    and Nalu-Wind wind spectra at z=20m for the stable 5 m/s boundary
+    layer. }
 \end{figure}
@@
   \caption{\label{fig:CompareAMRvsNaluRij}
-    Comparison of AMR-Wind and Nalu-Wind $\langle R_{ij}
+    Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
     \rangle$ correlation at z=20m. }
@@
 
-\subsubsection*{Computational efficiency}
+\subsubsection{Computational efficiency}
 How much faster is AMR-Wind compared to Nalu-Wind?  \\
@@
 
+%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
+% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
+\begin{table}
+\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
+  wind speeds} \centering
+\begin{tabular}{cccccc}
+  \hline
+  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  L \\
+  \hline
+  AMRWind & 5m/s      & 0.048255 &  0.165552 &  0.157399  & 52.512434 \\
+  AMRWind & 10m/s     & 0.050580 &  0.160337 &  0.318941  &  57.233491 \\
+  AMRWind & 15m/s     & 0.055034 &  0.118190 &  0.510645  & 131.341634 \\
+  \hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsubsection{Horizontally averaged profiles}
+
+%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
+\begin{figure}[hbt!]
+  \label{fig:CompareAMRallWS}
+  \centering
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
+  \caption{Calculation of the wind spectra $S_i$ for LES of stable
+    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
+    vertical lines correspond to the maximum resolvable frequency
+    $f_{max}$ according to equation (\ref{eq:fmax}). }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%% Stable spectra, all Z figure %%%%%%%%%%%%%%%%%%%%%%%%%
 % Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
@@
   \caption{Calculation of the averaged longitudinal and lateral
-    $R_{ij}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
+    $R_{11}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
-\caption{\label{tab:StabilityStudyLscale} The calculated turbulent
-  integral lengthscale for each of atmospheric stabilities} \centering
-\begin{tabular}{ccccc}
-  \hline
-  Stability   & Wind speed & Longitudinal L [m] & Lateral L [m] \\
-  \hline
-  Stable      &   5 m/s  & 0.0           & 0.0        \\
-  Stable      &  10 m/s  & 0.0           & 0.0        \\
-  Stable      &  15 m/s  & 0.0           & 0.0        \\
-  Neutral     &   5 m/s  & 110.435741    & 15.245327  \\
-  Neutral     &  10 m/s  & 165.398368    & 20.634052  \\
-  Neutral     &  15 m/s  & 184.081967    & 22.961169  \\
-  Unstable    &   5 m/s  & 187.868710    & 270.538753 \\
-  Unstable    &  10 m/s  & 177.457502    & 215.027457 \\
-  Unstable    &  15 m/s  & 263.475309    & 67.999898  \\
-\hline
-\end{tabular}
-\end{table}
+%%%%%%%%%%% All stability, turbulent L figure %%%%%%%%%%%%%%%%%%%%
+% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
+\begin{figure}[hbt!]
+  \label{fig:AllStabilityLengthscale}
+  \centering
+  \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
+  \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
+  \caption{Calculation of the averaged longitudinal and lateral
+    lengthscale at $z$=20m for all ABL stability cases.}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% %%%%%%%%%%%%%%% All stability: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%
+%% % see  Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb
+%% \begin{table}
+%% \caption{\label{tab:StabilityStudyLscale} The calculated turbulent
+%%   integral lengthscale for each of atmospheric stabilities} \centering
+%% \begin{tabular}{ccccc}
+%%   \hline
+%%   Stability   & Wind speed & Longitudinal L [m] & Lateral L [m] \\
+%%   \hline
+%%   Stable      &   5 m/s  & 0.0           & 0.0        \\
+%%   Stable      &  10 m/s  & 0.0           & 0.0        \\
+%%   Stable      &  15 m/s  & 0.0           & 0.0        \\
+%%   Neutral     &   5 m/s  & 110.435741    & 15.245327  \\
+%%   Neutral     &  10 m/s  & 165.398368    & 20.634052  \\
+%%   Neutral     &  15 m/s  & 184.081967    & 22.961169  \\
+%%   Unstable    &   5 m/s  & 187.868710    & 270.538753 \\
+%%   Unstable    &  10 m/s  & 177.457502    & 215.027457 \\
+%%   Unstable    &  15 m/s  & 263.475309    & 67.999898  \\
+%% \hline
+%% \end{tabular}
+%% \end{table}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-01 Paper/methodology.tex
Add governing equations section

@@
 
+Large Eddy Simulations (LES) of the stable atmopsheric conditions described in
+Table~\ref{tab:CapeWindMeasurements} are performed using the open-source,
+ExaWind simulation environment\footnote{\url{https://github.com/exawind}}.
+ExaWind is a suite of high-fidelity modeling tools for analyzing complex
+microscale atmospheric boundary layer flows and wind farm flows. The present
+study uses two different incompressible computational fluid dynamic solvers
+available within the ExaWind suite --
+Nalu-Wind~\footnote{\url{https://github.com/exawind/nalu-wind}} and
+AMR-Wind~\footnote{\url{https://github.com/exawind/amr-wind}}. This section
+briefly describes the incompressible Navier-Stokes equations solved in the
+solvers, the specifics of the turbulence model and the wall shear stress
+formulation used to model the terrain, and the details of the numerical
+discretization of the two equations in the two codes.
+
 \subsection{LES formulation}
@@
 \subsubsection{Governing equations}
+Both CFD codes solve the incompressible form of Navier-Stokes equations with
+appropriate models for turbulence closure. Equation~\ref{eqn:ns-les} shows the
+continuity and momentum equations with all the terms necessary to model the
+atmospheric boundary layer problem. Term $\mathbf{I}$ represents the pressure
+gradient forces as a deviation from hydrostatic and horizontal mean gradient,
+term $\mathbf{II}$ represents the contribution from viscous and sub-filter scale
+stresses, term $\mathbf{III}$ represents the contribution from Coriolis forces
+due to earth's rotation, term $\mathbf{IV}$ represents the effects of buoyancy,
+and term $\mathbf{V}$ represents source terms necessary to drive the flow to a
+desired horizontal mean velocity at prescribed heights.
+
+\begin{align}
+  \frac{\partial \bar{\rho}} {\partial t} + \frac{\partial \bar{\rho} \widetilde{u_j}}{\partial x_j} & = 0, \nonumber\\
+  \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{u}_i\right) +
+  \frac{\partial}{\partial x_j} \left( \bar{\rho}\, \widetilde{u}_i \widetilde{u}_j \right) &=
+  - \underbrace{\frac{\partial p'}{\partial x_j} \delta_{ij}}_\mathbf{I}
+  - \underbrace{\frac{\partial \tau_{ij}}{\partial x_j}}_\mathbf{II}
+  - \underbrace{2\bar{\rho}\,\epsilon_{ijk}\,\Omega_j\widetilde{u_k}}_\mathbf{III}
+  + \underbrace{\left(\rho - \rho_\circ \right) g_i}_\mathbf{IV}
+  + \underbrace{S^{u}_{i}}_\mathbf{V} \label{eqn:ns-les}
+\end{align}
+
+For the simulations presented in this paper, the buoyancy term ($\mathbf{IV}$)
+is approximated using the Bousinessq model. The Bousinessq model ignores the
+effect of density gradients on inertia while retaining its effects on buoyancy.
+The density fluctuations governing the buoyancy effects are approximated as
+
+\begin{align*}
+  \frac{\rho}{\rho_\circ} \approx 1 - \beta \left( \theta - \theta_\circ \right)
+\end{align*}
+This leads to a forcing term that depends on potential temperature ($\theta$),
+the reference density $\rho_\circ = \bar{\rho}$, and thermal expansion
+coefficient $\beta \approx 1 / \theta_\circ$ as
+\begin{align}
+  \left(\rho - \rho_\circ \right) g_i = -\rho_\circ\, \beta\, g_i \left( \theta - \theta_\circ \right)
+\end{align}
+
+For ABL problems, the conservation of energy equation is usually written in
+terms of potential temperature as shown in Eq.~\ref{eqn:pot-temp-les}.
+\begin{align}
+  \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{\theta}\right) +
+  \frac{\partial}{\partial x_j} \left(\bar{\rho}\, \widetilde{u}_j \widetilde{\theta} \right) = - \frac{\partial}{\partial x_j} \hat{q}_j \label{eqn:pot-temp-les}
+\end{align}
+Under the assumption of ideal gas conditions and constant specific heat capacity
+$c_p$, the gradients in potential temperature are proportional to the gradients
+in absolute temperature, i.e.,
+\begin{align*}
+   \left[ \frac{\partial T}{\partial t}, \frac{\partial T}{\partial x}, \frac{\partial T}{\partial y} \right] =
+   \left( \frac{\bar{p}}{p_\circ} \right)^{\left(\frac{R}{c_p}\right)} \left[ \frac{\partial \theta}{\partial t}, \frac{\partial \theta}{\partial x}, \frac{\partial \theta}{\partial y} \right]
+\end{align*}
+Furthermore, ignoring the pressure and viscous work terms in
+Eq.~\ref{eqn:pot-temp-les}, for incompressible flows, it can be shown that
+solving the enthalpy equation is equivalent to solving the potential temperature
+equation. The enthalpy equation solved in Nalu-Wind for wind energy problems is
+shown below
+\begin{align}
+  \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{h}\right) +
+  \frac{\partial}{\partial x_j} \left(\bar{\rho}\, \widetilde{u}_j \widetilde{h} \right) = - \frac{\partial}{\partial x_j} q_j \label{eqn:enthalpy-les}
+\end{align}
+It is noted here that the terms $\hat{q}_j$ (Eq.~\ref{eqn:pot-temp-les}) and
+$q_j$ (Eq.~\ref{eqn:enthalpy-les}) are not equivalent and must be scaled
+appropriately. User can still provide the appropriate initial and boundary
+conditions in terms of potential temperature field. Under these assumptions and
+conditions, the resulting solution can then be interpreted as the variation of
+potential temperature field in the computational domain.
+
+The subgrid-scale kinetic energy ($k$) one-equation turbulence model
+(Eq.~\ref{eqn:ksgs-les}), based on Moeng~\cite{Moeng1984}, is used for
+LES turbulence closure.
+
+\begin{align}
+  \frac{\partial}{\partial t}\left(\bar{\rho} k \right) + \frac{\partial}{\partial x_j} \bar{\rho} k \widetilde{u_j} &= \frac{\partial}{\partial x_j} \left (2 \nu_t \frac{\partial k}{\partial x_j} \right) - 2 \nu_t \widetilde{S_{ij}} \widetilde{S_{ij}} + \frac{g}{\theta_\circ} \tau_{\theta_i} - C_{\epsilon} \frac{k^{3/2}}{l} \label{eqn:ksgs-les}
+\end{align}
+where
+\begin{align*}
+  C_\epsilon &= 0.93 & \nu_t &= C_\epsilon l \sqrt{k} \\
+  \tau_{\theta i} &= - 2\ \frac{\nu_t}{\mathrm{Pr}_t}\ \frac{\partial \widetilde{\theta}}{\partial x_i} & \mathrm{Pr}_t &= \left( 1 + \frac{2l}{\Delta} \right)^{-1} \\
+\end{align*}
+The choice of the length scale ($l$) depends on whether the stratification is positive
+or negative, based on the recommendation by Moeng~\cite{Moeng1984}, and is given
+by
+\begin{align*}
+  l =
+  \begin{cases}
+    \Delta = \sqrt{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 \\
+    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 \\
+  \end{cases}
+\end{align*}
+
+\begin{comment}
   \fxnote{Shreyas write this part.  Currently placeholder equations below.}\\
@@
   \end{align}
+\end{comment}
 
@@
 \subsubsection{Nalu-Wind}
-\fxnote{Shreyas write this part}\\
-Describe Nalu-Wind
+
+Nalu-Wind~\cite{SpragueAVR2020} is an open-source, wind-focused fork of the Nalu CFD
+code~\cite{Domino:2015}. The codebase heavily leverages the open-source Trilinos
+suite of numerical libraries~\cite{Heroux:2003}. Nalu-Wind uses an
+unstructured-grid, node-centered, finite-volume formulation for solving the incompressible
+Navier-Stokes equations. Two spatial discretization approaches are supported
+within the codebase -- the edge-based scheme and control-volume finite-element
+scheme. The edge-based scheme, used in the present study, is similar to the
+classical cell-centered finite volume formulation formulated on a dual volume
+surrounding the nodes of the mesh. The governing equations are discretized in
+time using a split-operator approach. Implicit backward difference formula
+(BDF2) timestepping algorithm with an approximate pressure projection
+scheme~\cite{Moen-Domino:2003} is used to advance the equations in time.
+Multiple Picard-style outer-loop iterations are employed within each timestep
+to minimize the errors introduced from split-operator approximations. Nalu-Wind
+comes equipped with a suite of Reynolds-Averaged Navier-Stokes (RANS), LES, and
+Detached Eddy Simulation (DES) turbulence models to resolve the disparate
+spatial and temporal scales encountered when modeling wind plant flows.
+
+Nalu-Wind heavily utilizes the Sierra Toolkit (STK) library~\cite{Edwards:2010}
+for managing the unstructured mesh data structures. The linear systems resulting
+from the discretized equations are solved using solvers available within the
+Belos and MueLu libraries within Trilinos. The momentum and scalar transport
+equations are solved using GMRES iterative solver with symmetric Gauss-Seidel
+(SGS) preconditioners. The elliptic pressure-Poisson equation is solved using
+GMRES solvers with a smoothed-aggregated algebraic multigrid preconditioner. The
+reader is referred to Sprague et al.~\cite{SpragueAVR2020} and
+Domino~\cite{Domino:2015} more more details.
+
+While the primary objective of Nalu-Wind within the ExaWind simulation suite is
+to support blade-resolved simulations of wind turbines, it comes equipped
+with all the physics models necessary for modeling atmospheric boundary flows.
+In the present work, the prognostic equation for temperature is solved using the
+enthalpy equation (Eq.~\ref{eqn:enthalpy-les}). The prognostic one-equation,
+subgrid-scale kinetic energy equation (Eq.~\ref{eqn:ksgs-les}) is used for LES
+turbulence closure. Two Picard iterations were employed within each timestep to
+minimize splitting errors and recover second-order accuracy in time.
 

### 2020-12-01 Paper/main.tex
Adding more to paper
Add governing equations section
Added Nate's section

@@
 \setlength\LTleft{0pt}
+\hypersetup{
+  colorlinks=true
+}
 
@@
 
-\fxnote{Mention study by \cite{wurps2020grid}.  Nate's piece goes here.}
+\subsection{Prevous work}
+
+\fxnote{Nate's piece goes here.  Edit and merge with above.}
+
+Stably stratified boundary layers, or SBL, commonly occur on clear nights over land, in polar regions, and over cold oceans.
+Given that wind turbines are likely to experience the SBL as part of the diurnal cycle, or as part of there general locale, it is of utmost import to model such conditions correctly.
+Large eddy simulation, or LES, of the SBL presents certain challenges compared to neutral and convective stability states, stemming primarily from small dominant eddy length scales and low turbulence intensity.
+These challenges require higher resolution grids and/or advanced subgrid scale (SGS) models.
+As such, LES research of the SBL has been slower to evolve than the other stability states.
+
+The first successful LES of the SBL was published by Mason and Derbyshire in 1990 \cite{Mason1990}.
+They used a strategy of simulating a near steady-state neutral stability turbulent simulation, then added a cooling-surface boundary to develop the stable ABL.
+They recorded a need for implausibly strong initial perturbations to sustain turbulence using the Smagorinsky SGS model.
+Brown et al.\ \cite{Brown1994} worked with Mason and Derbyshire to add stochastic backscatter to the SGS model, resulting in better agreement with surface layer observations.
+Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and one capped by an inversion, comparing two SGS models.
+He found significant improvements with the Sullivan SGS model, on par with the earlier backscatter model.
+In 1995, Derbyshire flew two measurement balloons, one in a heterogeneous location, another in a more idealized location, with the hope that the measurements would be useful for comparison to LES.
+He found significant variation in the critical Richardson number, and the temperature structure led him to state that complete comparison with LES had little point.
+Kemp and Thompson \cite{Kemp1996} used the same model as \cite{Brown1994} to study particle dispersion, but the LES code did not replicate an expected plume growth.
+Derbyshire wrote a review of SBL modeling along with future projections in 1999 \cite{Derbyshire1999}, with discussion of the importance of local Richardson number, a general statement that LES is a good supplement to SBL observations, and identification of a need to go to higher resolutions in SBL research.
+
+In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS model containing backscatter to favorably compare to the BASE measurements, showing that the SBL could reach a quasi steady-state.
+They also showed good agreement with the Nieustadt analytical model.
+In the same year, Saiki et al.
+\cite{Saiki2000} simulated an SBL with a strong capping inversion at z=500m, producing reasonable surface layer profiles and identifying a need for SBL specific SGS models.
+Beare and MacVean \cite{Beare2004} presented the first grid-focused work on LES of the SBL, using grids with deltas between 2m and 12.5m, finding significant variation between grid sizes.
+The inclusion of a backscatter model resulted in significant variation at a 6.25m resolution, but very little at a 2m resolution.
+Basu et al.
+\cite{Basu2005} published a set of turbulence statistics, measurements, and supporting LES simulations in support of the viability of Nieustadt's local scaling hypothesis under very stable conditions.
+Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range for which standard SGS models, using the Kolmogorov theory for dissipation, were valid for increasingly stable flows.
+They found the model to perform adequately for weakly stable, and some moderately stable flow regimes.
+
+An inter-comparison of LES simulations of the SBL was organized in 2006, the results of which are published in Beare et al.\ \cite{Beare2006}.
+Collectively, this is knows as the GABLS initiative, and involved simulating a moderately stable flow taken from Kosovic and Curry \cite{Kosovic2000}.
+Eleven codes were compared in all, and in general, grid deltas of less than 12.5m were found successful at maintaining resolved turbulence, and at grid deltas less than 3.125m showed little statistical change.
+The comparison also identified that Smagorinsky constants less than 0.2 were desirable, and that results became independent of SGS at 1m resolution.
+In the same year, Kumar et al.
+\cite{Kumar2006} successfully simulated an entire diurnal cycle with LES using a Lagrangian dynamic scale dependent SGS model.
+Stoll and Porte-Agel \cite{Stoll2007} compared three grid refinements and three scale dependent dynamic SGS models, showing that the Lagrangian and locally averaged models reproduced important flow features.
+The work of van Dop and Axelsen \cite{vanDop2007} provided even more evidence in support Nieuwstadt's local scaling hypothesis for SBLs.
+Chow and Zhou \cite{Chow2011} showed evidence that the Smagorinsky model is simply too dissipative for use in strongly stable flows.
+
+The scale dependent Lagrangian SGS model has been used by several researchers since 2011, including Lu and Porte-Agel \cite{Lu2011}, Huang and Bou-Zeid \cite{Huang2013}, Park et al.\ \cite{Park2014}, and Abkar and Porte-Agel \cite{Abkar2015}.
+Recent work in LES of the SBL includes Matheou \cite{Matheou2016} who explored a large parameter space using the Smagorinsky-Lilly SGS closure.
+Several researchers have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}.
+This year, Wurps et al.
+\cite{Wurps2020} provided a rigorous grid resolution study for the SBL, looking at mean flow, turbulence variables, and two-point correlations, using a dynamic SGS model that allows backscatter.
+They found grid requirements to be 2.5m, 10m, and 20m for stable, neutral, and convective boundary layers respectively.
+They also found Pope's resolution requirement ratio of resolved energy to total energy of $\gamma < 0.8$ to be too lax in many cases.
+They advocate looking at two point correlations in order to quantify flow structure size, which in turn provides a basis for choice of grid resolution.
+
+\subsection{Study objective and outline}
+
+The current paper is organized as follows.
 

### 2020-12-01 Paper/main.tex
Nate initial intro changes

@@
 
-In addition to these measurements, large eddy simulations (LES) have
+\subsection{Previous Simulation Work}
+
+In addition to these measurement campaigns, large eddy simulations (LES) have
 also been used to study ABL stability characteristics.  Recent work by
@@
 \cite{archer2016predominance} and showed the effects of surface
-heating on atmospheric stratification.  Additional LES computations
-\cite{sullivan2016turbulent} have also previously explored stable
-conditions of onshore boundary layers, such as the GABLS1 boundary
-layer \cite{beare2006intercomparison}.  However, a complete comparison
+heating on atmospheric stratification. LES of the stable ABL (SBL) presents 
+certain challenges compared to neutral and convective stability states, stemming 
+primarily from small dominant eddy length scales and low turbulence intensity. 
+These challenges require higher resolution grids and/or advanced subgrid 
+scale (SGS) models. As such, LES research of the SBL has been slower 
+to evolve than the other stability states.
+
+The first successful LES of the SBL was published by Mason and Derbyshire in 
+1990 \cite{Mason1990}. They used a strategy of simulating a near steady-state 
+neutral stability turbulent simulation, then added a cooling-surface boundary 
+to develop the stable ABL. They recorded a need for implausibly strong initial 
+perturbations to sustain turbulence using the Smagorinsky SGS model. Brown et 
+al.\ \cite{Brown1994} worked with Mason and Derbyshire to add stochastic backscatter 
+to the SGS model, resulting in better agreement with surface layer observations. 
+Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and 
+one capped by an inversion, comparing two SGS models. He found significant improvements 
+with the Sullivan SGS model, on par with the earlier backscatter model. Kemp and 
+Thompson \cite{Kemp1996} used the same model as \cite{Brown1994} to study particle 
+dispersion, but the LES code did not replicate an expected plume growth. Derbyshire 
+wrote a review of SBL modeling along with future projections in 1999 \cite{Derbyshire1999}, 
+noting the importance of local Richardson number and identifying a need to go 
+to higher resolutions in SBL research.
+
+In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS 
+model containing backscatter to favorably compare to the BASE measurements, showing that 
+the SBL could reach a quasi steady-state. They also showed good agreement with the Nieustadt 
+analytical model. In the same year, Saiki et al. \cite{Saiki2000} simulated an SBL with 
+a strong capping inversion at z=500m, producing reasonable surface layer profiles and 
+identifying a need for SBL specific SGS models. Beare and MacVean \cite{Beare2004} 
+presented the first grid-focused work on LES of the SBL, using grids with deltas 
+between 2m and 12.5m, finding significant variation between grid sizes. The inclusion 
+of a backscatter model resulted in significant variation at a 6.25m resolution, but 
+very little at a 2m resolution. Basu et al. \cite{Basu2005} published a set of 
+turbulence statistics, measurements, and supporting LES simulations in support 
+of the viability of Nieustadt's local scaling hypothesis under very stable 
+conditions. Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range 
+for which standard SGS models, using the Kolmogorov theory for dissipation, were 
+valid for increasingly stable flows. They found the model to perform adequately 
+for weakly stable, and some moderately stable flow regimes.
+
+An inter-comparison of LES simulations of the SBL was organized in 2006, the 
+results of which are published in Beare et al.\ \cite{Beare2006}. Collectively, 
+this is knows as the GABLS initiative, and involved simulating a moderately 
+stable flow taken from Kosovic and Curry \cite{Kosovic2000}. Eleven codes 
+were compared in all, wherein grid deltas of less than 12.5m were found to 
+successfully maintain resolved turbulence, grid deltas less than 3.125m 
+showed little statistical change, and results became independent of SGS 
+modeling at 1m resolution. In the same year, Kumar et al. \cite{Kumar2006} 
+successfully simulated an entire diurnal cycle with LES using a Lagrangian 
+dynamic scale dependent SGS model. This model has been used by several 
+researchers since 2011, including Lu and Porte-Agel \cite{Lu2011}, Huang 
+and Bou-Zeid \cite{Huang2013}, Park et al.\ \cite{Park2014}, and 
+Abkar and Porte-Agel \cite{Abkar2015}. Stoll and Porte-Agel \cite{Stoll2007} 
+compared three grid refinements and three scale dependent dynamic SGS models, 
+showing that the Lagrangian and locally averaged models reproduced important 
+flow features. The work of van Dop and Axelsen \cite{vanDop2007} provided 
+even more evidence in support Nieuwstadt's local scaling hypothesis for SBLs. 
+Chow and Zhou \cite{Chow2011} showed evidence that the Smagorinsky model is 
+simply too dissipative for use in strongly stable flows.
+
+More recent work in LES of the SBL includes Matheou \cite{Matheou2016} who 
+explored a large parameter space using the Smagorinsky-Lilly SGS 
+closure, as well as Sullivan et al.\ \cite{sullivan2016turbulent}. Several researchers 
+have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}. 
+This year, Wurps et al. \cite{Wurps2020} provided a rigorous grid resolution study for the SBL, 
+looking at mean flow, turbulence variables, and two-point correlations, using a dynamic 
+SGS model that allows backscatter. They found grid requirements to be 2.5m, 10m, and 20m 
+for stable, neutral, and convective boundary layers respectively. They advocate looking 
+at two point correlations in order to quantify flow structure size, which in turn 
+provides a basis for evaluating grid resolution. In all of the reviewed literature, SBL LES 
+has been run in the onshore context only, a complete comparison
 including offshore stable ABL conditions has yet to be completed.
-
-\subsection{Prevous work}
-
-\fxnote{Nate's piece goes here.  Edit and merge with above.}
-
-Stably stratified boundary layers, or SBL, commonly occur on clear nights over land, in polar regions, and over cold oceans.
-Given that wind turbines are likely to experience the SBL as part of the diurnal cycle, or as part of there general locale, it is of utmost import to model such conditions correctly.
-Large eddy simulation, or LES, of the SBL presents certain challenges compared to neutral and convective stability states, stemming primarily from small dominant eddy length scales and low turbulence intensity.
-These challenges require higher resolution grids and/or advanced subgrid scale (SGS) models.
-As such, LES research of the SBL has been slower to evolve than the other stability states.
-
-The first successful LES of the SBL was published by Mason and Derbyshire in 1990 \cite{Mason1990}.
-They used a strategy of simulating a near steady-state neutral stability turbulent simulation, then added a cooling-surface boundary to develop the stable ABL.
-They recorded a need for implausibly strong initial perturbations to sustain turbulence using the Smagorinsky SGS model.
-Brown et al.\ \cite{Brown1994} worked with Mason and Derbyshire to add stochastic backscatter to the SGS model, resulting in better agreement with surface layer observations.
-Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and one capped by an inversion, comparing two SGS models.
-He found significant improvements with the Sullivan SGS model, on par with the earlier backscatter model.
-In 1995, Derbyshire flew two measurement balloons, one in a heterogeneous location, another in a more idealized location, with the hope that the measurements would be useful for comparison to LES.
-He found significant variation in the critical Richardson number, and the temperature structure led him to state that complete comparison with LES had little point.
-Kemp and Thompson \cite{Kemp1996} used the same model as \cite{Brown1994} to study particle dispersion, but the LES code did not replicate an expected plume growth.
-Derbyshire wrote a review of SBL modeling along with future projections in 1999 \cite{Derbyshire1999}, with discussion of the importance of local Richardson number, a general statement that LES is a good supplement to SBL observations, and identification of a need to go to higher resolutions in SBL research.
-
-In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS model containing backscatter to favorably compare to the BASE measurements, showing that the SBL could reach a quasi steady-state.
-They also showed good agreement with the Nieustadt analytical model.
-In the same year, Saiki et al.
-\cite{Saiki2000} simulated an SBL with a strong capping inversion at z=500m, producing reasonable surface layer profiles and identifying a need for SBL specific SGS models.
-Beare and MacVean \cite{Beare2004} presented the first grid-focused work on LES of the SBL, using grids with deltas between 2m and 12.5m, finding significant variation between grid sizes.
-The inclusion of a backscatter model resulted in significant variation at a 6.25m resolution, but very little at a 2m resolution.
-Basu et al.
-\cite{Basu2005} published a set of turbulence statistics, measurements, and supporting LES simulations in support of the viability of Nieustadt's local scaling hypothesis under very stable conditions.
-Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range for which standard SGS models, using the Kolmogorov theory for dissipation, were valid for increasingly stable flows.
-They found the model to perform adequately for weakly stable, and some moderately stable flow regimes.
-
-An inter-comparison of LES simulations of the SBL was organized in 2006, the results of which are published in Beare et al.\ \cite{Beare2006}.
-Collectively, this is knows as the GABLS initiative, and involved simulating a moderately stable flow taken from Kosovic and Curry \cite{Kosovic2000}.
-Eleven codes were compared in all, and in general, grid deltas of less than 12.5m were found successful at maintaining resolved turbulence, and at grid deltas less than 3.125m showed little statistical change.
-The comparison also identified that Smagorinsky constants less than 0.2 were desirable, and that results became independent of SGS at 1m resolution.
-In the same year, Kumar et al.
-\cite{Kumar2006} successfully simulated an entire diurnal cycle with LES using a Lagrangian dynamic scale dependent SGS model.
-Stoll and Porte-Agel \cite{Stoll2007} compared three grid refinements and three scale dependent dynamic SGS models, showing that the Lagrangian and locally averaged models reproduced important flow features.
-The work of van Dop and Axelsen \cite{vanDop2007} provided even more evidence in support Nieuwstadt's local scaling hypothesis for SBLs.
-Chow and Zhou \cite{Chow2011} showed evidence that the Smagorinsky model is simply too dissipative for use in strongly stable flows.
-
-The scale dependent Lagrangian SGS model has been used by several researchers since 2011, including Lu and Porte-Agel \cite{Lu2011}, Huang and Bou-Zeid \cite{Huang2013}, Park et al.\ \cite{Park2014}, and Abkar and Porte-Agel \cite{Abkar2015}.
-Recent work in LES of the SBL includes Matheou \cite{Matheou2016} who explored a large parameter space using the Smagorinsky-Lilly SGS closure.
-Several researchers have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}.
-This year, Wurps et al.
-\cite{Wurps2020} provided a rigorous grid resolution study for the SBL, looking at mean flow, turbulence variables, and two-point correlations, using a dynamic SGS model that allows backscatter.
-They found grid requirements to be 2.5m, 10m, and 20m for stable, neutral, and convective boundary layers respectively.
-They also found Pope's resolution requirement ratio of resolved energy to total energy of $\gamma < 0.8$ to be too lax in many cases.
-They advocate looking at two point correlations in order to quantify flow structure size, which in turn provides a basis for choice of grid resolution.
 

### 2020-12-01 Paper/results.tex

@@
 %%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h!]
+\begin{table} %[h!]
 \caption{\label{tab:GridStudyLscale} The calculated turbulent integral
@@
   \hline
-  Nalu-wind coarse  &  10.0  & 36.43 m         & 0.0 m     \\
-  Nalu-wind medium  &   5.0  & 21.49 m         & 4.52 m    \\
-  Nalu-wind fine    &   2.5  & 25.25 m         & 5.92 m    \\
-% AMR-wind fine     &   2.5  & 27.689340 m     & 9.332672   \\
+  Nalu-wind coarse  &  10.0  & 36.4 m         & 0.0 m     \\
+  Nalu-wind medium  &   5.0  & 21.5 m         & 4.52 m    \\
+  Nalu-wind fine    &   2.5  & 25.3 m         & 5.92 m    \\
 \hline
@@
 
-\subsubsection{Wind spectra and turbulent correlation}
-
 In addition to the mean profiles described above, we also examined the
@@
 predicts a slightly lower the peak amplitude than Nalu-Wind.
-
-A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
-correlation coefficient is shown in figure
-\ref{fig:CompareAMRvsNaluRij}.
 
@@
 
-%%%%%%%%%%% Compare Nalu/AMR lengthscale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
-\begin{figure} %[hbt!]
-  \centering
-  \fxnote{UPDATE THIS FIGURE}\\
-  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Longitudinal.png}
-  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Lateral.png}
+%% A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
+%% correlation coefficient is shown in figure \ref{fig:CompareAMRvsNaluRij}.
 
-  \caption{\label{fig:CompareAMRvsNaluRij}
-    Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
-    \rangle$ correlation at z=20m. }
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% %%%%%%%%%%% Compare Nalu/AMR lengthscale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% % Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
+%% \begin{figure} %[hbt!]
+%%   \centering
+%%   \fxnote{UPDATE THIS FIGURE}\\
+%%   \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Longitudinal.png}
+%%   \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Lateral.png}
+
+%%   \caption{\label{fig:CompareAMRvsNaluRij}
+%%     Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
+%%     \rangle$ correlation at z=20m. }
+%% \end{figure}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+Using the results of the stable cases described in \ref{sec:CFDsetup},
+as well as the computations from the previous study in
+\cite{cheung2020large}, we can examine the influence of wind speed and
+stratification on offshore ABL behavior.  In this section we first
+compare the differences between the three stable ABL cases, and then
+compare their behavior with the previously computed neutral and
+unstable counterparts.
+
 \subsubsection{ABL integrated quantities}
-Describe integrated quantities
+From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
+15m/s, a number of quantities can be computed to compare with the
+measured targets from Archer et al \cite{archer2016predominance}.
+
+The Obukhov length $L_{Ob}$ can be calculated as
+\begin{equation}
+  L_{Ob} = -\frac{u_\tau^3 T_0}{\kappa g \langle \overline{w'T'} \rangle}
+\end{equation}
+where the $\kappa$=0.41 is the Kolmogorov constant, $g$ is the
+gravitational acceleration, and $\langle \overline{w'T'} \rangle$ is the
+horizontally and time-averaged temperature flux.  In this study we use
+the same classification guidelines as Archer et al
+\cite{archer2016predominance}, and identify cases where $100 < L_{Ob}
+< 500$ as ``stable'', and cases where $5 < L_{Ob}<100$ as ``very stable''.
 
@@
   wind speeds} \centering
-\begin{tabular}{cccccc}
+\begin{tabular}{ccccccc}
   \hline
-  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  L \\
+  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  $L_{Ob}$ & Stability \\
   \hline
-  AMRWind & 5m/s      & 0.048255 &  0.165552 &  0.157399  & 52.512434 \\
-  AMRWind & 10m/s     & 0.050580 &  0.160337 &  0.318941  &  57.233491 \\
-  AMRWind & 15m/s     & 0.055034 &  0.118190 &  0.510645  & 131.341634 \\
+  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m   & Very stable\\
+  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m   & Very stable\\
+  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m   & Stable \\
   \hline
@@
 
-\subsubsection{Horizontally averaged profiles}
+\subsubsection{Flow behavior and horizontally averaged profiles}
+
+%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
+\begin{figure}[hbt!]
+  \centering
+  \includegraphics[width=2.5in]{figures/snapshots/05ms/velh_mag_z20.png}
+  \includegraphics[width=2.5in]{figures/snapshots/05ms/velz_z20.png} \\
+
+  \includegraphics[width=2.5in]{figures/snapshots/10ms/velh_mag_z20.png}
+  \includegraphics[width=2.5in]{figures/snapshots/10ms/velz_z20.png} \\
+
+  \includegraphics[width=2.5in]{figures/snapshots/15ms/velh_mag_z20.png}
+  \includegraphics[width=2.5in]{figures/snapshots/15ms/velz_z20.png} \\
+  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
+    velocity and vertical velocity }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
+\begin{figure}[hbt!]
+  \centering
+  \includegraphics[height=2.0in]{figures/snapshots/05ms/velh_mag_side.png} \\
+
+  \includegraphics[height=2.0in]{figures/snapshots/10ms/velh_mag_side.png} \\
+
+  \includegraphics[height=2.0in]{figures/snapshots/15ms/velh_mag_side.png} \\
+
+  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
+    velocity and vertical velocity }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
-  \caption{Calculation of the wind spectra $S_i$ for LES of stable
-    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
-    vertical lines correspond to the maximum resolvable frequency
-    $f_{max}$ according to equation (\ref{eq:fmax}). }
+  \caption{Comparison of the horizontal wind speed and wind direction
+    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
+\begin{figure}[hbt!]
+  \label{fig:CompareAMRallTTI}
+  \centering
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
+  \caption{Comparison of the turbulence intensity and temperature
+    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
 \end{figure}

### 2020-12-01 Paper/results.tex

@@
 % Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
-\begin{figure} %[hbt!]
+\begin{figure} [hbt!]
   \centering
@@
 
-\subsubsection{ABL integrated quantities}
+\subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
 From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
 15m/s, a number of quantities can be computed to compare with the
-measured targets from Archer et al \cite{archer2016predominance}.
+measured targets from Archer et al \cite{archer2016predominance}.  In
+table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
+$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
+longitudinal lengthscale $L$, and stability classification for each of
+these three cases.  The TI values, calculated at the height $z$=20m
+fall within the target range of 4.5\% to 6.0\% for stable conditions
+from the Cape Wind measurements.  The calculated friction velocities
+are also similar to the values from the neutral offshore ABL
+calculations of \cite{cheung2020large}, where $u_\tau$ varied from
+0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.
 
-The Obukhov length $L_{Ob}$ can be calculated as
+The degree of stratification in each of the marine boundary layers can
+be quantified through the Obukhov length $L_{Ob}$, defined here as 
 \begin{equation}
@@
 where the $\kappa$=0.41 is the Kolmogorov constant, $g$ is the
-gravitational acceleration, and $\langle \overline{w'T'} \rangle$ is the
-horizontally and time-averaged temperature flux.  In this study we use
-the same classification guidelines as Archer et al
-\cite{archer2016predominance}, and identify cases where $100 < L_{Ob}
-< 500$ as ``stable'', and cases where $5 < L_{Ob}<100$ as ``very stable''.
+gravitational acceleration, $T_0$ is the reference temperature, and
+$\langle \overline{w'T'} \rangle$ is the horizontally and
+time-averaged temperature flux.  In this study we adopt the same
+classification guidelines as Archer et al
+\cite{archer2016predominance}, and identify boundary layer cases where
+$100 < L_{Ob} < 500$ as ``stable'', and cases where $5 < L_{Ob}<100$
+as ``very stable''.  From the values listed in table
+\ref{tab:CompareAMRallWS}, we find that the lower wind speeds are
+``very stable'', while the highest 15 m/s wind speed is classified as
+``stable''.  This is consistent with the measured Cape Wind
+distributions, where very stable conditions are more frequent than
+stable conditions at lower wind speeds, and gradually disappear beyond
+13 m/s (c.f. figure 5b in \cite{archer2016predominance}).
 
@@
   wind speeds} \centering
-\begin{tabular}{ccccccc}
+\begin{tabular}{cccccccc}
   \hline
-  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  $L_{Ob}$ & Stability \\
+  Code & Wind speed   & TI     & $\alpha$& $u_\tau$ & Obukhov $L_{Ob}$ & Longitudinal $L$ & Stability \\
   \hline
-  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m   & Very stable\\
-  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m   & Very stable\\
-  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m   & Stable \\
+  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m & 27.7 m  & Very stable\\
+  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m & 29.6 m  & Very stable\\
+  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m & 43.8 m  & Stable \\
   \hline
@@
 
+The qualitative behavior of the stable boundary layers can be seen
+through snapshots of the flow taken from each of the simulations.  In
+figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
+horizontal and vertical velocities for each of the three cases at the
+z=20m measurement height are shown.  The largest difference can be
+seen in the size of the flow structures between the very unstable and
+stable cases.  Longer streaks are evident in the 15 m/s case compared
+to the 5 m/s and 15 m/s cases, which is consistent with the nearly
+50\% larger integral lengthscale $L$ given in table
+\ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
+are also evident in \ref{fig:SnapshotsZ20}.  At higher wind speeds the
+magnitude of the vertical $w'$ fluctuations increase, which plays a
+strong role in the growth the boundary layer.
+
 %%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \includegraphics[width=2.5in]{figures/snapshots/05ms/velh_mag_z20.png}
-  \includegraphics[width=2.5in]{figures/snapshots/05ms/velz_z20.png} \\
+  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
+  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
+  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20.png} \\
 
-  \includegraphics[width=2.5in]{figures/snapshots/10ms/velh_mag_z20.png}
-  \includegraphics[width=2.5in]{figures/snapshots/10ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
+  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20.png} \\
 
-  \includegraphics[width=2.5in]{figures/snapshots/15ms/velh_mag_z20.png}
-  \includegraphics[width=2.5in]{figures/snapshots/15ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
+  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20.png} \\
   \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
-    velocity and vertical velocity }
+    velocity and vertical velocity, taken at t=20,000 seconds of the
+    simulations at height z=20m.}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This observation can also be seen in images taken along the flow
+direction $\theta=225^\circ$, as shown in figure
+\ref{fig:SnapshotsSide}.  At the time t=20,000 seconds, the growth the
+of 15 m/s stable boundary layer is considerably larger than the very
+stable 5 m/s and 10 m/s cases, and has nearly reached the inversion
+layer height.  To reach the same level of boundary layer growth, the
+very stable ABL cases would require longer simulation times, possibly
+longer than the nighttime conditions measured experimentally.
 
@@
   \centering
-  \includegraphics[height=2.0in]{figures/snapshots/05ms/velh_mag_side.png} \\
+  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
+  \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\
 
-  \includegraphics[height=2.0in]{figures/snapshots/10ms/velh_mag_side.png} \\
+  \includegraphics[height=2.5in]{figures/snapshots/10ms/velh_mag_side.png} \\
 
-  \includegraphics[height=2.0in]{figures/snapshots/15ms/velh_mag_side.png} \\
+  \includegraphics[height=2.5in]{figures/snapshots/15ms/velh_mag_side.png} \\
 
   \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
-    velocity and vertical velocity }
+    velocity, taken at t=20,000 seconds along the wind direction. }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Horizontally averaged flow profiles shown in figures
+\ref{fig:CompareAMRallWS} and \ref{fig:CompareAMRallTTI} provide a
+more quantitative assessment of the ABL evolution.  The rapid growth
+of the 15 m/s stable case leads to strong shear throughout the
+boundary layer up to the inversion height, while the very stable 5 m/s
+and 10 m/s cases showed minimal shear at higher elevations.  The
+change in wind direction is also indicative of the boundary layer
+penetration.  Approximately linear veer profiles are visible up to
+heights of $z\approx$250 m and $z\approx$350 m for the 5 m/s and 10
+m/s cases, respectively, while the linear veer is present in the 15
+m/s stable case up to $z$=650m.
+
+The behavior of the TI and temperature profiles in figure
+\ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
+discussed above.  Despite all cases reaching a similar TI levels at
+$z$=20m, the turbulence decays at different rates for each case until
+reaching the top of the boundary layer.  The effect of the different
+surface temperature changes is also visible in the horizontally
+averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
+similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
+and each similar temperatures at the ocean surface.  However, the
+cooling effect in the very unstable 10 m/s case is limited to $z$<350
+m, similar to the veer and turbulence profiles.
+
+%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
+% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
+\begin{figure}[hbt!]
+  \centering
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
+  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
+    wind speed and wind direction profile for the stable 5m/s, 10m/s,
+    and 15m/s boundary layers. }
 \end{figure}
@@
 \begin{figure}[hbt!]
-  \label{fig:CompareAMRallWS}
   \centering
-  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
-  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
-  \caption{Comparison of the horizontal wind speed and wind direction
-    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
+  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
+  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
+    intensity and temperature profile for the stable 5m/s, 10m/s, and
+    15m/s boundary layers. }
 \end{figure}
@@
 
-%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
-% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
-\begin{figure}[hbt!]
-  \label{fig:CompareAMRallTTI}
-  \centering
-  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
-  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
-  \caption{Comparison of the turbulence intensity and temperature
-    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% \subsubsection{Wind spectra and turbulence statistics}
 
-\subsubsection{Wind spectra and turbulence statistics}
+%% The Kaimal model for spectra \cite{kaimal1973turbulence,
+%%   cheynet2017spectral} for neutral atmospheric conditions:
+%% \begin{equation}
+%%   \label{eq:kaimal}
+%%   \frac{fS_i}{u_\tau^2} = \frac{a_i(fz/\bar{U})}{\left(1+b_i(fz/\bar{U})^{\alpha_i}\right)^{\beta_i}}
+%% \end{equation}
 
-The Kaimal model for spectra \cite{kaimal1973turbulence,
-  cheynet2017spectral} for neutral atmospheric conditions:
-\begin{equation}
-  \label{eq:kaimal}
-  \frac{fS_i}{u_\tau^2} = \frac{a_i(fz/\bar{U})}{\left(1+b_i(fz/\bar{U})^{\alpha_i}\right)^{\beta_i}}
-\end{equation}
+%% %%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% \begin{table}[h]
+%% \caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
+%% \centering
+%% \begin{tabular}{ccccc}
+%%   \hline
+%%   Index $i$& $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
+%%   \hline
+%%   $u$      & 105.0 & 33.0  & 1           & 5/3  \\
+%%   $v$      &  17.0 &  9.5  & 1           & 5/3  \\
+%%   $w$      &   2.1 &  5.3  & 5/3         &   1  \\
+%% \hline
+%% \end{tabular}
+%% \end{table}
 
-%%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
-\caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
-\centering
-\begin{tabular}{ccccc}
-  \hline
-  Index $i$& $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
-  \hline
-  $u$      & 105.0 & 33.0  & 1           & 5/3  \\
-  $v$      &  17.0 &  9.5  & 1           & 5/3  \\
-  $w$      &   2.1 &  5.3  & 5/3         &   1  \\
-\hline
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%% Stable spectra, all Z figure %%%%%%%%%%%%%%%%%%%%%%%%%
-% Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
-\begin{figure}[hbt!]
-  \label{fig:ABLSpectra_AllZ}
-  \centering
-  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
-  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
-  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
-  \caption{Calculation of the wind spectra $S_i$ for LES of stable
-    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
-    vertical lines correspond to the maximum resolvable frequency
-    $f_{max}$ according to equation (\ref{eq:fmax}). }
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% %%%%%%%%%%% Stable spectra, all Z figure %%%%%%%%%%%%%%%%%%%%%%%%%
+%% % Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
+%% \begin{figure}[hbt!]
+%%   \label{fig:ABLSpectra_AllZ}
+%%   \centering
+%%   \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
+%%   \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
+%%   \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
+%%   \caption{Calculation of the wind spectra $S_i$ for LES of stable
+%%     5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
+%%     vertical lines correspond to the maximum resolvable frequency
+%%     $f_{max}$ according to equation (\ref{eq:fmax}). }
+%% \end{figure}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsubsection{Comparison with neutral and unstable conditions}
+
+Strong differences based on the atmospheric stratification can also be
+seen when we compare the stable ABL cases with the neutral and
+unstable counterparts from \cite{cheung2020large}.  In the previous
+study, both neutral and unstable offshore boundary layer cases were
+considered at the same 5 m/s, 10 m/s and 15 m/s wind speeds.  Similar
+to the findings in \ref{sec:stableABLStats}, the 5 m/s and 10 m/s
+unstable cases were classified as ``very unstable'', while the 15 m/s
+was identified as ``stable'' based on the Obukhov length scale.
+
+The impact of the stability on the turbulent structures can be seen
+through the correlation statistics and calculated lengthscales in
+figure \ref{fig:AllStabilityRij} and
+\ref{fig:AllStabilityLengthscale}.  The large disparity between the
+size of the turbulent structures in the stable and neutral or unstable
+cases is immediately evident from the calculated $\langle
+R_{11}(\boldsymbol{\xi})\rangle$ coefficients.  The longitudinal
+lengthscales for the unstable ABL cases can also be an order of
+magnitude larger than the stable ABL cases.  The large lateral
+lengthscales for the very unstable ABL cases, compared to the lateral
+lengthscales for the neutral and stable cases, is also worth noting.
+For the 5 m/s and 10 m/s very unstable ABL cases, the lateral
+dimensions of the turbulent structures are similar to the longitudinal
+lengthscale.  This is consistent with the large convective structures
+which develops in those cases.  For the unstable 15 m/s case, the
+lateral lengthscales was closer to neutral and stable cases.
 
@@
 \begin{figure}[hbt!]
-  \label{fig:AllStabilityRij}
   \centering
+  \fxnote{Fix legend and line styles} \\
   \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
   \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
-  \caption{Calculation of the averaged longitudinal and lateral
-    $R_{11}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
+  \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
+    longitudinal and lateral $R_{11}(\xi)$ coefficient at $z$=20m for
+    all ABL stability cases.}
 \end{figure}
@@
 \begin{figure}[hbt!]
-  \label{fig:AllStabilityLengthscale}
   \centering
+  \fxnote{Fix legend and marker styles} \\
   \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
   \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
-  \caption{Calculation of the averaged longitudinal and lateral
-    lengthscale at $z$=20m for all ABL stability cases.}
+  \caption{ \label{fig:AllStabilityLengthscale} Calculation of the
+    averaged longitudinal and lateral lengthscale at $z$=20m for all
+    ABL stability cases.}
 \end{figure}

### 2020-12-01 Paper/methodology.tex
Fix typo in formula
Editing paper details

@@
 \section{Methodology}
-Write something about what we're comparing with, the codes we're
-using, and how we set up the simulations.
+\fxnote{Write something about what we're comparing with, the codes we're
+using, and how we set up the simulations.}
 
@@
 \subsection{Computational methodology}
-Provide a general description of the LES codes that we use.
+%Provide a general description of the LES codes that we use.
 
@@
   \begin{cases}
-    \Delta = \sqrt{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 \\
+    \Delta = \sqrt[3]{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 \\
     0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 \\
@@
 
-\fxnote{Do we want a github link reference for amr-wind? exawind?}\\
+% \fxnote{Do we want a github link reference for amr-wind? exawind?}\\
 
@@
 
-\subsection{Computational setup}
+\subsection{\label{sec:CFDsetup}Computational setup}
 % \fxnote{Domains, grids, boundary conditions}

### 2020-12-01 Paper/results.tex

@@
 $L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
-required to capture the lateral scales.  Based on this longitudinal
-length scale, we also determined the overall domain size necessary for
-stable ABL calculations.  A minimum domain of 750m $\times$ 750m in
-the horizontal directions was used in all Nalu-Wind and AMR-Wind LES
-calculations, which provided sufficient space for the largest
-turbulent structures to develop and evolve without interference from
-the boundaries or other structures.
+required to capture the lateral scales.
+
+Based on this longitudinal length scale, we also determined the
+overall domain size necessary for stable ABL calculations.  To provide
+sufficient space to ensure development and decorrelation of turbulent
+structures, domain sizes of approximately 10 times the longitudinal
+lengthscale is recommended.  However, the inclusion of sample probes
+with sufficient separation distance to accurately calculate $\langle
+R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
+requirements.  Assuming the longitudinal length scales on the order of
+30 m, we estimated a minimum domain size of 750m $\times$ 750m in the
+horizontal directions for both the Nalu-Wind and AMR-Wind LES
+calculations.
 
@@
   \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
-    longitudinal and lateral $R_{11}(\xi)$ coefficient at $z$=20m for
-    all ABL stability cases.}
+    longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$
+    coefficient at $z$=20m for all ABL stability cases.}
 \end{figure}

### 2020-12-01 Paper/results.tex
copied over new plots and updated results.tex

@@
   \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
-  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20_samelimits.png}
+  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\
 
-  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20_samelimits.png}
+  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20_samelimits.png} \\
 
-  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20_samelimits.png}
+  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20_samelimits.png} \\
   \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal

### 2020-12-01 Paper/main.tex
updated ack

@@
 U.S. Department of Energy (DOE) under Contract No. DE-AC36-
-08GO28308. M. Brazell was partially funded by the Exascale Computing
+08GO28308. M. Brazell was funded by the Exascale Computing
 Project (17-SC-20-SC), a collaborative effort of two DOE organizations

### 2020-12-02 Paper/main.tex
Update paper sections

--- 2020-12-01 Paper/main.tex
@@
 \author{
-  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
+  Shreyas Ananthan\footnote{Researcher V, High-Performance Algorithms and Complex Fluids, AIAA Member},
   Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
@@
 $f$       & Frequency \\
+$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
+$f_{Ny}$   & Nyquist frequency \\
 $L$       & Turbulent integral length scale \\
@@
 \section{Introduction}
-\fxnote{Update this introduction.}
+%\fxnote{Update this introduction.}
 
@@
 
-\subsection{Study objective and outline}
-
-The current paper is organized as follows.
+\subsection{Objectives}
+In the current study on stable marine boundary layers, we aim to build
+on the previous work in the literature and complete several
+objectives.  First, a series of stable boundary layer conditions will
+be computed using the Exawind solvers which match the measurements of
+Archer et al \cite{archer2016predominance}.  The behavior of the
+stable boundary layers, including mean flow quantities and turbulent
+statistics, are examined and compared to the neutral and unstable
+cases computed in \cite{cheung2020large}.  Secondly, we examine the
+domain and mesh requirements necessary to capture the turbulent scales
+for the stable offshore boundary layers.  Finally, two LES solvers
+within the Exawind project are compared in this study: the
+unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
+structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
+used to calculate the same stable boundary layer, and the relative
+differences between the codes are reported.
 
@@
 
-\section*{Appendix}
+%% \section*{Appendix}
 
-An Appendix, if needed, should appear before the acknowledgments.
+%% An Appendix, if needed, should appear before the acknowledgments.
 

### 2020-12-02 Paper/results.tex
Update paper sections

--- 2020-12-01 Paper/results.tex
@@
   \centering
-  \fxnote{remove AMR-Wind results from graphs}\\
   \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
@@
   \centering
-  \fxnote{remove AMR-Wind results from graphs}\\
   \includegraphics[width=2.5in]{figures/GridStudy_Rij_Longitudinal.png}
@@
 
-Similar conclusions can be drawn by examining the turbulent integral
-length scale $L$.  This lengthscale can be calculated from $\langle
-R_{11}(\boldsymbol{\xi}) \rangle$ via
+Additional information about the mesh and domain requirements can be
+drawn by examining the turbulent integral length scale $L$.  This
+lengthscale can be calculated from $\langle R_{11}(\boldsymbol{\xi})
+\rangle$ via
 \begin{equation}
@@
   \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\
 
   \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20_samelimits.png} \\
 
   \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20.png} \\
+  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20_samelimits.png} \\
   \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal

### 2020-12-02 Paper/results.tex
Fix typo and notes
added amr-wind timings still need nalu-wind timings

@@
 \subsubsection{Computational efficiency}
-How much faster is AMR-Wind compared to Nalu-Wind?  \\
-\fxnote{PUT SOME NUMBERS HERE FROM MIKE}
+
+For the 5 m/s SBL case AMR-Wind had a median time of 2.66 seconds per time step.
+This means the entire simulation took about 6 hours to simulate 20k seconds 
+of physical time. For this case a total of $288\times 288 \times 384$ cells were used 
+which were solved in parallel using 972 MPI ranks. Simulations were carried out NREL's 
+Eagle supercomputer and AMR-Wind was compiled using Intel 2018.
+Typically on CPU's we see a strong scaling limit at around 15k cells per MPI rank. 
+But for this case we used 32,768 cells per MPI rank which is about half the strong scaling limit.
+The time per degree of freedom for AMR-Wind is
+\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-5}\]
+where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
+the total number of degrees of freedom (for AMR-Wind we are using the number of cells).
+This value allows us to compare speed relative to Nalu-Wind when using a different
+grid and number of MPI ranks, where a smaller value means a faster time to solution.
+
+In comparison the same case for Nalu-Wind takes x seconds per time step which
+takes a total of x*4*20000/3600 hours to complete the simulation. This simulation was carried out 
+on z MPI ranks on a grid that contains $400\times 400 \times 400$ cells. The equivalent
+time per time step for Nalu-Wind is \fxnote{insert nalu-wind number here and x above}
 
@@
 and each similar temperatures at the ocean surface.  However, the
-cooling effect in the very unstable 10 m/s case is limited to $z$<350
+cooling effect in the very stable 10 m/s case is limited to $z$<350
 m, similar to the veer and turbulence profiles.
@@
   \centering
-  \fxnote{Fix legend and line styles} \\
   \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
@@
   \centering
-  \fxnote{Fix legend and marker styles} \\
   \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}

### 2020-12-02 Paper/results.tex
oops used the wrong time per time step

@@
 
-For the 5 m/s SBL case AMR-Wind had a median time of 2.66 seconds per time step.
+For the 5 m/s SBL case AMR-Wind had a median time of 0.266 seconds per time step.
 This means the entire simulation took about 6 hours to simulate 20k seconds 
@@
 The time per degree of freedom for AMR-Wind is
-\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-5}\]
+\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-6}\]
 where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is

### 2020-12-02 Paper/main.tex
small typo
Added conclusion

@@
 \section{Conclusion}
-Put conclusion here.
+In this study we have simulated the stable offshore boundary layer
+matching the characteristics of measurements from Nantucket Sound in
+the Northeastern US.  Three cases with wind speeds of 5 m/s, 10 m/s,
+and 15 m/s were selected, and simulations were performed using the
+ExaWind codes to match the TI and stability levels observed at from
+the Cape Wind platform.  When examining the effect of stratification
+using the Obukhov length, differences in the ABL behavior were seen
+bewteen the very stable boundary layer cases (5 m/s and 10 m/s), and
+the stably stratified case (15 m/s).  The very stable cases had
+shorter turbulent structures and less growth in the boundary layer
+compared to the 15 m/s case.  The behavior of the three stable
+boundary layers was also compared to the neutral and unstable cases
+studied in \cite{cheung2020large}.  As expected, the turbulent
+structures in all stable cases were noticeably smaller than in the
+neutral and unstable boundary layers.
+
+In addition to these simulations, we also examined the domain and mesh
+requirements necessary for the stable offshore boundary layers
+considered here.  Based on the calculated turbulent integral
+lengthscale, horizontal domain sizes of 750m $\times$ 750m were found
+to be necessary for these simulations.  Various mesh resolutions were
+also considered for the stable runs, and it was determined that the
+finest resolution of $dx$=2.5m was able to resolve the longitudinal
+length scales and highest temporal frequencies, but inadequate for
+resolving the turbulence in the lateral direction.  Further study is
+warranted to comprehensively determine the impact of stable
+stratification on the required mesh resolution.
+
+Lastly, a comparison of the ExaWind solvers Nalu-Wind and AMR-Wind was
+conducted using the stable offshore boundary layer at 5 m/s.  The mean
+statistics were found to agree well between the two LES codes.  Small
+differences were found in wind profiles at higher elevations and for
+the peak $S_u$ spectra, and excellent matches were observed for the
+averaged veer, temperature, and TI profiles.
 
@@
 
-The authors wish to acknowlege the contributions from M. Churchfield
+The authors wish to acknowledge the contributions from M. Churchfield
 and S. Yellapantula for their development of the LES boundary

### 2020-12-02 Paper/results.tex
fixed a few typos

@@
 The time per degree of freedom for AMR-Wind is
-\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-6}\]
+\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-6} [s]\]
 where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
@@
 on z MPI ranks on a grid that contains $400\times 400 \times 400$ cells. The equivalent
-time per time step for Nalu-Wind is \fxnote{insert nalu-wind number here and x above}
+time per degree of freedom for Nalu-Wind is \fxnote{insert nalu-wind number here and x above}
 

### 2020-12-02 Paper/main.tex
Added abstract

@@
 \begin{abstract}
-Put abstract here
+  In this work we investigate the behavior of stable marine boundary
+  layers located near the coast of the Northeastern United States.
+  Using the ExaWind LES codes, three stable atmospheric conditions
+  were chosen to match the Cape Wind measurements of Archer \emph{et
+    al} with wind speeds of 5 m/s, 10 m/s, and 15 m/s.  The behavior
+  of the stable boundary layers, including mean flow quantities and
+  turbulent statistics, are examined and compared to previous
+  computations of the neutral and unstable offshore boundary layer at
+  the same location.  This study also examines the domain and mesh
+  requirements necessary to capture the turbulent scales for the
+  stable offshore boundary layers.  Finally, we compare solutions
+  computed using both Nalu-Wind and AMR-Wind solvers, and report on
+  their relative accuracy and performance in this study.
+
 \end{abstract}

### 2020-12-02 Paper/methodology.tex
Update paper sections
Add wall model description

@@
 \section{Methodology}
-\fxnote{Write something about what we're comparing with, the codes we're
-using, and how we set up the simulations.}
+%%\fxnote{Write something about what we're comparing with, the codes we're
+%%using, and how we set up the simulations.}
 
@@
   \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
-  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u' + v'v' + w'w'}
+  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u'} + \overline{v'v'} + \overline{w'w'}
       \right)}}{\overline{U}_{horiz}}
@@
 \fxnote{Ganesh write this part}\\
-What we implemented in terms of the lower boundary condition.
+The sub-filter scale stresses are specified at the terrain boundary following
+Moeng~\cite{Moeng1984} as
+\begin{align}
+ (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{S_1 \average{\widetilde{u}_1} + \average{S_1} (\widetilde{u}_1 - \average{\widetilde{u}_1} ) }{ \average{S_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
+ (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{S_1 \average{\widetilde{v}_1} + \average{S_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{S_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } \\
+  (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{S_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{S_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{S_1} ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) },
+\end{align}
+where all quantities with the subscript 1 are values at the first vertical grid
+level, $S_1$ is the resolved wind speed at the first grid level and
+$\average{f}$ represents the horizontal planar average of $f$. The mean
+sub-filter stresses are computed using Monin-Obukhov similarity
+law~\cite{Etling1996}. The formulation for the potential temperature flux could
+potentially experience a singularity when the mean resolved potential
+temperature at the first grid level $\average{\widetilde{\theta}_1}$ crosses the
+reference temperature $\theta_{\circ}$. Hence the model for the sub-filter
+potential temperature flux is reformulated using the Monin-Obukhov similarity
+law as
+\begin{equation}
+(\tau_{\theta z})_0 = \left ( \frac{u_{\tau} \kappa}{ \phi_h} \right ) \frac{S_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{S_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{S_1} },
+\end{equation}
+where $\phi_h$ is the non-dimensional potential temperature gradient from
+Monin-Obukhov similarity law~\cite{Etling1996}.
 

### 2020-12-02 Paper/results.tex
Removed some fxnotes
Add nalu-wind timing results

@@
 
-In comparison the same case for Nalu-Wind takes x seconds per time step which
-takes a total of x*4*20000/3600 hours to complete the simulation. This simulation was carried out 
-on z MPI ranks on a grid that contains $400\times 400 \times 400$ cells. The equivalent
-time per degree of freedom for Nalu-Wind is \fxnote{insert nalu-wind number here and x above}
+In comparison the same case for Nalu-Wind takes 3.404363 seconds per time step which
+takes a total of 113.48 hours to complete the simulation. This simulation was carried out
+on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
+time per degree of freedom for Nalu-Wind is $1.032 \times 10^{-4}$ s.
 
@@
   \centering
-  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
+  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
   \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
@@
   \centering
-  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
+  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
   \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\

### 2020-12-02 Paper/methodology.tex

@@
 \subsubsection{\label{sec:wallmodelBC}Lower wall model BC}
-\fxnote{Ganesh write this part}\\
 The sub-filter scale stresses are specified at the terrain boundary following

### 2020-12-03 Paper/results.tex
Added tikZ image labels

@@
 In comparison the same case for Nalu-Wind takes 3.404363 seconds per time step which
-takes a total of 113.48 hours to complete the simulation. This simulation was carried out
+takes a total of 75.65 hours to complete the simulation. This simulation was carried out
 on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
@@
   %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
-  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\
+  \begin{tikzpicture}
+    % 5 m/s plots
+    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
+         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
+    \node[align=left] at (1in, 4.50in){(a) horizontal vel, 5 m/s};
+    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
+         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
+    \node[align=left] at (4.25in, 4.50in){(b) vertical vel, 5 m/s};
 
-  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20_samelimits.png} \\
+    % 10 m/s plots    
+    \node[anchor=south west, inner sep=0](image) at (0in,2.25in)
+         {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
+    \node[align=left] at (1in, 2.25in){(c) horizontal vel, 10 m/s};
+    \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
+         {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
+    \node[align=left] at (4.25in, 2.25in){(d) vertical vel, 10 m/s};
 
-  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
-  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20_samelimits.png} \\
+    % 15 m/s plots
+    \node[anchor=south west, inner sep=0](image) at (0in,0in)
+         {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
+    \node[align=left] at (1in, 0in){(e) horizontal vel, 15 m/s};
+    \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
+         {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
+    \node[align=left] at (4.25in, 0in){(f) vertical vel, 15 m/s};
+
+  \end{tikzpicture}
   \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
     velocity and vertical velocity, taken at t=20,000 seconds of the
-    simulations at height z=20m.}
+    simulations at height z=20m, for the AMR-Wind calculation of the
+    stable 5 m/s, 10 m/s, and 15 m/s ABL. }
 \end{figure}
@@
   \centering
-  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
-  \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\
+  \begin{tikzpicture}         
+    \node[anchor=south west, inner sep=0](image) at (0,0in)
+         {\includegraphics[height=2.5in]{figures/snapshots/15ms/velh_mag_side.png}};
+    \node[align=left] at (2.5in, 0){(c) AMR-Wind stable, 15 m/s};
 
-  \includegraphics[height=2.5in]{figures/snapshots/10ms/velh_mag_side.png} \\
+    \node[anchor=south west, inner sep=0](image) at (0,2.5in)
+         {\includegraphics[height=2.5in]{figures/snapshots/10ms/velh_mag_side.png}};
+    \node[align=left] at (2.5in, 2.5in){(b) AMR-Wind stable, 10 m/s};
 
-  \includegraphics[height=2.5in]{figures/snapshots/15ms/velh_mag_side.png} \\
+    \node[anchor=south west, inner sep=0](image) at (0,5.0in)
+         {\includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png}};
+    \node[align=left] at (2.5in, 5.0in){(a) AMR-Wind stable, 5 m/s};
+  \end{tikzpicture}
+  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
+    velocity, taken at t=20,000 seconds along the wind direction, for
+    the (a) 5m/s, (b) 10 m/s, and (c) 15 m/s AMR-Wind stable
+    calculations }
 
-  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
-    velocity, taken at t=20,000 seconds along the wind direction. }
 \end{figure}

### 2020-12-03 Paper/main.tex
Add wall model description
Added tikZ image labels
Fix typos and stuff

@@
 }
+\usepackage{tikz}
+
+\newcommand{\average}[1]{\langle #1 \rangle}
 
@@
     Energy Technologies Department, AIAA member} and Alan
-  S. Hsieh.\footnote{Postdoctoral appointee, Wind Energy Technologies
-    Department, AIAA member}} \affil{Sandia National Laboratories,
-  Albuquerque, NM 87185}
+  S. Hsieh.\footnote{Senior member of technical staff, Wind Energy
+    Technologies Department, AIAA member}} \affil{Sandia National
+  Laboratories, Albuquerque, NM 87185}
 
@@
   were chosen to match the Cape Wind measurements of Archer \emph{et
-    al} with wind speeds of 5 m/s, 10 m/s, and 15 m/s.  The behavior
-  of the stable boundary layers, including mean flow quantities and
-  turbulent statistics, are examined and compared to previous
-  computations of the neutral and unstable offshore boundary layer at
-  the same location.  This study also examines the domain and mesh
-  requirements necessary to capture the turbulent scales for the
-  stable offshore boundary layers.  Finally, we compare solutions
-  computed using both Nalu-Wind and AMR-Wind solvers, and report on
-  their relative accuracy and performance in this study.
+    al.} with wind speeds of 5 m/s, 10 m/s, and 15 m/s at the 20m
+  measurement height.  The behavior of the stable boundary layers,
+  including mean flow quantities and turbulent statistics, are
+  examined and compared to previous computations of the neutral and
+  unstable offshore boundary layer at the same location.  This study
+  also examines the domain and mesh requirements necessary to capture
+  the turbulent scales for the stable offshore boundary layers.
+  Finally, we compare solutions computed using both Nalu-Wind and
+  AMR-Wind solvers, and report on their relative accuracy and
+  performance in this study.
 
@@
 \section{Nomenclature}
-
+\fxnote{Update symbols}
 {\renewcommand\arraystretch{1.0}
   \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
+ABL       & Atmospheric Boundary Layer \\
 $\alpha$  & Wind shear exponent  \\
@@
 $L$       & Turbulent integral length scale \\
+$L_{Ob}$   & Obukhov length scale \\
+LES       & Large Eddy Simulation \\
 $u_\tau$   & Friction velocity    \\
 $R_{ij}$   & Two point correlation tensor \\
+SBL       & Stable Boundary Layer \\
 $TI$      & Turbulence intensity \\
@@
 Kaul et al. \cite{kaul2020large} has shown that LES computations using
-Nalu-Wind can capture the neutrally and convectively unstable onshore
+Nalu-Wind can capture the neutral and convectively unstable onshore
 ABL.  Previous simulations by Cheung et al. \cite{cheung2020large}
@@
 to the SGS model, resulting in better agreement with surface layer observations.
-Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and 
+Andren \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and
 one capped by an inversion, comparing two SGS models. He found significant improvements
@@
 In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS
-model containing backscatter to favorably compare to the BASE measurements, showing that 
+model containing backscatter to favorably compare to the \fxnote{[Nate: define BASE]} BASE measurements, showing that
 the SBL could reach a quasi steady-state. They also showed good agreement with the Nieustadt
@@
 very little at a 2m resolution. Basu et al. \cite{Basu2005} published a set of
-turbulence statistics, measurements, and supporting LES simulations in support 
+turbulence statistics, measurements, and LES simulations in support
 of the viability of Nieustadt's local scaling hypothesis under very stable
@@
 results of which are published in Beare et al.\ \cite{Beare2006}. Collectively,
-this is knows as the GABLS initiative, and involved simulating a moderately 
+this is known as the GABLS initiative, and involved simulating a moderately
 stable flow taken from Kosovic and Curry \cite{Kosovic2000}. Eleven codes
@@
 have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}.
-This year, Wurps et al. \cite{Wurps2020} provided a rigorous grid resolution study for the SBL, 
+In 2020, Wurps et al. \cite{Wurps2020} provided a rigorous grid resolution study for the SBL,
 looking at mean flow, turbulence variables, and two-point correlations, using a dynamic
@@
 be computed using the Exawind solvers which match the measurements of
-Archer et al \cite{archer2016predominance}.  The behavior of the
+Archer et al. \cite{archer2016predominance}.  The behavior of the
 stable boundary layers, including mean flow quantities and turbulent
@@
 structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
-used to calculate the same stable boundary layer, and the relative
-differences between the codes are reported.
+used to calculate the same SBL, and the relative differences between
+the codes are reported.
 

### 2020-12-03 Paper/results.tex
Fix typos and stuff

@@
   \hline
-  Nalu-wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
-  Nalu-wind medium  &   5.0  &  5.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
-  Nalu-wind fine    &   2.5  &  2.5   & 2.5 & 1.0km $\times$ 1.0km $\times$ 1.0km  \\
+  Nalu-Wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
+  Nalu-Wind medium  &   5.0  &  5.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
+  Nalu-Wind fine    &   2.5  &  2.5   & 2.5 & 1.0km $\times$ 1.0km $\times$ 1.0km  \\
 % AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
@@
   \hline
-  Nalu-wind coarse  &  10.0  & 36.4 m         & 0.0 m     \\
-  Nalu-wind medium  &   5.0  & 21.5 m         & 4.52 m    \\
-  Nalu-wind fine    &   2.5  & 25.3 m         & 5.92 m    \\
+  Nalu-Wind coarse  &  10.0  & 36.4 m         & 0.0 m     \\
+  Nalu-Wind medium  &   5.0  & 21.5 m         & 4.52 m    \\
+  Nalu-Wind fine    &   2.5  & 25.3 m         & 5.92 m    \\
 \hline
@@
 %%   \centering
-%%   \fxnote{UPDATE THIS FIGURE}\\
 %%   \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_Lengthscale_Stable_z20_Longitudinal.png}
@@
   \centering
-  %\fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
   \begin{tikzpicture}

### 2020-12-03 Paper/main.tex
minor wording change

@@
 
-In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS
-model containing backscatter to favorably compare to the \fxnote{[Nate: define BASE]} BASE measurements, showing that
-the SBL could reach a quasi steady-state. They also showed good agreement with the Nieustadt
-analytical model. In the same year, Saiki et al. \cite{Saiki2000} simulated an SBL with
+In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation
+with a nonlinear SGS model containing backscatter to favorably compare
+to the Beaufort Sea Arctic Stratus Experiment (BASE) measurements,
+showing that the SBL could reach a quasi steady-state. They also
+showed good agreement with the Nieustadt analytical model. In the same
+year, Saiki et al. \cite{Saiki2000} simulated an SBL with
 a strong capping inversion at z=500m, producing reasonable surface layer profiles and

### 2020-12-03 Paper/main.tex
Finished making Alan's changes

@@
 $u_\tau$   & Friction velocity    \\
+$\rho$    & Density \\
+$\rho_\circ$ & Reference density  \\
 $R_{ij}$   & Two point correlation tensor \\
 SBL       & Stable Boundary Layer \\
+$\theta$  & Potential temperature \\
 $TI$      & Turbulence intensity \\
@@
 using the Obukhov length, differences in the ABL behavior were seen
-bewteen the very stable boundary layer cases (5 m/s and 10 m/s), and
+between the very stable boundary layer cases (5 m/s and 10 m/s), and
 the stably stratified case (15 m/s).  The very stable cases had

### 2020-12-03 Paper/methodology.tex
Fix typos and stuff
Finished making Alan's changes

@@
 computational study.  A summary of the conditions for all stability
-classes is given table \ref{tab:CapeWindMeasurements}. In this work we
+classes is given in table \ref{tab:CapeWindMeasurements}. In this work we
 focus on the three stable atmospheric conditions at wind speeds of
@@
 
-Large Eddy Simulations (LES) of the stable atmopsheric conditions described in
+Large Eddy Simulations of the stable atmopsheric conditions described in
 Table~\ref{tab:CapeWindMeasurements} are performed using the open-source,
@@
 study uses two different incompressible computational fluid dynamic solvers
-available within the ExaWind suite --
+available within the ExaWind suite,
 Nalu-Wind~\footnote{\url{https://github.com/exawind/nalu-wind}} and
 AMR-Wind~\footnote{\url{https://github.com/exawind/amr-wind}}. This section
-briefly describes the incompressible Navier-Stokes equations solved in the
-solvers, the specifics of the turbulence model and the wall shear stress
+briefly describes the incompressible Navier-Stokes equations solved,
+the specifics of the turbulence model and the wall shear stress
 formulation used to model the terrain, and the details of the numerical
-discretization of the two equations in the two codes.
+discretization in the two codes.
 
@@
 \subsubsection{Governing equations}
-Both CFD codes solve the incompressible form of Navier-Stokes equations with
+Both CFD codes solve the incompressible form of the Navier-Stokes equations with
 appropriate models for turbulence closure. Equation~\ref{eqn:ns-les} shows the
@@
 atmospheric boundary layer problem. Term $\mathbf{I}$ represents the pressure
-gradient forces as a deviation from hydrostatic and horizontal mean gradient,
+gradient forces as a deviation from hydrostatic and horizontal mean gradients,
 term $\mathbf{II}$ represents the contribution from viscous and sub-filter scale
@@
 
-\begin{align*}
+\begin{align}
   \frac{\rho}{\rho_\circ} \approx 1 - \beta \left( \theta - \theta_\circ \right)
-\end{align*}
+\end{align}
 This leads to a forcing term that depends on potential temperature ($\theta$),
@@
 in absolute temperature, i.e.,
-\begin{align*}
+\begin{align}
    \left[ \frac{\partial T}{\partial t}, \frac{\partial T}{\partial x}, \frac{\partial T}{\partial y} \right] =
    \left( \frac{\bar{p}}{p_\circ} \right)^{\left(\frac{R}{c_p}\right)} \left[ \frac{\partial \theta}{\partial t}, \frac{\partial \theta}{\partial x}, \frac{\partial \theta}{\partial y} \right]
-\end{align*}
+\end{align}
 Furthermore, ignoring the pressure and viscous work terms in
@@
   \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{h}\right) +
-  \frac{\partial}{\partial x_j} \left(\bar{\rho}\, \widetilde{u}_j \widetilde{h} \right) = - \frac{\partial}{\partial x_j} q_j \label{eqn:enthalpy-les}
+  \frac{\partial}{\partial x_j} \left(\bar{\rho}\, \widetilde{u}_j \widetilde{h} \right) = - \frac{\partial}{\partial x_j} q_j . \label{eqn:enthalpy-les}
 \end{align}
@@
 (Eq.~\ref{eqn:ksgs-les}), based on Moeng~\cite{Moeng1984}, is used for
-LES turbulence closure.
+LES turbulence closure,
 
@@
 where
-\begin{align*}
+\begin{align}
   C_\epsilon &= 0.93 & \nu_t &= C_\epsilon l \sqrt{k} \\
   \tau_{\theta i} &= - 2\ \frac{\nu_t}{\mathrm{Pr}_t}\ \frac{\partial \widetilde{\theta}}{\partial x_i} & \mathrm{Pr}_t &= \left( 1 + \frac{2l}{\Delta} \right)^{-1} \\
-\end{align*}
+\end{align}
 The choice of the length scale ($l$) depends on whether the stratification is positive
@@
 by
-\begin{align*}
+\begin{align}
   l =
@@
   \end{cases}
-\end{align*}
-
-\begin{comment}
-  \fxnote{Shreyas write this part.  Currently placeholder equations below.}\\
-
-  The low-Mach number equations:
-  \begin{align}
-    \frac{\partial \rho} {\partial t} + \frac{\partial \rho u_j}{\partial x_j} & = 0, \\
-    \frac{\partial \rho u_i}{\partial t} + \frac{\partial \rho u_j u_i}{\partial x_j}
-    + \frac{\partial P}{\partial x_i} & = \frac{\partial \tau_{ij}}{\partial x_j}
-                                        + \left( \rho - \rho_{\circ} \right) g_i, \\
-    \frac{\partial \rho h}{\partial t} + \frac{\partial \rho u_j h}{\partial x_j} & =
-                                                                                    - \frac{\partial q_j}{\partial x_j} + \frac{\partial P_{th}}{\partial t},
 \end{align}
-\end{comment}
 
@@
 level, $S_1$ is the resolved wind speed at the first grid level and
-$\average{f}$ represents the horizontal planar average of $f$. The mean
+$\average{\bullet}$ represents the horizontal planar average. The mean
 sub-filter stresses are computed using Monin-Obukhov similarity
@@
 Navier-Stokes equations. Two spatial discretization approaches are supported
-within the codebase -- the edge-based scheme and control-volume finite-element
+within the codebase: the edge-based scheme and control-volume finite-element
 scheme. The edge-based scheme, used in the present study, is similar to the
@@
 Belos and MueLu libraries within Trilinos. The momentum and scalar transport
-equations are solved using GMRES iterative solver with symmetric Gauss-Seidel
+equations are solved using GMRES iterative solvers with symmetric Gauss-Seidel
 (SGS) preconditioners. The elliptic pressure-Poisson equation is solved using
@@
 reader is referred to Sprague et al.~\cite{SpragueAVR2020} and
-Domino~\cite{Domino:2015} more more details.
+Domino~\cite{Domino:2015} for more details.
 
@@
 adaptive mesh refinement (AMR) applications \cite{AMReX_JOSS}.
-Since AMR-Wind is limited to Cartesian block-structured grids it is specialized
-to handle atmospheric boundary layer physics and wind turbine wakes.
+Since AMR-Wind is limited to Cartesian block-structured grids, it is specialized
+to handle ABL physics and wind turbine wakes.
 The block-structured grids enable more efficient algorithms such as
@@
 which guarantees a divergence free flow. The diffusion terms can be handled explicitly, semi-implicitly,
-or fully implicit and are the discretized using a second-order central difference formula.
-For the simulations in this paper we use a fully implicit scheme as the variable viscosity
+or fully implicit and are discretized using a second-order central difference formula.
+For the simulations in this paper, we use a fully implicit scheme as the variable viscosity
 from the eddy viscosity may cause time step restrictions. After the scalar equations
-and the momentum equations are advanced in time a nodal projection is used to
-approximately correct the velocity field to make it divergence free. Where the nodal projection
+and the momentum equations are advanced in time, a nodal projection is used to
+approximately correct the velocity field to make it divergence free.  The nodal projection
 is based on a node centered finite element method \cite{almgren1998conservative}.
@@
 The computational methodology for the AMR-Wind and Nalu-Wind LES codes
-follows practices similar to the previous offshore ABL study, with
+follows practices similar to the previous offshore ABL study \cite{cheung2020large}, with
 some modifications to handle the stable stratification.  As in
@@
 trial-and-error process.  The final surface roughness of $z_0$=0.0005m
-used the stable offshore conditions (see table \ref{tab:z0tempparam})
+used for the stable offshore conditions (see table \ref{tab:z0tempparam})
 matched the roughness used in the neutral 15m/s and unstable 5m/s and
@@
 The values of the prescribed temperature change at the ocean surface
-is also given in table \ref{tab:CapeWindMeasurements}.  As the wind
+is also given in table \ref{tab:z0tempparam}.  As the wind
 speed increases, a larger temperature decrease was used to maintain

### 2020-12-03 Paper/results.tex
Finished making Alan's changes

@@
 denotes the longitudinal, lateral, or vertical velocity, respectively.
-For the LES simulations in this study, we desire that that the mesh
+For the LES simulations in this study, we desire that the mesh
 resolution be sufficiently fine to capture the high frequency
@@
 \end{equation}
-Here, equation \ref{eq:fmax} assumes that the turbulent eddies convect
+Here, Eq. \ref{eq:fmax} assumes that the turbulent eddies convect
 with a velocity of $0.6\bar{U}_{horiz}$ and $N=8$ is chosen for the
 purposes of this study.  Due to the alignment of the flow with the
-mesh directions, the grid size $\Delta = \sqrt{2}\cdot \textrm{dx}$.
+mesh directions, the grid size is defined as $\Delta = \sqrt{2}\cdot \textrm{dx}$.
 In all cases considered here, $f_{max} < f_{Ny}$, so the limiting
@@
 \ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20m
-height and averaged using 1/3 octave-bins to enchance clarity. For the
-$S_u$ and $S_w$ spectra, there noticeable shifts in the peak
+height and averaged using 1/3 octave-bins to enhance clarity. For the
+$S_u$ and $S_w$ spectra, there are noticeable shifts in the peak
 amplitude, while the peak amplitudes for $S_v$ remained fairly
@@
     longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
-    \rangle$ coefficient at $z$=20m for LES of stable 5m/s case with
+    \rangle$ coefficients at $z$=20m for LES of stable 5m/s case with
     different resolutions.}
@@
 resolution to fully resolve.  This may be an important consideration
-in situations where turbulence in a stable boundary layer interacts
+in situations where turbulence in a SBL interacts
 with turbine features, such as blade motions or downstream wakes.
@@
 
-Before examining the behavior the offshore ABL across all wind speeds,
+Before examining the behavior of the offshore ABL across all wind speeds,
 we first compare the results for a single case using both LES codes.
@@
 figure \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
-z=20m, the wind speed and wind shear match are close to an exact match
+z=20m, the wind speed and wind shear are close to an exact match
 between the two LES codes.  The horizontal wind speeds continue to
@@
   \caption{\label{fig:CompareAMRvsNaluWind_WSDir} Comparison of
-    AMR-Wind and Nalu-Wind velocity profiles for the stable 5 m/s
-    boundary layer. The dashed horizontal line corresponds to the
-    measurement height z=20m. }
+    AMR-Wind and Nalu-Wind horizontal velocity and wind direction
+    profiles for the stable 5 m/s boundary layer. The dashed
+    horizontal line corresponds to the measurement height z=20m. }
 \end{figure}
@@
 of physical time. For this case a total of $288\times 288 \times 384$ cells were used
-which were solved in parallel using 972 MPI ranks. Simulations were carried out NREL's
+which were solved in parallel using 972 MPI ranks. Simulations were carried out using NREL's
 Eagle supercomputer and AMR-Wind was compiled using Intel 2018.
@@
 
-In comparison the same case for Nalu-Wind takes 3.404363 seconds per time step which
+In comparison, the same case for Nalu-Wind takes 3.404363 seconds per time step which
 takes a total of 75.65 hours to complete the simulation. This simulation was carried out
@@
 \ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
-are also evident in \ref{fig:SnapshotsZ20}.  At higher wind speeds the
+are also evident in figure \ref{fig:SnapshotsZ20}.  At higher wind speeds the
 magnitude of the vertical $w'$ fluctuations increase, which plays a
-strong role in the growth the boundary layer.
+strong role in the growth of the boundary layer.
 
@@
 This observation can also be seen in images taken along the flow
-direction $\theta=225^\circ$, as shown in figure
-\ref{fig:SnapshotsSide}.  At the time t=20,000 seconds, the growth the
+direction $225^\circ$, as shown in figure
+\ref{fig:SnapshotsSide}.  At the time t=20,000 seconds, the growth of the
 of 15 m/s stable boundary layer is considerably larger than the very
@@
 boundary layer up to the inversion height, while the very stable 5 m/s
-and 10 m/s cases showed minimal shear at higher elevations.  The
+and 10 m/s cases showed minimal shear at higher elevations (figure \ref{CompareAMRallWS}).  The
 change in wind direction is also indicative of the boundary layer
@@
 similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
-and each similar temperatures at the ocean surface.  However, the
+and similar temperatures at the ocean surface.  However, the
 cooling effect in the very stable 10 m/s case is limited to $z$<350
@@
 unstable cases were classified as ``very unstable'', while the 15 m/s
-was identified as ``stable'' based on the Obukhov length scale.
+was identified as ``unstable'' based on the Obukhov length scale.
 
@@
 magnitude larger than the stable ABL cases.  The large lateral
-lengthscales for the very unstable ABL cases, compared to the lateral
+lengthscales for the very unstable ABL cases, compared to the smaller lateral
 lengthscales for the neutral and stable cases, is also worth noting.
@@
 lengthscale.  This is consistent with the large convective structures
-which develops in those cases.  For the unstable 15 m/s case, the
-lateral lengthscales was closer to neutral and stable cases.
+which develop in those cases.  For the unstable 15 m/s case, the
+lateral lengthscales were closer to neutral and stable cases.
 
@@
     longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$
-    coefficient at $z$=20m for all ABL stability cases.}
+    coefficient at $z$=20m for all ABL stability cases and windspeeds.}
 \end{figure}

### 2020-12-04 Paper/main.tex
Added Myra edits

@@
   were chosen to match the Cape Wind measurements of Archer \emph{et
-    al.} with wind speeds of 5 m/s, 10 m/s, and 15 m/s at the 20m
+    al.} with wind speeds of 5 m/s, 10 m/s, and 15 m/s at the 20 m
   measurement height.  The behavior of the stable boundary layers,
@@
 $TI$      & Turbulence intensity \\
-$TKE$     & Turbulent kinetic energy
+$TKE$     & Turbulent kinetic energy \\
+$\overline{U}_{horiz}$ & Time averaged horizontal velocity
 \end{longtable*}}
@@
 year, Saiki et al. \cite{Saiki2000} simulated an SBL with
-a strong capping inversion at z=500m, producing reasonable surface layer profiles and
+a strong capping inversion at z=500 m, producing reasonable surface layer profiles and
 identifying a need for SBL specific SGS models. Beare and MacVean \cite{Beare2004}
@@
 looking at mean flow, turbulence variables, and two-point correlations, using a dynamic
-SGS model that allows backscatter. They found grid requirements to be 2.5m, 10m, and 20m
+SGS model that allows backscatter. They found grid requirements to be 2.5 m, 10 m, and 20 m
 for stable, neutral, and convective boundary layers respectively. They advocate looking
@@
 \subsection{Objectives}
+\fxnote{fix order of objectives}
 In the current study on stable marine boundary layers, we aim to build
@@
 objectives.  First, a series of stable boundary layer conditions will
-be computed using the Exawind solvers which match the measurements of
+be computed using the ExaWind solvers which match the measurements of
 Archer et al. \cite{archer2016predominance}.  The behavior of the
@@
 for the stable offshore boundary layers.  Finally, two LES solvers
-within the Exawind project are compared in this study: the
+within the ExaWind project are compared in this study: the
 unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
@@
 considered here.  Based on the calculated turbulent integral
-lengthscale, horizontal domain sizes of 750m $\times$ 750m were found
+lengthscale, horizontal domain sizes of 750 m $\times$ 750 m were found
 to be necessary for these simulations.  Various mesh resolutions were
 also considered for the stable runs, and it was determined that the
-finest resolution of $dx$=2.5m was able to resolve the longitudinal
+finest resolution of $dx$=2.5 m was able to resolve the longitudinal
 length scales and highest temporal frequencies, but inadequate for

### 2020-12-04 Paper/methodology.tex
Added Myra edits

@@
 for this computational study.  The Cape Wind platform collected wind
-measurements at 20m, 41m, and 60m above the mean water level, along
+measurements at 20 m, 41 m, and 60 m above the mean water level, along
 with temperature and barometric measurements from the years 2003-2011.
@@
 found that the marine boundary layer is predominantly unstable, with
-61\% of conditions classified as unstable, versus 21\% neutral and
+61\% of conditions were classified as unstable, versus 21\% neutral and
 18\% stable.  The stratification of the marine boundary layer, as
@@
 kinetic energies (TKE), and wind speeds from the Cape Wind platform at
-z=20m, a stable set of conditions were chosen as targets for this
+z=20 m, a stable set of conditions were chosen as targets for this
 computational study.  A summary of the conditions for all stability
@@
 focus on the three stable atmospheric conditions at wind speeds of
-5m/s, 10m/s, and 15m/s, while the neutral and unstable conditions
+5 m/s, 10 m/s, and 15 m/s, while the neutral and unstable conditions
 where studied in previous work \cite{cheung2020large}.
@@
 The averaged wind speeds were enforced at the measurement height of
-20m, and the applied wind directions were consistent with the
+20 m, and the applied wind directions were consistent with the
 predominant stable direction of 225 degrees southwest.
@@
   Wind.  The stable atmospheric conditions used in this study are
-  highlighted in bold below.} \centering
+  highlighted in bold below, while the neutral and unstable conditions
+  from \cite{cheung2020large} are included for comparison.} \centering
 \begin{tabular}{cccc}
@@
 Large Eddy Simulations of the stable atmopsheric conditions described in
-Table~\ref{tab:CapeWindMeasurements} are performed using the open-source,
+table~\ref{tab:CapeWindMeasurements} are performed using the open-source,
 ExaWind simulation environment\footnote{\url{https://github.com/exawind}}.
@@
 
-% \fxnote{Do we want a github link reference for amr-wind? exawind?}\\
+\fxnote{Clarify we don't actually use adaptive refinement -- that is future work.}
 
@@
 and are well suited for next generation supercomputers that use GPU's.
+In the current work, we focus on applying AMR-Wind to ABL computations
+using statically refined, uniform meshes, and will examine adaptive
+mesh capabilities in future studies.
 
@@
 through a numerical grid study.  As discussed in section
-\ref{sec:gridstudy}, the horizontal dimensions of 750m $\times$ 750m
+\ref{sec:gridstudy}, the horizontal dimensions of 750 m $\times$ 750 m
 were found to be sufficient to capture any large scale structures in
-the boundary layer, and in all cases the vertical dimension of 1000m
+the boundary layer, and in all cases the vertical dimension of 1000 m
 was also used.  The grid study in section \ref{sec:gridstudy} also
@@
 The initial temperature profile in all cases was a constant 300K until
-the specified inversion height of 650m.  The inversion layer thickness
-was 100m, and above this, the temperature linearly increased until it
+the specified inversion height of 650 m.  The inversion layer thickness
+was 100 m, and above this, the temperature linearly increased until it
 reached 308.75K at the upper boundary.  The initial mean velocity
@@
 matched the roughness used in the neutral 15m/s and unstable 5m/s and
-10m/s cases from the previous study \cite{cheung2020large}.  This
+10 m/s cases from the previous study \cite{cheung2020large}.  This
 value of surface roughness is consistent with the measurements from
@@
 determined, and the correct mesh requirements known from the study in
-section \ref{sec:gridstudy}, the LES computations for the stable 5m/s,
-10m/s, and 15m/s ABL cases could be set up and run.  Each of the cases
+section \ref{sec:gridstudy}, the LES computations for the stable 5 m/s,
+10 m/s, and 15 m/s ABL cases could be set up and run.  Each of the cases
 was run for 15,000 seconds before collecting statistics for another

### 2020-12-04 Paper/results.tex
Added Myra edits

@@
 table \ref{tab:GridStudySetup}, the horizontal resolutions varied from
-10m to 2.5m cells for the coarse and fine cases, respectively.  All
+10 m to 2.5 m cells for the coarse and fine cases, respectively.  All
 simulations for the grid study also used a vertical resolution of
-dz=2.5m and the same vertical extent of 1km.
+dz=2.5 m and the same vertical extent of 1 km.
 
@@
   \hline
-  Nalu-Wind coarse  &  10.0  & 10.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
-  Nalu-Wind medium  &   5.0  &  5.0   & 2.5 & 1.5km $\times$ 1.5km $\times$ 1.0km  \\
-  Nalu-Wind fine    &   2.5  &  2.5   & 2.5 & 1.0km $\times$ 1.0km $\times$ 1.0km  \\
+  Nalu-Wind coarse  &  10.0  & 10.0   & 2.5 & 1.5 km $\times$ 1.5km $\times$ 1.0 km  \\
+  Nalu-Wind medium  &   5.0  &  5.0   & 2.5 & 1.5 km $\times$ 1.5 km $\times$ 1.0 km  \\
+  Nalu-Wind fine    &   2.5  &  2.5   & 2.5 & 1.0 km $\times$ 1.0 km $\times$ 1.0 km  \\
 % AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
@@
 $f_{max}$ for the different mesh resolutions is shown in figure
-\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20m
+\ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20 m
 height and averaged using 1/3 octave-bins to enhance clarity. For the
@@
 peaks in the lateral and vertical directions.
+\fxnote{OK for temporal resolution}
 
@@
 correlation coefficient $\langle R_{11}(\boldsymbol{\xi})\rangle$ by
-sampling over multiple points at the $z$=20m height, typically 100-150
+sampling over multiple points at the $z$=20 m height, typically 100-150
 points, and averaging the result.  The longitudinal $\langle
@@
     longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
-    \rangle$ coefficients at $z$=20m for LES of stable 5m/s case with
+    \rangle$ coefficients at $z$=20 m for LES of stable 5m/s case with
     different resolutions.}
@@
 requirements.  Assuming the longitudinal length scales on the order of
-30 m, we estimated a minimum domain size of 750m $\times$ 750m in the
+30 m, we estimated a minimum domain size of 750 m $\times$ 750 m in the
 horizontal directions for both the Nalu-Wind and AMR-Wind LES
@@
 statistics are given for both cases, including the friction velocity
-$u_\tau$, the turbulence intensity TI at z=20m, and local shear
-exponent $\alpha$ at z=20m, defined as
+$u_\tau$, the turbulence intensity TI at z=20 m, and local shear
+exponent $\alpha$ at z=20 m, defined as
 $$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
@@
 figure \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
-z=20m, the wind speed and wind shear are close to an exact match
+z=20 m, the wind speed and wind shear are close to an exact match
 between the two LES codes.  The horizontal wind speeds continue to
-agree well for $z$<100m, beyond which a relatively constant velocity
+agree well for $z$<100 m, beyond which a relatively constant velocity
 difference is observed.   For both AMR-Wind and Nalu-Wind, an
-approximately linear veer profile was observed until $z\approx$ 250m,
+approximately linear veer profile was observed until $z\approx$ 250 m,
 at which point the wind direction remained constant until the
@@
     profiles for the stable 5 m/s boundary layer. The dashed
-    horizontal line corresponds to the measurement height z=20m. }
+    horizontal line corresponds to the measurement height z=20 m. }
 \end{figure}
@@
     the stable 5 m/s boundary layer. The dashed horizontal line
-    corresponds to the measurement height z=20m.}
+    corresponds to the measurement height z=20 m.}
 \end{figure}
@@
   \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
-    and Nalu-Wind wind spectra at z=20m for the stable 5 m/s boundary
+    and Nalu-Wind wind spectra at z=20 m for the stable 5 m/s boundary
     layer. }
@@
 %%     Comparison of AMR-Wind and Nalu-Wind $\langle R_{11}
-%%     \rangle$ correlation at z=20m. }
+%%     \rangle$ correlation at z=20 m. }
 %% \end{figure}
@@
 Using the results of the stable cases described in \ref{sec:CFDsetup},
-as well as the computations from the previous study in
-\cite{cheung2020large}, we can examine the influence of wind speed and
+as well as the neutral and unstable ABL computations from the previous study in
+Cheung et al. \cite{cheung2020large}, we can examine the influence of wind speed and
 stratification on offshore ABL behavior.  In this section we first
@@
 \subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
-From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
-15m/s, a number of quantities can be computed to compare with the
+\fxnote{Explain why AMR-Wind only}
+From AMR-Wind calculations of the stable ABL at 5 m/s, 10 m/s, and
+15 m/s, a number of quantities can be computed to compare with the
 measured targets from Archer et al \cite{archer2016predominance}.  In
@@
 longitudinal lengthscale $L$, and stability classification for each of
-these three cases.  The TI values, calculated at the height $z$=20m
+these three cases.  The TI values, calculated at the height $z$=20 m
 fall within the target range of 4.5\% to 6.0\% for stable conditions
@@
   \hline
-  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m & 27.7 m  & Very stable\\
-  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m & 29.6 m  & Very stable\\
-  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m & 43.8 m  & Stable \\
+  AMRWind & 5 m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m & 27.7 m  & Very stable\\
+  AMRWind & 10 m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m & 29.6 m  & Very stable\\
+  AMRWind & 15 m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m & 43.8 m  & Stable \\
   \hline
@@
 horizontal and vertical velocities for each of the three cases at the
-z=20m measurement height are shown.  The largest difference can be
+z=20 m measurement height are shown.  The largest difference can be
 seen in the size of the flow structures between the very unstable and
@@
 
-%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%% z=20 m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
 % Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
@@
     velocity and vertical velocity, taken at t=20,000 seconds of the
-    simulations at height z=20m, for the AMR-Wind calculation of the
+    simulations at height z=20 m, for the AMR-Wind calculation of the
     stable 5 m/s, 10 m/s, and 15 m/s ABL. }
@@
 boundary layer up to the inversion height, while the very stable 5 m/s
-and 10 m/s cases showed minimal shear at higher elevations (figure \ref{CompareAMRallWS}).  The
+and 10 m/s cases showed minimal shear at higher elevations (figure \ref{fig:CompareAMRallWS}).  The
 change in wind direction is also indicative of the boundary layer
@@
 m/s cases, respectively, while the linear veer is present in the 15
-m/s stable case up to $z$=650m.
+m/s stable case up to $z$=650 m.
 
@@
 discussed above.  Despite all cases reaching a similar TI levels at
-$z$=20m, the turbulence decays at different rates for each case until
+$z$=20 m, the turbulence decays at different rates for each case until
 reaching the top of the boundary layer.  The effect of the different
@@
   \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
-    wind speed and wind direction profile for the stable 5m/s, 10m/s,
-    and 15m/s boundary layers. }
+    wind speed and wind direction profile for the stable 5 m/s, 10 m/s,
+    and 15 m/s boundary layers. }
 \end{figure}
@@
   \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
-    intensity and temperature profile for the stable 5m/s, 10m/s, and
-    15m/s boundary layers. }
+    intensity and temperature profile for the stable 5 m/s, 10 m/s, and
+    15 m/s boundary layers. }
 \end{figure}
@@
 %%   \caption{Calculation of the wind spectra $S_i$ for LES of stable
-%%     5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
+%%     5 m/s, 10 m/s, and 15 m/s cases at z=20 m, 40 m, and 60 m.  The black
 %%     vertical lines correspond to the maximum resolvable frequency
@@
     longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})\rangle$
-    coefficient at $z$=20m for all ABL stability cases and windspeeds.}
+    coefficient at $z$=20 m for all ABL stability cases and windspeeds.}
 \end{figure}
@@
   \caption{ \label{fig:AllStabilityLengthscale} Calculation of the
-    averaged longitudinal and lateral lengthscale at $z$=20m for all
+    averaged longitudinal and lateral lengthscale at $z$=20 m for all
     ABL stability cases.}

### 2020-12-04 Paper/results.tex
Update paper

@@
 resolution with 2.5m mesh cells was required to capture the spectral
-peaks in the lateral and vertical directions.
-\fxnote{OK for temporal resolution}
+peaks for the lateral and vertical velocities.
 
-The second metric for determining the appropriate grid size and mesh
-resolution is through the correlation tensor and turbulence integral
-length scale.  The two-point correlation tensor
-$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at position $\mathbf{x}$ and
-separation vector $\boldsymbol{\xi}$ is defined as
+However, the above analysis of spectra only provides information to
+determine if the turbulent fluctuations can be resolved temporally,
+and a separate analysis is needed to determine if the fluctuations can
+be resolved in different spatial directions.  The second metric for
+examining the appropriate grid size and mesh resolution is through the
+correlation tensor and turbulence integral length scale.  The
+two-point correlation tensor $R_{ij}(\mathbf{x},\boldsymbol{\xi})$ at
+position $\mathbf{x}$ and separation vector $\boldsymbol{\xi}$ is
+defined as
 \begin{equation}
@@
          {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
-    \node[align=left] at (1in, 4.50in){(a) horizontal vel, 5 m/s};
+    \node[align=left] at (1in, 4.50in){(a) horizontal vel., stable 5 m/s};
     \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
          {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
-    \node[align=left] at (4.25in, 4.50in){(b) vertical vel, 5 m/s};
+    \node[align=left] at (4.25in, 4.50in){(b) vertical vel., stable 5 m/s};
 
@@
          {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
-    \node[align=left] at (1in, 2.25in){(c) horizontal vel, 10 m/s};
+    \node[align=left] at (1in, 2.25in){(c) horizontal vel., stable 10 m/s};
     \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
          {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
-    \node[align=left] at (4.25in, 2.25in){(d) vertical vel, 10 m/s};
+    \node[align=left] at (4.25in, 2.25in){(d) vertical vel., stable 10 m/s};
 
@@
          {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
-    \node[align=left] at (1in, 0in){(e) horizontal vel, 15 m/s};
+    \node[align=left] at (1in, 0in){(e) horizontal vel., stable 15 m/s};
     \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
          {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
-    \node[align=left] at (4.25in, 0in){(f) vertical vel, 15 m/s};
+    \node[align=left] at (4.25in, 0in){(f) vertical vel., stable 15 m/s};
 

### 2020-12-04 Paper/main.tex
Update paper
Edit objectives

@@
 \section{Nomenclature}
-\fxnote{Update symbols}
 {\renewcommand\arraystretch{1.0}
@@
 \section{Introduction}
-%\fxnote{Update this introduction.}
 
@@
 \subsection{Objectives}
-\fxnote{fix order of objectives}
-In the current study on stable marine boundary layers, we aim to build
-on the previous work in the literature and complete several
-objectives.  First, a series of stable boundary layer conditions will
-be computed using the ExaWind solvers which match the measurements of
-Archer et al. \cite{archer2016predominance}.  The behavior of the
-stable boundary layers, including mean flow quantities and turbulent
-statistics, are examined and compared to the neutral and unstable
-cases computed in \cite{cheung2020large}.  Secondly, we examine the
+\fxnote{fix order of objectives} In the current study on stable marine
+boundary layers, we aim to build on the previous work in the
+literature and complete several objectives.  First, we examine the
 domain and mesh requirements necessary to capture the turbulent scales
-for the stable offshore boundary layers.  Finally, two LES solvers
-within the ExaWind project are compared in this study: the
+for the stable offshore boundary layers.  Secondly, two LES solvers
+within the ExaWind project will be compared in this study: the
 unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
@@
 used to calculate the same SBL, and the relative differences between
-the codes are reported.
+the codes are reported.  Finally, a series of stable boundary layer
+conditions will be computed using AMR-Wind which match the
+measurements of Archer et al. \cite{archer2016predominance}.  The
+behavior of the stable boundary layers, including mean flow quantities
+and turbulent statistics, are examined and compared to the neutral and
+unstable cases computed in \cite{cheung2020large}.
 

### 2020-12-04 Paper/main.tex
Phil's modifications to text

@@
 \subsection{Objectives}
-\fxnote{fix order of objectives} In the current study on stable marine
+In the current study on stable marine
 boundary layers, we aim to build on the previous work in the

### 2020-12-04 Paper/results.tex
Phil's modifications to text

@@
 $L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
-required to capture the lateral scales.
+required to capture the lateral scales.  This may be a critical
+consideration when resolving both the lateral and longitudinal
+turbulent scales are important, such as in SBL simulations with
+turbine interactions.  However, in other situations, the additional
+computational cost incurred may be prohibitive and only the
+longitudinal component can be resolved.
 
-Based on this longitudinal length scale, we also determined the
+Based on the longitudinal length scale, we also determined the
 overall domain size necessary for stable ABL calculations.  To provide
@@
 
-\subsection{Comparison of stable offshore ABL for different wind speeds and stabilities}
+\subsection{Comparison of the stable offshore ABL for different wind speeds and stabilities}
 
 Using the results of the stable cases described in \ref{sec:CFDsetup},
-as well as the neutral and unstable ABL computations from the previous study in
-Cheung et al. \cite{cheung2020large}, we can examine the influence of wind speed and
-stratification on offshore ABL behavior.  In this section we first
+as well as the neutral and unstable ABL computations from the previous
+study in Cheung et al. \cite{cheung2020large}, we can examine the
+influence of wind speed and stratification on offshore ABL behavior.
+In this section, we use the AMR-Wind code to calculate the stable ABL
+at 5 m/s, 10 m/s, and 15 m/s because of its computational efficiency
+and comparable accuracy to Nalu-Wind.  From the results we first
 compare the differences between the three stable ABL cases, and then
@@
 \subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
-\fxnote{Explain why AMR-Wind only}
-From AMR-Wind calculations of the stable ABL at 5 m/s, 10 m/s, and
-15 m/s, a number of quantities can be computed to compare with the
-measured targets from Archer et al \cite{archer2016predominance}.  In
+
+From AMR-Wind LES calculations, a number of quantities can be computed
+to compare with the measured targets from Archer et al
+\cite{archer2016predominance}.  In
 table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
@@
   \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
-    wind speed and wind direction profile for the stable 5 m/s, 10 m/s,
-    and 15 m/s boundary layers. }
+    wind speed and wind direction profile for the stable 5 m/s, 10
+    m/s, and 15 m/s boundary layers. The dashed horizontal line
+    corresponds to the measurement height z=20 m.}
 \end{figure}
@@
   \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
-    intensity and temperature profile for the stable 5 m/s, 10 m/s, and
-    15 m/s boundary layers. }
+    intensity and temperature profile for the stable 5 m/s, 10 m/s,
+    and 15 m/s boundary layers. The dashed horizontal line corresponds
+    to the measurement height z=20 m.}
 \end{figure}

### 2020-12-04 Paper/main.tex
Added nomenclature and fixed notationi

@@
 $\alpha$  & Wind shear exponent  \\
+$\beta$   & Thermal expansion coefficient \\
+$c_p$     & Specific heat capacity \\
+$\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
 $f$       & Frequency \\
@@
 $f_{Ny}$   & Nyquist frequency \\
+$g, g_i$   & Gravitational acceleration \\
+$k, TKE$  & Turbulent kinetic energy \\
 $L$       & Turbulent integral length scale \\
 $L_{Ob}$   & Obukhov length scale \\
+$\nu_t$   & Turbulent viscosity \\
 LES       & Large Eddy Simulation \\
-$u_\tau$   & Friction velocity    \\
 $\rho$    & Density \\
 $\rho_\circ$ & Reference density  \\
+$\phi_h$  & Potential temperature gradient \\
+$Pr_t$    & Turbulent Prandtl number \\
+$R$       & Universal gas constant \\
 $R_{ij}$   & Two point correlation tensor \\
@@
 $\theta$  & Potential temperature \\
+$S_i$     & Wind spectra \\
+$\sigma_i$ & Wind speed variance \\
+$\tau_{ij}$ & Shear stress \\
 $TI$      & Turbulence intensity \\
-$TKE$     & Turbulent kinetic energy \\
-$\overline{U}_{horiz}$ & Time averaged horizontal velocity
+$\overline{U}_{horiz}$ & Time averaged horizontal velocity \\
+$u_\tau$   & Friction velocity    \\
+$V_1$     & Resolved wind speed at first grid level 
 \end{longtable*}}
@@
 also considered for the stable runs, and it was determined that the
-finest resolution of $dx$=2.5 m was able to resolve the longitudinal
+finest resolution of $\Delta_x$=2.5 m was able to resolve the longitudinal
 length scales and highest temporal frequencies, but inadequate for

### 2020-12-04 Paper/methodology.tex
Added nomenclature and fixed notationi

@@
 \subsection{Measured offshore conditions}
-% \fxnote{Lawrence write this part}
 
@@
 \begin{align}
- (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{S_1 \average{\widetilde{u}_1} + \average{S_1} (\widetilde{u}_1 - \average{\widetilde{u}_1} ) }{ \average{S_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
- (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{S_1 \average{\widetilde{v}_1} + \average{S_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{S_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } \\
-  (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{S_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{S_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{S_1} ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) },
+ (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{V_1 \average{\widetilde{u}_1} + \average{V_1} (\widetilde{u}_1 - \average{\widetilde{u}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
+ (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{V_1 \average{\widetilde{v}_1} + \average{V_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } \\
+  (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{V_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{V_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{V_1} ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) },
 \end{align}
 where all quantities with the subscript 1 are values at the first vertical grid
-level, $S_1$ is the resolved wind speed at the first grid level and
+level, $V_1$ is the resolved wind speed at the first grid level and
 $\average{\bullet}$ represents the horizontal planar average. The mean
@@
 \begin{equation}
-(\tau_{\theta z})_0 = \left ( \frac{u_{\tau} \kappa}{ \phi_h} \right ) \frac{S_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{S_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{S_1} },
+(\tau_{\theta z})_0 = \left ( \frac{u_{\tau} \kappa}{ \phi_h} \right ) \frac{V_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{V_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{V_1} },
 \end{equation}
@@
 
-\fxnote{Clarify we don't actually use adaptive refinement -- that is future work.}
-
 As part of a suite of physics codes within the open-source project called ExaWind,
@@
 \subsection{\label{sec:CFDsetup}Computational setup}
-% \fxnote{Domains, grids, boundary conditions}
 

### 2020-12-04 Paper/results.tex
Added nomenclature and fixed notationi

@@
   \hline
-  Case              & dx [m] & dy [m] & dz [m] & Domain size \\
+  Case              & $\Delta_x$ & $\Delta_y$ & $\Delta_z$ & Domain size \\
   \hline
-  Nalu-Wind coarse  &  10.0  & 10.0   & 2.5 & 1.5 km $\times$ 1.5km $\times$ 1.0 km  \\
-  Nalu-Wind medium  &   5.0  &  5.0   & 2.5 & 1.5 km $\times$ 1.5 km $\times$ 1.0 km  \\
-  Nalu-Wind fine    &   2.5  &  2.5   & 2.5 & 1.0 km $\times$ 1.0 km $\times$ 1.0 km  \\
+  Nalu-Wind coarse  &  10.0 m  & 10.0 m & 2.5 m & 1.5 km $\times$ 1.5km $\times$ 1.0 km  \\
+  Nalu-Wind medium  &   5.0 m &  5.0 m  & 2.5 m & 1.5 km $\times$ 1.5 km $\times$ 1.0 km  \\
+  Nalu-Wind fine    &   2.5 m &  2.5 m  & 2.5 m & 1.0 km $\times$ 1.0 km $\times$ 1.0 km  \\
 % AMR-wind fine     &   2.5  &  2.5   & 2.5 & 0.0 \\
@@
 purposes of this study.  Due to the alignment of the flow with the
-mesh directions, the grid size is defined as $\Delta = \sqrt{2}\cdot \textrm{dx}$.
+mesh directions, the grid size is defined as $\Delta = \sqrt{2} \Delta_x $.
 In all cases considered here, $f_{max} < f_{Ny}$, so the limiting
@@
   \hline
-  Case              & dx [m] & Longitudinal L  & Lateral L \\
+  Case              & $\Delta_x$ & Longitudinal L  & Lateral L \\
   \hline
-  Nalu-Wind coarse  &  10.0  & 36.4 m         & 0.0 m     \\
-  Nalu-Wind medium  &   5.0  & 21.5 m         & 4.52 m    \\
-  Nalu-Wind fine    &   2.5  & 25.3 m         & 5.92 m    \\
+  Nalu-Wind coarse  &  10.0 m  & 36.4 m         & 0.0 m     \\
+  Nalu-Wind medium  &   5.0 m & 21.5 m         & 4.52 m    \\
+  Nalu-Wind fine    &   2.5 m & 25.3 m         & 5.92 m    \\
 \hline

### 2020-12-04 Paper/main.tex
More nomenclature stuff

@@
 $c_p$     & Specific heat capacity \\
+$C_\epsilon$  & Turbulence model constant \\
 $\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
@@
 $g, g_i$   & Gravitational acceleration \\
+$h$       & Enthalpy \\
 $k, TKE$  & Turbulent kinetic energy \\
@@
 $\sigma_i$ & Wind speed variance \\
-$\tau_{ij}$ & Shear stress \\
+$\tau_{ij}$ & Stress tensor \\
 $TI$      & Turbulence intensity \\

### 2020-12-05 Paper/main.tex
Editing part of conclusion

@@
 the peak $S_u$ spectra, and excellent matches were observed for the
-averaged veer, temperature, and TI profiles.
+averaged veer, temperature, and TI profiles.  For the problem sizes
+considered here, it was also found that AMR-Wind was significantly
+more computationally efficient than Nalu-Wind when measured on a time
+per degree of freedom basis.  However, the good agreement is a
+promising indication that the two codes can be used together
+effectively for future wind farm applications, where the highly
+efficient, structured nature of AMR-Wind handles the free stream
+boundary layer and is combined with the unstructured Nalu-Wind solver
+for complex turbine geometries.
+
+% The performance difference may be caused
+% by XXX, but warrants further investigation in future work.
 

### 2020-12-05 Paper/results.tex
More nomenclature stuff
updated computation performance

@@
 \caption{\label{tab:CompareAMRvsNalu} Comparison of AMR-Wind and
-  Nalu-Wind} \centering
+  Nalu-Wind ABL statistics} \centering
 \begin{tabular}{cccccc}
@@
 The time per degree of freedom for AMR-Wind is
-\[\frac{n_r t_{ts} }{n_{dofs}} = 8\times10^{-6} [s]\]
+\[\frac{n_r t_{ts} }{n_{dofs}} = 8.118\times10^{-6} [s]\]
 where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
-the total number of degrees of freedom (for AMR-Wind we are using the number of cells).
-This value allows us to compare speed relative to Nalu-Wind when using a different
-grid and number of MPI ranks, where a smaller value means a faster time to solution.
+the total number of degrees of freedom (for AMR-Wind degrees of freedom are taken to be
+ number of cells in the grid). This value allows us to compare speed relative to 
+Nalu-Wind when using a different grid and number of MPI ranks, where a smaller value 
+means a faster time to solution. It should be noted that the choice to use fewer 
+elements for AMR-Wind was to ensure perfect load balancing across MPI ranks. This 
+$288 \times 288 \times 384$ grid can be perfectly decomposed into smaller $32^3$ blocks.
 
-In comparison, the same case for Nalu-Wind takes 3.404363 seconds per time step which
-takes a total of 75.65 hours to complete the simulation. This simulation was carried out
-on 1224 MPI ranks on a grid that contains $300\times 300 \times 400$ cells. The equivalent
-time per degree of freedom for Nalu-Wind is $1.032 \times 10^{-4}$ s.
+In comparison, the same case for Nalu-Wind takes 3.404 seconds per time step which
+takes a total of 75.64 hours to complete the simulation. This simulation was carried out
+on 1224 MPI ranks for a grid that contains $300\times 300 \times 400$ cells. The equivalent
+time per degree of freedom for Nalu-Wind is $1.147 \times 10^{-4}$ s, where degrees of freedom
+are the number of nodes in the mesh.
+
+For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
+A time step within AMR-Wind requires two poisson solves (MAC and nodal projection),
+a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
+(potential temperature equation and subgrid-scale kinetic energy equation).
+Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
+step, in this work we use two Picard iterations for every time step.
+Each Picard iteration requires a Poisson solve and five Helmholtz solves
+(three momentum equations, an Enthalpy equation, and the subgrid-scale kinetic energy equation).
+It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
+implementation. The most significant difference between the two solvers is that AMR-Wind uses structured grids
+whereas Nalu-Wind uses unstructured grids. There is a lot of computational overhead with storing
+and manipulating unstructured data.
 

### 2020-12-05 Paper/results.tex
typo: lower case for enthalpy

@@
 Each Picard iteration requires a Poisson solve and five Helmholtz solves
-(three momentum equations, an Enthalpy equation, and the subgrid-scale kinetic energy equation).
+(three momentum equations, an enthalpy equation, and the subgrid-scale kinetic energy equation).
 It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical

### 2020-12-05 Paper/results.tex
fix last sentence
minor change to Sec. IV.B.1

@@
 For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work. 
-A time step within AMR-Wind requires two poisson solves (MAC and nodal projection),
+A time step within AMR-Wind requires two Poisson solves (MAC and nodal projection),
 a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves 
@@
 It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
-implementation. The most significant difference between the two solvers is that AMR-Wind uses structured grids
-whereas Nalu-Wind uses unstructured grids. There is a lot of computational overhead with storing
-and manipulating unstructured data.
+implementation, and additional study is required to understand the performance comparisons.
+The most significant difference between the two solvers is that AMR-Wind uses structured grids
+whereas Nalu-Wind uses unstructured grids. The differences in performance can be attributed with the 
+computational overhead of storing and manipulating unstructured data.
 

### 2020-12-05 Paper/main.tex
Added more nomenclature symbols

@@
 LES       & Large Eddy Simulation \\
+$n_{dofs}$ & Number of degrees of freedom \\
+$n_r$     & Number MPI ranks \\
 $\rho$    & Density \\
@@
 $TI$      & Turbulence intensity \\
+$t_{ts}$  & Time per time-step \\
 $\overline{U}_{horiz}$ & Time averaged horizontal velocity \\

### 2020-12-06 Paper/main.tex
Apply changes suggested by NREL Editorial office

@@
 
-\title{Computation and comparison of the stable Northeastern US marine boundary layer}
+\title{Computation and comparison of the stable northeastern United States
+  marine boundary layer}
 
@@
 \begin{abstract}
-  In this work we investigate the behavior of stable marine boundary
-  layers located near the coast of the Northeastern United States.
-  Using the ExaWind LES codes, three stable atmospheric conditions
-  were chosen to match the Cape Wind measurements of Archer \emph{et
-    al.} with wind speeds of 5 m/s, 10 m/s, and 15 m/s at the 20 m
-  measurement height.  The behavior of the stable boundary layers,
-  including mean flow quantities and turbulent statistics, are
-  examined and compared to previous computations of the neutral and
-  unstable offshore boundary layer at the same location.  This study
-  also examines the domain and mesh requirements necessary to capture
-  the turbulent scales for the stable offshore boundary layers.
-  Finally, we compare solutions computed using both Nalu-Wind and
-  AMR-Wind solvers, and report on their relative accuracy and
-  performance in this study.
+  In this work we investigate the behavior of stable marine boundary layers
+  located near the coast of the Northeastern United States.  Using the ExaWind
+  large eddy simulation (LES) codes, three stable atmospheric conditions were
+  chosen to match the Cape Wind measurements of Archer \emph{et al.} with wind
+  speeds of 5 m/s, 10 m/s, and 15 m/s at the 20 m measurement height.  The
+  behavior of the stable boundary layers, including mean flow quantities and
+  turbulent statistics, are examined and compared to previous computations of
+  the neutral and unstable offshore boundary layer at the same location.  This
+  study also examines the domain and mesh requirements necessary to capture the
+  turbulent scales for the stable offshore boundary layers.  Finally, we compare
+  solutions computed using both Nalu-Wind and AMR-Wind solvers, and report on
+  their relative accuracy and performance in this study.
 
@@
 plants in the United States has highlighted the need to properly
-understand the wind resource and atmospheric characteristics of the US
+understand the wind resource and atmospheric characteristics of the U.S.
 Atlantic Coast.  Several atmospheric phenomena particular to this
@@
 current study is the atmospheric stability of the marine boundary
-layer in the Northeastern US.
+layer in the Northeastern United States.
 
@@
 the ABL and wind characteristics for potential offshore wind farms in
-the Northeastern US.  Pichugina et al. \cite{pichugina2017properties}
+the Northeastern United States.  Pichugina et al. \cite{pichugina2017properties}
 measured the wind profiles and vertical shear profiles in the Gulf of
@@
 showing that the SBL could reach a quasi steady-state. They also
-showed good agreement with the Nieustadt analytical model. In the same
+showed good agreement with the Nieuwstadt analytical model. In the same
 year, Saiki et al. \cite{Saiki2000} simulated an SBL with
@@
 presented the first grid-focused work on LES of the SBL, using grids with deltas
-between 2m and 12.5m, finding significant variation between grid sizes. The inclusion
-of a backscatter model resulted in significant variation at a 6.25m resolution, but
-very little at a 2m resolution. Basu et al. \cite{Basu2005} published a set of
+between 2 m and 12.5 m, finding significant variation between grid sizes. The inclusion
+of a backscatter model resulted in significant variation at a 6.25 m resolution, but
+very little at a 2 m resolution. Basu et al. \cite{Basu2005} published a set of
 turbulence statistics, measurements, and LES simulations in support
-of the viability of Nieustadt's local scaling hypothesis under very stable
+of the viability of Nieuwstadt's local scaling hypothesis under very stable
 conditions. Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range
@@
 stable flow taken from Kosovic and Curry \cite{Kosovic2000}. Eleven codes
-were compared in all, wherein grid deltas of less than 12.5m were found to
+were compared in all, wherein grid deltas of less than 12.5 m were found to
 successfully maintain resolved turbulence, grid deltas less than 3.125m
 showed little statistical change, and results became independent of SGS
-modeling at 1m resolution. In the same year, Kumar et al. \cite{Kumar2006}
+modeling at 1 m resolution. In the same year, Kumar et al. \cite{Kumar2006}
 successfully simulated an entire diurnal cycle with LES using a Lagrangian
@@
 provides a basis for evaluating grid resolution. In all of the reviewed literature, SBL LES
-has been run in the onshore context only, a complete comparison
+has been run in the onshore context only; a complete comparison
 including offshore stable ABL conditions has yet to be completed.
@@
 the codes are reported.  Finally, a series of stable boundary layer
-conditions will be computed using AMR-Wind which match the
+conditions will be computed using AMR-Wind that match the
 measurements of Archer et al. \cite{archer2016predominance}.  The
@@
 \section{Conclusion}
-In this study we have simulated the stable offshore boundary layer
-matching the characteristics of measurements from Nantucket Sound in
-the Northeastern US.  Three cases with wind speeds of 5 m/s, 10 m/s,
-and 15 m/s were selected, and simulations were performed using the
-ExaWind codes to match the TI and stability levels observed at from
-the Cape Wind platform.  When examining the effect of stratification
-using the Obukhov length, differences in the ABL behavior were seen
-between the very stable boundary layer cases (5 m/s and 10 m/s), and
-the stably stratified case (15 m/s).  The very stable cases had
-shorter turbulent structures and less growth in the boundary layer
-compared to the 15 m/s case.  The behavior of the three stable
-boundary layers was also compared to the neutral and unstable cases
-studied in \cite{cheung2020large}.  As expected, the turbulent
-structures in all stable cases were noticeably smaller than in the
-neutral and unstable boundary layers.
+In this study, we have simulated the stable offshore boundary layer matching the
+characteristics of measurements from Nantucket Sound in the Northeastern United
+States. Three cases with wind speeds of 5 m/s, 10 m/s, and 15 m/s were
+selected, and simulations were performed using the ExaWind codes to match the TI
+and stability levels observed at the Cape Wind platform.  When examining
+the effect of stratification using the Obukhov length, differences in the ABL
+behavior were seen between the very stable boundary layer cases (5 m/s and 10
+m/s), and the stably stratified case (15 m/s).  The very stable cases had
+shorter turbulent structures and less growth in the boundary layer compared to
+the 15 m/s case.  The behavior of the three stable boundary layers was also
+compared to the neutral and unstable cases studied in \cite{cheung2020large}.
+As expected, the turbulent structures in all stable cases were noticeably
+smaller than in the neutral and unstable boundary layers.
 
@@
 considered here.  Based on the calculated turbulent integral
-lengthscale, horizontal domain sizes of 750 m $\times$ 750 m were found
+length scale, horizontal domain sizes of 750 m $\times$ 750 m were found
 to be necessary for these simulations.  Various mesh resolutions were
@@
 
-This research was supported by the Wind Energy Technologies Office of
-the US Department of Energy Office of Energy Efficiency and Renewable
-Energy.  Sandia National Laboratories is a multimission laboratory
-managed and operated by National Technology \& Engineering Solutions
-of Sandia, LLC, a wholly owned subsidiary of Honeywell International
-Inc., for the U.S. Department of Energy's National Nuclear Security
-Administration under contract DE-NA0003525. The views expressed in the
-article do not necessarily represent the views of the U.S. Department
-of Energy or the United States Government.
+This research was supported by the Wind Energy Technologies Office of the
+U.S. Department of Energy (DOE) Office of Energy Efficiency and Renewable
+Energy.  Sandia National Laboratories is a multimission laboratory managed and
+operated by National Technology \& Engineering Solutions of Sandia, LLC, a
+wholly owned subsidiary of Honeywell International Inc., for the U.S. Department
+of Energy's National Nuclear Security Administration under contract
+DE-NA0003525. The views expressed in the article do not necessarily represent
+the views of the U.S. Department of Energy or the United States Government.
 
-This work was authored in part by the National Renewable Energy
-Laboratory, operated by Alliance for Sustainable Energy, LLC, for the
-U.S. Department of Energy (DOE) under Contract No. DE-AC36-
-08GO28308. M. Brazell was funded by the Exascale Computing
-Project (17-SC-20-SC), a collaborative effort of two DOE organizations
-(Office of Science and the National Nuclear Security Administration).
+This work was authored in part by the National Renewable Energy Laboratory,
+operated by Alliance for Sustainable Energy, LLC, for the U.S. Department of
+Energy (DOE) under Contract No. DE-AC36- 08GO28308. M. Brazell was funded by the
+Exascale Computing Project (17-SC-20-SC), a collaborative effort of two DOE
+organizations (Office of Science and the National Nuclear Security
+Administration).
 
-A portion of the research was performed using computational
-resources sponsored by the Department of Energy's Office of Energy
-Efficiency and Renewable Energy and located at the National Renewable
-Energy Laboratory.
+A portion of the research was performed using computational resources sponsored
+by the DOE's Office of Energy Efficiency and Renewable Energy and located at the
+National Renewable Energy Laboratory.
 

### 2020-12-06 Paper/methodology.tex
Apply changes suggested by NREL Editorial office

@@
 
-Following the work of Cheung et al \cite{cheung2020large}, we use
+Following the work of Cheung et al.~\cite{cheung2020large}, we use
 measurements of the offshore coastal marine boundary layer, collected
@@
 with temperature and barometric measurements from the years 2003-2011.
-From the observations, Archer et al.\cite{archer2016predominance}
+From the observations, Archer et al.~\cite{archer2016predominance}
 found that the marine boundary layer is predominantly unstable, with
@@
 computational study.  A summary of the conditions for all stability
-classes is given in table \ref{tab:CapeWindMeasurements}. In this work we
+classes is given in Table~\ref{tab:CapeWindMeasurements}. In this work we
 focus on the three stable atmospheric conditions at wind speeds of
@@
 Large Eddy Simulations of the stable atmopsheric conditions described in
-table~\ref{tab:CapeWindMeasurements} are performed using the open-source,
+Table~\ref{tab:CapeWindMeasurements} are performed using the open-source,
 ExaWind simulation environment\footnote{\url{https://github.com/exawind}}.
@@
 \subsubsection{Governing equations}
-Both CFD codes solve the incompressible form of the Navier-Stokes equations with
-appropriate models for turbulence closure. Equation~\ref{eqn:ns-les} shows the
-continuity and momentum equations with all the terms necessary to model the
-atmospheric boundary layer problem. Term $\mathbf{I}$ represents the pressure
-gradient forces as a deviation from hydrostatic and horizontal mean gradients,
-term $\mathbf{II}$ represents the contribution from viscous and sub-filter scale
-stresses, term $\mathbf{III}$ represents the contribution from Coriolis forces
-due to earth's rotation, term $\mathbf{IV}$ represents the effects of buoyancy,
-and term $\mathbf{V}$ represents source terms necessary to drive the flow to a
-desired horizontal mean velocity at prescribed heights.
+Both computational fluid dynamics (CFD) codes solve the incompressible form of
+the Navier-Stokes equations with appropriate models for turbulence
+closure. Equation~\ref{eqn:ns-les} shows the continuity and momentum equations
+with all the terms necessary to model the atmospheric boundary layer
+problem. Term $\mathbf{I}$ represents the pressure gradient forces as a
+deviation from hydrostatic and horizontal mean gradients, term $\mathbf{II}$
+represents the contribution from viscous and sub-filter scale stresses, term
+$\mathbf{III}$ represents the contribution from Coriolis forces due to earth's
+rotation, term $\mathbf{IV}$ represents the effects of buoyancy, and term
+$\mathbf{V}$ represents source terms necessary to drive the flow to a desired
+horizontal mean velocity at prescribed heights.
 
@@
 $q_j$ (Eq.~\ref{eqn:enthalpy-les}) are not equivalent and must be scaled
-appropriately. User can still provide the appropriate initial and boundary
+appropriately. Users can still provide the appropriate initial and boundary
 conditions in terms of potential temperature field. Under these assumptions and
@@
 $\average{\bullet}$ represents the horizontal planar average. The mean
-sub-filter stresses are computed using Monin-Obukhov similarity
+sub-filter stresses are computed using the Monin-Obukhov similarity
 law~\cite{Etling1996}. The formulation for the potential temperature flux could
@@
 surrounding the nodes of the mesh. The governing equations are discretized in
-time using a split-operator approach. Implicit backward difference formula
-(BDF2) timestepping algorithm with an approximate pressure projection
+time using a split-operator approach. An implicit backward difference formula
+(BDF2) time-stepping algorithm with an approximate pressure projection
 scheme~\cite{Moen-Domino:2003} is used to advance the equations in time.
-Multiple Picard-style outer-loop iterations are employed within each timestep
+Multiple Picard-style outer-loop iterations are employed within each time step
 to minimize the errors introduced from split-operator approximations. Nalu-Wind
@@
 equations are solved using GMRES iterative solvers with symmetric Gauss-Seidel
-(SGS) preconditioners. The elliptic pressure-Poisson equation is solved using
+(SGS) preconditioners. The elliptic pressure Poisson equation is solved using
 GMRES solvers with a smoothed-aggregated algebraic multigrid preconditioner. The
@@
 subgrid-scale kinetic energy equation (Eq.~\ref{eqn:ksgs-les}) is used for LES
-turbulence closure. Two Picard iterations were employed within each timestep to
+turbulence closure. Two Picard iterations were employed within each time step to
 minimize splitting errors and recover second-order accuracy in time.
@@
 
-As part of a suite of physics codes within the open-source project called ExaWind,
+As part of a suite of physics codes within the open-source project ExaWind,
 AMR-Wind enables more efficient and scalable simulations of wind power plants.
-This is because it is built on top of the AMReX software framework which contains
-all of the functionality needed to develop massively parallel, block-structured
-adaptive mesh refinement (AMR) applications \cite{AMReX_JOSS}.
-Since AMR-Wind is limited to Cartesian block-structured grids, it is specialized
-to handle ABL physics and wind turbine wakes.
-The block-structured grids enable more efficient algorithms such as
-Multi-Level Multi-Grid (MLMG) \cite{AMReX_JOSS}
-and are well suited for next generation supercomputers that use GPU's.
-In the current work, we focus on applying AMR-Wind to ABL computations
-using statically refined, uniform meshes, and will examine adaptive
-mesh capabilities in future studies.
+This is because it is built on top of the AMReX software framework, which
+contains all of the functionality needed to develop massively parallel,
+block-structured adaptive mesh refinement (AMR) applications \cite{AMReX_JOSS}.
+Because AMR-Wind is limited to Cartesian block-structured grids, it is
+specialized to handle ABL physics and wind turbine wakes.  The block-structured
+grids enable more efficient algorithms such as Multi-Level Multi-Grid (MLMG)
+\cite{AMReX_JOSS} and are well suited for next generation supercomputers that
+use graphical processing units (GPUs).  In the current work, we focus on
+applying AMR-Wind to ABL computations using statically refined, uniform meshes,
+and will examine adaptive mesh capabilities in future studies.
 
 AMR-Wind solves the incompressible Navier-Stokes equations and is generalized to
-handle variable density and viscosity. Additionally scalar transport equations can be
-solved such as potential temperature or turbulence models. The discretization in AMR-Wind
-is based on the approximate projection method used in IAMR \cite{almgren1998conservative}
-and incflo \cite{sverdrup2018highly}. It is a semi-staggered scheme where the velocity and scalar
-variables are located at cell centers and pressure is located at nodes. Pressure is also staggered
-in time so that pressure and the pressure gradient (located at cell centers) are at time $n+1/2$.
-The time discretization is handled with a Crank Nicholson approach where the right hand side
-of the system of equations is evaluated at time $n+1/2$. The advection term is handled explicitly
-using an upwind finite-volume method. There are multiple options
-within AMR-Wind, but in this paper only the high-order Godunov Piecewise Parabolic
-method (PPM) is used \cite{Colella1984}. The advection terms are projected to face
-centers at $n+1/2$ and are corrected using an exact MAC projection \cite{almgren1998conservative}
-which guarantees a divergence free flow. The diffusion terms can be handled explicitly, semi-implicitly,
-or fully implicit and are discretized using a second-order central difference formula.
-For the simulations in this paper, we use a fully implicit scheme as the variable viscosity
-from the eddy viscosity may cause time step restrictions. After the scalar equations
-and the momentum equations are advanced in time, a nodal projection is used to
-approximately correct the velocity field to make it divergence free.  The nodal projection
-is based on a node centered finite element method \cite{almgren1998conservative}.
+handle variable density and viscosity. Additionally, scalar transport equations
+can be solved, such as potential temperature or turbulence models. The
+discretization in AMR-Wind is based on the approximate projection method used in
+IAMR \cite{almgren1998conservative} and incflo \cite{sverdrup2018highly}. It is
+a semi-staggered scheme where the velocity and scalar variables are located at
+cell centers and pressure is located at nodes. Pressure is also staggered in
+time so that pressure and the pressure gradient (located at cell centers) are at
+time $n+1/2$.  The time discretization is handled with a Crank Nicolson
+approach where the right-hand side of the system of equations is evaluated at
+time $n+1/2$. The advection term is handled explicitly using an upwind
+finite-volume method. There are multiple options within AMR-Wind, but in this
+paper only the high-order Godunov Piecewise Parabolic Method (PPM) is used
+\cite{Colella1984}. The advection terms are projected to face centers at $n+1/2$
+and are corrected using an exact MAC projection~\cite{almgren1998conservative},
+which guarantees a divergence free flow. The diffusion terms can be handled
+explicitly, semi-implicitly, or fully implicit and are discretized using a
+second-order central difference formula.  For the simulations in this paper, we
+use a fully implicit scheme, as the variable viscosity from the eddy viscosity
+may cause time step restrictions. After the scalar equations and the momentum
+equations are advanced in time, a nodal projection is used to approximately
+correct the velocity field to make it divergence free.  The nodal projection is
+based on a node centered finite element method \cite{almgren1998conservative}.
 
@@
   Stability & Wind speed & Surface roughness $z_0$ & Surface
-  temperature change & timestep\\
+  temperature change & Time step\\
   \hline
@@
 
-The initial temperature profile in all cases was a constant 300K until
+The initial temperature profile in all cases was a constant 300 K until
 the specified inversion height of 650 m.  The inversion layer thickness
 was 100 m, and above this, the temperature linearly increased until it
-reached 308.75K at the upper boundary.  The initial mean velocity
+reached 308.75 K at the upper boundary.  The initial mean velocity
 profile was uniform throughout the domain with superimposed sinusoidal
@@
 trial-and-error process.  The final surface roughness of $z_0$=0.0005m
-used for the stable offshore conditions (see table \ref{tab:z0tempparam})
+used for the stable offshore conditions (see Table~\ref{tab:z0tempparam})
 matched the roughness used in the neutral 15m/s and unstable 5m/s and
@@
 The values of the prescribed temperature change at the ocean surface
-is also given in table \ref{tab:z0tempparam}.  As the wind
+is also given in Table~\ref{tab:z0tempparam}.  As the wind
 speed increases, a larger temperature decrease was used to maintain
@@
 5,000 seconds.  To maintain a CFL number less than unity during these
-runs, a smaller timestep was used for the higher wind speeds (see
-table \ref{tab:z0tempparam}).
+runs, a smaller time step was used for the higher wind speeds (see
+Table~\ref{tab:z0tempparam}).

### 2020-12-06 Paper/results.tex
Apply changes suggested by NREL Editorial office

@@
 domain size and mesh resolution needed to be determined.
-Under-resolved meshes or domain sizes which are too small may miss the
+Under-resolved meshes or domain sizes that are too small may miss the
 smaller turbulence scales or remove the larger structures required for
@@
 To determine the appropriate mesh size and resolution, a grid study
-was conducted using the stable 5m/s ABL case and the Nalu-Wind code.
+was conducted using the stable 5 m/s ABL case and the Nalu-Wind code.
 A number of cases were set up using the surface roughness and
-prescribed temperature decreases listed in table
+prescribed temperature decreases listed in Table
 \ref{tab:z0tempparam}, but with varying grid resolutions and
@@
   \hline
-  Nalu-Wind coarse  &  10.0 m  & 10.0 m & 2.5 m & 1.5 km $\times$ 1.5km $\times$ 1.0 km  \\
+  Nalu-Wind coarse  &  10.0 m  & 10.0 m & 2.5 m & 1.5 km $\times$ 1.5 km $\times$ 1.0 km  \\
   Nalu-Wind medium  &   5.0 m &  5.0 m  & 2.5 m & 1.5 km $\times$ 1.5 km $\times$ 1.0 km  \\
@@
 \begin{equation}
-  \int_0^\infty S_i(f) \textrm{d}f = \sigma_i^2
+  \int_0^\infty S_i(f) \textrm{d}f = \sigma_i^2,
 \end{equation}
@@
     Calculation of the wind spectra $S_i$ for LES of stable
-    5m/s case with different resolutions.  The gray vertical lines
+    5 m/s case with different resolutions.  The gray vertical lines
     correspond to the maximum resolvable frequency $f_{max}$ according
@@
 limits the highest resolved frequency to half the sampling frequency, or
-
 \begin{equation}
-  f_{Ny} = \frac{1}{2\times \textrm{dt}}
+  f_{Ny} = \frac{1}{2\times \textrm{dt}}.
 \end{equation}
@@
 was sufficient to capture the peak frequency for $S_u$, the fine
-resolution with 2.5m mesh cells was required to capture the spectral
+resolution with 2.5 m mesh cells was required to capture the spectral
 peaks for the lateral and vertical velocities.
@@
   \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
-       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
+       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} },
 \end{equation}
@@
 \begin{equation}
-  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
+  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) },
 \end{equation}
@@
     longitudinal and lateral $\langle R_{11}(\boldsymbol{\xi})
-    \rangle$ coefficients at $z$=20 m for LES of stable 5m/s case with
+    \rangle$ coefficients at $z$=20 m for LES of stable 5 m/s case with
     different resolutions.}
@@
 
-The results shown in figure \ref{fig:GridStudyRij} show that the
+The results shown in Figure  \ref{fig:GridStudyRij} show that the
 finest resolution is required to resolve both the longitudinal and the
@@
 finer in the lateral direction compared to the longitudinal direction.
-While 2.5m resolution is adequate to resolve the longitudinal
+While 2.5 m resolution is adequate to resolve the longitudinal
 turbulent structures, the lateral direction may require even finer
@@
 drawn by examining the turbulent integral length scale $L$.  This
-lengthscale can be calculated from $\langle R_{11}(\boldsymbol{\xi})
+length scale can be calculated from $\langle R_{11}(\boldsymbol{\xi})
 \rangle$ via
 \begin{equation}
-  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
+  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi,
 \end{equation}
-and the results are shown in table \ref{tab:GridStudyLscale}.  With a
+and the results are shown in Table \ref{tab:GridStudyLscale}.  With a
 resolution of 2.5m, the ratio of the longitudinal length scale to the
@@
 structures, domain sizes of approximately 10 times the longitudinal
-lengthscale is recommended.  However, the inclusion of sample probes
+length scale is recommended.  However, the inclusion of sample probes
 with sufficient separation distance to accurately calculate $\langle
 R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
-requirements.  Assuming the longitudinal length scales on the order of
+requirements.  Assuming longitudinal length scales on the order of
 30 m, we estimated a minimum domain size of 750 m $\times$ 750 m in the
@@
 \caption{\label{tab:GridStudyLscale} The calculated turbulent integral
-  lengthscale for each of the grid resolutions} \centering
+  length scale for each of the grid resolutions} \centering
 \begin{tabular}{ccccc}
@@
 
-\subsection{Comparison of AMR-Wind vs Nalu-Wind}
+\subsection{Comparison of AMR-Wind versus Nalu-Wind}
 
@@
 
-Before examining the behavior of the offshore ABL across all wind speeds,
+Before examining the behavior of offshore ABL across all wind speeds,
 we first compare the results for a single case using both LES codes.
-In this section, we consider the stable 5m/s case, calculated in the
+In this section, we consider the stable 5 m/s case, calculated in the
 same manner using both AMR-Wind and Nalu-Wind.  Both LES codes used a
-mesh resolution of 2.5m based on the guidance from section
+mesh resolution of 2.5 m based on the guidance from section
 \ref{sec:gridstudy} and the computational resources available.
 
-After running each case for 15,000 seconds, the boundary layer
+After running each case for 15,000 s, the boundary layer
 statistics and horizontally averaged profiles were averaged for
-another 5,000 seconds.  In table \ref{tab:CompareAMRvsNalu}, some mean
+another 5,000 s.  In Table \ref{tab:CompareAMRvsNalu}, some mean
 statistics are given for both cases, including the friction velocity
@@
 The comparison of the horizontally averaged wind profiles is shown in
-figure \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
+Figure  \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
 z=20 m, the wind speed and wind shear are close to an exact match
 between the two LES codes.  The horizontal wind speeds continue to
-agree well for $z$<100 m, beyond which a relatively constant velocity
+agree well for $z < 100$ m, beyond which a relatively constant velocity
 difference is observed.   For both AMR-Wind and Nalu-Wind, an
@@
 The computed TI and temperature profiles were observed to agree
-remarkably well between the LES codes. As shown in figure
+remarkably well between the LES codes. As shown in Figure
 \ref{fig:CompareAMRvsNaluWind_TTI}, the stable ABL computed using
@@
 wind spectra and turbulent correlation statistics from both AMR-Wind
-and Nalu-Wind for the stable 5m/s case.  A comparison of the computed
+and Nalu-Wind for the stable 5 m/s case.  A comparison of the computed
 wind spectra $S_i(f)$ from both LES codes is shown in figure
@@
 predict relatively similar spectral peaks for the $S_v$ and $S_w$
-spectra.  For the longitudinal spectra $S_u$, however, AMR-wind
+spectra.  For the longitudinal spectra $S_u$, however, AMR-Wind
 predicts a slightly lower the peak amplitude than Nalu-Wind.
@@
 %% A comparison of the averaged $\langle R_{11}(\boldsymbol{\xi})\rangle$
-%% correlation coefficient is shown in figure \ref{fig:CompareAMRvsNaluRij}.
+%% correlation coefficient is shown in Figure~\ref{fig:CompareAMRvsNaluRij}.
 
-%% %%%%%%%%%%% Compare Nalu/AMR lengthscale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% %%%%%%%%%%% Compare Nalu/AMR length scale %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% % Postprocessing/ABLLength/CompareAMRNalu_ABL_Lengthscales.ipynb
@@
 
-For the 5 m/s SBL case AMR-Wind had a median time of 0.266 seconds per time step.
-This means the entire simulation took about 6 hours to simulate 20k seconds
+For the 5 m/s SBL case AMR-Wind had a median time of 0.266 s per time step.
+This means the entire simulation took about 6 hours to simulate 20000 s
 of physical time. For this case a total of $288\times 288 \times 384$ cells were used
@@
 
-In comparison, the same case for Nalu-Wind takes 3.404 seconds per time step which
+In comparison, the same case for Nalu-Wind takes 3.404 s per time step which
 takes a total of 75.64 hours to complete the simulation. This simulation was carried out
@@
 $\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
-longitudinal lengthscale $L$, and stability classification for each of
+longitudinal length scale $L$, and stability classification for each of
 these three cases.  The TI values, calculated at the height $z$=20 m
@@
 \begin{equation}
-  L_{Ob} = -\frac{u_\tau^3 T_0}{\kappa g \langle \overline{w'T'} \rangle}
+  L_{Ob} = -\frac{u_\tau^3 T_0}{\kappa g \langle \overline{w'T'} \rangle},
 \end{equation}
@@
 \cite{archer2016predominance}, and identify boundary layer cases where
-$100 < L_{Ob} < 500$ as ``stable'', and cases where $5 < L_{Ob}<100$
-as ``very stable''.  From the values listed in table
+$100 < L_{Ob} < 500$ as ``stable,'' and cases where $5 < L_{Ob}<100$
+as ``very stable.''  From the values listed in Table
 \ref{tab:CompareAMRallWS}, we find that the lower wind speeds are
-``very stable'', while the highest 15 m/s wind speed is classified as
-``stable''.  This is consistent with the measured Cape Wind
+``very stable,'' while the highest 15 m/s wind speed is classified as
+``stable.''  This is consistent with the measured Cape Wind
 distributions, where very stable conditions are more frequent than
@@
 through snapshots of the flow taken from each of the simulations.  In
-figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
+Figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
 horizontal and vertical velocities for each of the three cases at the
@@
 to the 5 m/s and 15 m/s cases, which is consistent with the nearly
-50\% larger integral lengthscale $L$ given in table
+50\% larger integral length scale $L$ given in Table
 \ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
-are also evident in figure \ref{fig:SnapshotsZ20}.  At higher wind speeds the
+are also evident in Figure  \ref{fig:SnapshotsZ20}.  At higher wind speeds the
 magnitude of the vertical $w'$ fluctuations increase, which plays a
@@
   \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
-    velocity and vertical velocity, taken at t=20,000 seconds of the
+    velocity and vertical velocity, taken at t=20,000 s of the
     simulations at height z=20 m, for the AMR-Wind calculation of the
@@
 This observation can also be seen in images taken along the flow
-direction $225^\circ$, as shown in figure
-\ref{fig:SnapshotsSide}.  At the time t=20,000 seconds, the growth of the
+direction $225^\circ$, as shown in Figure
+\ref{fig:SnapshotsSide}.  At the time t=20,000 s, the growth of the
 of 15 m/s stable boundary layer is considerably larger than the very
@@
   \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
-    velocity, taken at t=20,000 seconds along the wind direction, for
-    the (a) 5m/s, (b) 10 m/s, and (c) 15 m/s AMR-Wind stable
+    velocity, taken at t=20,000 s along the wind direction, for
+    the (a) 5 m/s, (b) 10 m/s, and (c) 15 m/s AMR-Wind stable
     calculations }
@@
 
-Horizontally averaged flow profiles shown in figures
+Horizontally averaged flow profiles shown in Figures
 \ref{fig:CompareAMRallWS} and \ref{fig:CompareAMRallTTI} provide a
@@
 \ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
-discussed above.  Despite all cases reaching a similar TI levels at
+discussed above.  Despite all cases reaching similar TI levels at
 $z$=20 m, the turbulence decays at different rates for each case until
@@
 surface temperature changes is also visible in the horizontally
-averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
+averaged temperature profiles.  Both the 10 m/s and 15 m/s cases impose
 similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
@@
 
-Strong differences based on the atmospheric stratification can also be
+Strong differences based on atmospheric stratification can also be
 seen when we compare the stable ABL cases with the neutral and
@@
 to the findings in \ref{sec:stableABLStats}, the 5 m/s and 10 m/s
-unstable cases were classified as ``very unstable'', while the 15 m/s
+unstable cases were classified as ``very unstable,'' while the 15 m/s
 was identified as ``unstable'' based on the Obukhov length scale.
@@
 The impact of the stability on the turbulent structures can be seen
-through the correlation statistics and calculated lengthscales in
-figure \ref{fig:AllStabilityRij} and
+through the correlation statistics and calculated length scales in
+Figure \ref{fig:AllStabilityRij} and
 \ref{fig:AllStabilityLengthscale}.  The large disparity between the
@@
 R_{11}(\boldsymbol{\xi})\rangle$ coefficients.  The longitudinal
-lengthscales for the unstable ABL cases can also be an order of
+length scales for the unstable ABL cases can also be an order of
 magnitude larger than the stable ABL cases.  The large lateral
-lengthscales for the very unstable ABL cases, compared to the smaller lateral
-lengthscales for the neutral and stable cases, is also worth noting.
+length scales for the very unstable ABL cases, compared to the smaller lateral
+length scales for the neutral and stable cases, is also worth noting.
 For the 5 m/s and 10 m/s very unstable ABL cases, the lateral
 dimensions of the turbulent structures are similar to the longitudinal
-lengthscale.  This is consistent with the large convective structures
+length scale.  This is consistent with the large convective structures
 which develop in those cases.  For the unstable 15 m/s case, the
-lateral lengthscales were closer to neutral and stable cases.
+lateral length scales were closer to neutral and stable cases.
 
@@
   \caption{ \label{fig:AllStabilityLengthscale} Calculation of the
-    averaged longitudinal and lateral lengthscale at $z$=20 m for all
+    averaged longitudinal and lateral length scale at $z$=20 m for all
     ABL stability cases.}
@@
 %% \caption{\label{tab:StabilityStudyLscale} The calculated turbulent
-%%   integral lengthscale for each of atmospheric stabilities} \centering
+%%   integral length scale for each of atmospheric stabilities} \centering
 %% \begin{tabular}{ccccc}

### 2020-12-07 Paper/results.tex
updated vertical velocity plots

@@
     \node[align=left] at (1in, 4.50in){(a) horizontal vel., stable 5 m/s};
-    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
-         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
+    \node[anchor=south west, inner sep=0](image) at (3in,4.45in)
+         {\includegraphics[width=3.50in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
     \node[align=left] at (4.25in, 4.50in){(b) vertical vel., stable 5 m/s};
@@
     \node[align=left] at (1in, 2.25in){(c) horizontal vel., stable 10 m/s};
-    \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
-         {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
+    \node[anchor=south west, inner sep=0](image) at (3in,2.20in)
+         {\includegraphics[width=3.50in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
     \node[align=left] at (4.25in, 2.25in){(d) vertical vel., stable 10 m/s};
@@
     \node[align=left] at (1in, 0in){(e) horizontal vel., stable 15 m/s};
-    \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
-         {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
+    \node[anchor=south west, inner sep=0](image) at (3in,-0.05in)
+         {\includegraphics[width=3.50in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
     \node[align=left] at (4.25in, 0in){(f) vertical vel., stable 15 m/s};

### 2020-12-07 Paper/methodology.tex
Adding first part of Mike Sprague's comments

@@
   \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
-  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u'} + \overline{v'v'} + \overline{w'w'}
+  \frac{\sqrt{\frac{1}{3}\left( \overline{u'_1 u'_1} + \overline{u'_2 u'_2} + \overline{u'_3 u'_3}
       \right)}}{\overline{U}_{horiz}}
@@
 
-\subsection{Computational methodology}
+\subsection{Computational methodology and LES formulation}
 %Provide a general description of the LES codes that we use.
@@
 
-\subsection{LES formulation}
+% \subsection{LES formulation}
 
@@
   \begin{cases}
-    \Delta = \sqrt[3]{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 \\
-    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 \\
+    \Delta = \sqrt[3]{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 , \\
+    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 .\\
   \end{cases}
@@
  (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{V_1 \average{\widetilde{u}_1} + \average{V_1} (\widetilde{u}_1 - \average{\widetilde{u}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
- (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{V_1 \average{\widetilde{v}_1} + \average{V_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } \\
+ (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{V_1 \average{\widetilde{v}_1} + \average{V_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
   (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{V_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{V_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{V_1} ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) },
@@
 level, $V_1$ is the resolved wind speed at the first grid level and
-$\average{\bullet}$ represents the horizontal planar average. The mean
+$\average{\bullet}$ represents the horizontal plane average at that height. The mean
 sub-filter stresses are computed using the Monin-Obukhov similarity
@@
 turbulence closure. Two Picard iterations were employed within each time step to
-minimize splitting errors and recover second-order accuracy in time.
+reduce splitting errors and improving time accuracy.
 
@@
 
-As part of a suite of physics codes within the open-source project ExaWind,
+As part of a suite of physics codes within the open-source ExaWind simulation environment,
 AMR-Wind enables more efficient and scalable simulations of wind power plants.
@@
 and are corrected using an exact MAC projection~\cite{almgren1998conservative},
-which guarantees a divergence free flow. The diffusion terms can be handled
-explicitly, semi-implicitly, or fully implicit and are discretized using a
+which guarantees a divergence-free flow. The diffusion terms can be handled
+explicitly, semi-implicitly, or implicitly and are spatially discretized using a
 second-order central difference formula.  For the simulations in this paper, we
@@
 to capture the smaller turbulent scales, and a uniform cell size of
-2.5m was adopted for the offshore LES computations across both codes.
+2.5 m was adopted for the offshore LES computations across both codes.
 
@@
 \subsubsection{Determination of surface roughness and prescribed temperature }
-To match the measured TI conditions given in table
+To match the measured TI conditions given in Table
 \ref{tab:CapeWindMeasurements}, the surface roughness and prescribed
 surface temperature change were adjusted through an initial
-trial-and-error process.  The final surface roughness of $z_0$=0.0005m
+trial-and-error process.  The final surface roughness of $z_0$=0.0005 m
 used for the stable offshore conditions (see Table~\ref{tab:z0tempparam})
-matched the roughness used in the neutral 15m/s and unstable 5m/s and
+matched the roughness used in the neutral 15 m/s and unstable 5 m/s and
 10 m/s cases from the previous study \cite{cheung2020large}.  This
@@
 the North Sea \cite{taylor2001dependence}, which found values of $z_0$
-ranging from $5 \times 10^{-5}$m to $5\times 10^{-3}$m.
+ranging from $5 \times 10^{-5}$m to $5\times 10^{-3}$ m.
 

### 2020-12-07 Paper/main.tex

@@
   turbulent scales for the stable offshore boundary layers.  Finally, we compare
-  solutions computed using both Nalu-Wind and AMR-Wind solvers, and report on
-  their relative accuracy and performance in this study.
+  solutions computed using both Nalu-Wind and AMR-Wind solvers, and
+  compare their predicted solutions and performance in this study.
 
@@
 measured the wind profiles and vertical shear profiles in the Gulf of
-Maine using a ship-borne lidar approach.  Analysis of measured data
+Maine using a ship-borne LIDAR approach.  Analysis of measured data
 sets from Nantucket Sound by Archer et
@@
 to the SGS model, resulting in better agreement with surface layer observations.
-Andren \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and
+Andren \cite{Andren1995} simulated two SBL types, one with a neutral layer aloft, and
 one capped by an inversion, comparing two SGS models. He found significant improvements
@@
 year, Saiki et al. \cite{Saiki2000} simulated an SBL with
-a strong capping inversion at z=500 m, producing reasonable surface layer profiles and
+a strong capping inversion at $z$=500 m, producing reasonable surface layer profiles and
 identifying a need for SBL specific SGS models. Beare and MacVean \cite{Beare2004}
@@
 were compared in all, wherein grid deltas of less than 12.5 m were found to
-successfully maintain resolved turbulence, grid deltas less than 3.125m
+successfully maintain resolved turbulence, grid deltas less than 3.125 m
 showed little statistical change, and results became independent of SGS
@@
 \subsection{Objectives}
-In the current study on stable marine
-boundary layers, we aim to build on the previous work in the
-literature and complete several objectives.  First, we examine the
-domain and mesh requirements necessary to capture the turbulent scales
-for the stable offshore boundary layers.  Secondly, two LES solvers
-within the ExaWind project will be compared in this study: the
-unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
-structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
-used to calculate the same SBL, and the relative differences between
-the codes are reported.  Finally, a series of stable boundary layer
-conditions will be computed using AMR-Wind that match the
-measurements of Archer et al. \cite{archer2016predominance}.  The
-behavior of the stable boundary layers, including mean flow quantities
-and turbulent statistics, are examined and compared to the neutral and
-unstable cases computed in \cite{cheung2020large}.
+In the current study on stable marine boundary layers, we aim to build
+on the previous work in the literature and complete several
+objectives.  First, we examine the domain and mesh requirements
+necessary to capture the turbulent scales for the stable offshore
+boundary layers.  Secondly, two incompressible-flow LES solvers within
+the ExaWind simulation suite will be compared in this study: The
+unstructured-grid solver Nalu-Wind and the structured, adaptive mesh
+refinement (AMR) solver AMR-Wind.  Both codes are used to calculate
+the same SBL, and the relative differences between the codes are
+reported.  Finally, a series of stable boundary layer conditions will
+be computed using AMR-Wind that match the measurements of Archer et
+al. \cite{archer2016predominance}.  The behavior of the stable
+boundary layers, including mean flow quantities and turbulent
+statistics, are examined and compared to the neutral and unstable
+cases computed in \cite{cheung2020large}.
 

### 2020-12-07 Paper/results.tex
Minor change to sentence in results.tex

@@
 and the results are shown in Table \ref{tab:GridStudyLscale}.  With a
-resolution of 2.5m, the ratio of the longitudinal length scale to the
+resolution of 2.5 m, the ratio of the longitudinal length scale to the
 grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
@@
 The most significant difference between the two solvers is that AMR-Wind uses structured grids
-whereas Nalu-Wind uses unstructured grids. The differences in performance can be attributed with the
+whereas Nalu-Wind uses unstructured grids. The differences in performance could be attributed with the
 computational overhead of storing and manipulating unstructured data.

### 2020-12-08 Paper/results.tex
More changes to results.tex

@@
 The comparison of the wind spectra and maximum resolvable frequency
-$f_{max}$ for the different mesh resolutions is shown in figure
+$f_{max}$ for the different mesh resolutions is shown in Figure
 \ref{fig:GridStudySpectra}.  Here spectra is shown at the $z$=20 m
@@
 and Nalu-Wind for the stable 5 m/s case.  A comparison of the computed
-wind spectra $S_i(f)$ from both LES codes is shown in figure
+wind spectra $S_i(f)$ from both LES codes is shown in Figure
 \ref{fig:CompareAMRvsNaluSpectra}.  At low frequencies, both AMR-Wind
@@
 stable conditions at lower wind speeds, and gradually disappear beyond
-13 m/s (c.f. figure 5b in \cite{archer2016predominance}).
+13 m/s (c.f. Figure 5b in \cite{archer2016predominance}).
 
@@
   \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
-    velocity and vertical velocity, taken at t=20,000 s of the
+    velocity and vertical velocity, taken at $t$=20,000 s of the
     simulations at height z=20 m, for the AMR-Wind calculation of the
@@
 direction $225^\circ$, as shown in Figure
-\ref{fig:SnapshotsSide}.  At the time t=20,000 s, the growth of the
+\ref{fig:SnapshotsSide}.  At the time $t$=20,000 s, the growth of the
 of 15 m/s stable boundary layer is considerably larger than the very
@@
   \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
-    velocity, taken at t=20,000 s along the wind direction, for
+    velocity, taken at $t$=20,000 s along the wind direction, for
     the (a) 5 m/s, (b) 10 m/s, and (c) 15 m/s AMR-Wind stable
@@
 boundary layer up to the inversion height, while the very stable 5 m/s
-and 10 m/s cases showed minimal shear at higher elevations (figure \ref{fig:CompareAMRallWS}).  The
+and 10 m/s cases showed minimal shear at higher elevations (Figure \ref{fig:CompareAMRallWS}).  The
 change in wind direction is also indicative of the boundary layer
@@
 
-The behavior of the TI and temperature profiles in figure
+The behavior of the TI and temperature profiles in Figure
 \ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles

### 2020-12-08 Paper/methodology.tex
Small changes to implicit viscous description

@@
 second-order central difference formula.  For the simulations in this paper, we
-use a fully implicit scheme, as the variable viscosity from the eddy viscosity
+use an implicit scheme for the viscous terms, as the variable viscosity from the eddy viscosity
 may cause time step restrictions. After the scalar equations and the momentum

### 2020-12-08 Paper/results.tex
modified performance section in response to Mike S. comments

@@
 
-For the 5 m/s SBL case AMR-Wind had a median time of 0.266 s per time step.
+For the 5 m/s SBL case AMR-Wind had a median time of 0.27 s per time step.
 This means the entire simulation took about 6 hours to simulate 20000 s
@@
 The time per degree of freedom for AMR-Wind is
-\[\frac{n_r t_{ts} }{n_{dofs}} = 8.118\times10^{-6} [s]\]
+\[\frac{n_r t_{ts} }{n_{dofs}} = 8.2\times10^{-6} [s]\]
 where $n_r$ is the number of MPI ranks, $t_{ts}$ is time per time step, and $n_{dofs}$ is
@@
 
-In comparison, the same case for Nalu-Wind takes 3.404 s per time step which
+In comparison, the same case for Nalu-Wind takes 3.4 s per time step which
 takes a total of 75.64 hours to complete the simulation. This simulation was carried out
 on 1224 MPI ranks for a grid that contains $300\times 300 \times 400$ cells. The equivalent
-time per degree of freedom for Nalu-Wind is $1.147 \times 10^{-4}$ s, where degrees of freedom
-are the number of nodes in the mesh.
+time per degree of freedom for Nalu-Wind is $1.1 \times 10^{-4}$ s, where degrees of freedom
+are the number of nodes in the mesh. For this case AMR-Wind is more than an order of magnitude
+faster per degree of freedom than Nalu-Wind. This significant speed difference is due to the use
+of structured grids in AMR-Wind compared with unstructured grids in Nalu-Wind. There are many 
+benefits to using structured grids and for AMR-Wind this speed advantage is mostly attributed
+ to the MLMG linear solver in the AMReX library \cite{AMReX_JOSS}. This is because for each 
+ time step the computational work is dominated by solving two Poisson equations (MAC projection and nodal projection).
 
-For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work.
-A time step within AMR-Wind requires two Poisson solves (MAC and nodal projection),
-a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves
-(potential temperature equation and subgrid-scale kinetic energy equation).
-Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
-step, in this work we use two Picard iterations for every time step.
-Each Picard iteration requires a Poisson solve and five Helmholtz solves
-(three momentum equations, an enthalpy equation, and the subgrid-scale kinetic energy equation).
-It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
-implementation, and additional study is required to understand the performance comparisons.
-The most significant difference between the two solvers is that AMR-Wind uses structured grids
-whereas Nalu-Wind uses unstructured grids. The differences in performance could be attributed with the
-computational overhead of storing and manipulating unstructured data.
+%For both AMR-Wind and Nalu-Wind each time step is dominated by the linear solver work.
+%A time step within AMR-Wind requires two Poisson solves (MAC and nodal projection),
+%a tensor Helmholtz solve for Momentum equations, and two scalar Helmholtz solves
+%(potential temperature equation and subgrid-scale kinetic energy equation).
+%Nalu-Wind is a fully implicit scheme and requires a non-linear Picard iteration for each time
+%step, in this work we use two Picard iterations for every time step.
+%Each Picard iteration requires a Poisson solve and five Helmholtz solves
+%(three momentum equations, an enthalpy equation, and the subgrid-scale kinetic energy equation).
+%It is difficult to compare AMR-Wind and Nalu-Wind due to the differences in discretization and numerical
+%implementation, and additional study is required to understand the performance comparisons.
+%The most significant difference between the two solvers is that AMR-Wind uses structured grids
+%whereas Nalu-Wind uses unstructured grids. The differences in performance could be attributed with the
+%computational overhead of storing and manipulating unstructured data.
 

### 2020-12-08 Paper/main.tex
Added more nomenclature

@@
 $\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
+$\epsilon_{ijk}$ & Levi-Civita symbol\\
 $f$       & Frequency \\
@@
 $n_r$     & Number MPI ranks \\
+$\phi_h$  & Potential temperature gradient \\
+$q_j$     & Energy flux vector\\
 $\rho$    & Density \\
 $\rho_\circ$ & Reference density  \\
-$\phi_h$  & Potential temperature gradient \\
 $Pr_t$    & Turbulent Prandtl number \\
@@
 SBL       & Stable Boundary Layer \\
-$\theta$  & Potential temperature \\
+$S^u_i$    & ABL forcing source term \\
 $S_i$     & Wind spectra \\
@@
 $\tau_{ij}$ & Stress tensor \\
+$\theta$  & Potential temperature \\
 $TI$      & Turbulence intensity \\
@@
 $\overline{U}_{horiz}$ & Time averaged horizontal velocity \\
+$u_i$     & Wind velocity in the $i$ direction  \\
 $u_\tau$   & Friction velocity    \\
-$V_1$     & Resolved wind speed at first grid level
+$V_1$     & Resolved wind speed at first grid level \\
+$\Omega_i$ & Earth angular velocity vector
 \end{longtable*}}

### 2020-12-08 Paper/methodology.tex
Added more nomenclature

@@
   \frac{\sqrt{\frac{1}{3}\left( \overline{u'_1 u'_1} + \overline{u'_2 u'_2} + \overline{u'_3 u'_3}
-      \right)}}{\overline{U}_{horiz}}
+      \right)}}{\overline{U}_{horiz}},
 \end{equation}
-The averaged wind speeds were enforced at the measurement height of
-20 m, and the applied wind directions were consistent with the
-predominant stable direction of 225 degrees southwest.
+where $u'_i$ is the fluctuating wind velocity in the $i$
+direction. The averaged wind speeds were enforced at the measurement
+height of 20 m, and the applied wind directions were consistent with
+the predominant stable direction of 225 degrees southwest.
 

### 2020-12-08 Paper/results.tex
another sig fig edit
Added more nomenclature

@@
 In comparison, the same case for Nalu-Wind takes 3.4 s per time step which
-takes a total of 75.64 hours to complete the simulation. This simulation was carried out
+takes about 75 hours to complete the simulation. This simulation was carried out
 on 1224 MPI ranks for a grid that contains $300\times 300 \times 400$ cells. The equivalent
@@
 From AMR-Wind LES calculations, a number of quantities can be computed
-to compare with the measured targets from Archer et al
+to compare with the measured targets from Archer et al. 
 \cite{archer2016predominance}.  In

### 2020-12-08 Paper/results.tex
More fixes from Mike Sprague

@@
 simulations for the grid study also used a vertical resolution of
-dz=2.5 m and the same vertical extent of 1 km.
+$\Delta_z$=2.5 m and the same vertical extent of 1 km.
 
@@
 statistics are given for both cases, including the friction velocity
-$u_\tau$, the turbulence intensity TI at z=20 m, and local shear
-exponent $\alpha$ at z=20 m, defined as
+$u_\tau$, the turbulence intensity TI at $z$=20 m, and local shear
+exponent $\alpha$ at $z$=20 m, defined as
 $$ \alpha = \frac{z}{U_{horiz}} \frac{d U_{horiz}}{dz}.
@@
 Figure  \ref{fig:CompareAMRvsNaluWind_WSDir}.  At the forcing height
-z=20 m, the wind speed and wind shear are close to an exact match
+$z$=20 m, the wind speed and wind shear are close to an exact match
 between the two LES codes.  The horizontal wind speeds continue to
@@
 inversion layer height.
+The level of agreement between AMR-Wind and Nalu-Wind at the higher
+elevations is comparable to the inter-comparison of LES simulations
+Beare et al.~\cite{Beare2006}, and may be improved through finer scale
+simulations which fully resolve the lateral turbulent lengthscales.
 
@@
     profiles for the stable 5 m/s boundary layer. The dashed
-    horizontal line corresponds to the measurement height z=20 m. }
+    horizontal line corresponds to the measurement height $z$=20 m. }
 \end{figure}
@@
     the stable 5 m/s boundary layer. The dashed horizontal line
-    corresponds to the measurement height z=20 m.}
+    corresponds to the measurement height $z$=20 m.}
 \end{figure}
@@
   \caption{\label{fig:CompareAMRvsNaluSpectra} Comparison of AMR-Wind
-    and Nalu-Wind wind spectra at z=20 m for the stable 5 m/s boundary
+    and Nalu-Wind wind spectra at $z$=20 m for the stable 5 m/s boundary
     layer. }
@@
 horizontal and vertical velocities for each of the three cases at the
-z=20 m measurement height are shown.  The largest difference can be
+$z$=20 m measurement height are shown.  The largest difference can be
 seen in the size of the flow structures between the very unstable and
@@
     velocity and vertical velocity, taken at $t$=20,000 s of the
-    simulations at height z=20 m, for the AMR-Wind calculation of the
+    simulations at height $z$=20 m, for the AMR-Wind calculation of the
     stable 5 m/s, 10 m/s, and 15 m/s ABL. }
@@
     m/s, and 15 m/s boundary layers. The dashed horizontal line
-    corresponds to the measurement height z=20 m.}
+    corresponds to the measurement height $z$=20 m.}
 \end{figure}
@@
     and 15 m/s boundary layers. The dashed horizontal line corresponds
-    to the measurement height z=20 m.}
+    to the measurement height $z$=20 m.}
 \end{figure}

### 2020-12-08 Paper/methodology.tex
More fixes from Mike Sprague
Modify equations section based on comments from Sprague

@@
 with all the terms necessary to model the atmospheric boundary layer
-problem. Term $\mathbf{I}$ represents the pressure gradient forces as a
+problem. LES filtered variables are denoted using the operation ${\left(\bullet \right)}$.
+Term $\mathbf{I}$ represents the pressure gradient forces as a
 deviation from hydrostatic and horizontal mean gradients, term $\mathbf{II}$
@@
 \begin{align}
-  \frac{\partial \bar{\rho}} {\partial t} + \frac{\partial \bar{\rho} \widetilde{u_j}}{\partial x_j} & = 0, \nonumber\\
-  \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{u}_i\right) +
-  \frac{\partial}{\partial x_j} \left( \bar{\rho}\, \widetilde{u}_i \widetilde{u}_j \right) &=
+  \frac{\partial {u_j}}{\partial x_j} & = 0 \nonumber\\
+  \frac{\partial}{\partial t} \left(\rho\, {u}_i\right) +
+  \frac{\partial}{\partial x_j} \left( \rho\, {u}_i {u}_j \right) &=
   - \underbrace{\frac{\partial p'}{\partial x_j} \delta_{ij}}_\mathbf{I}
   - \underbrace{\frac{\partial \tau_{ij}}{\partial x_j}}_\mathbf{II}
-  - \underbrace{2\bar{\rho}\,\epsilon_{ijk}\,\Omega_j\widetilde{u_k}}_\mathbf{III}
+  - \underbrace{2\rho\,\epsilon_{ijk}\,\Omega_j{u_k}}_\mathbf{III}
   + \underbrace{\left(\rho - \rho_\circ \right) g_i}_\mathbf{IV}
@@
 \end{align}
-
 For the simulations presented in this paper, the buoyancy term ($\mathbf{IV}$)
@@
 This leads to a forcing term that depends on potential temperature ($\theta$),
-the reference density $\rho_\circ = \bar{\rho}$, and thermal expansion
+the reference density $\rho_\circ = \rho$, and thermal expansion
 coefficient $\beta \approx 1 / \theta_\circ$ as
@@
 \begin{align}
-  \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{\theta}\right) +
-  \frac{\partial}{\partial x_j} \left(\bar{\rho}\, \widetilde{u}_j \widetilde{\theta} \right) = - \frac{\partial}{\partial x_j} \hat{q}_j \label{eqn:pot-temp-les}
+  \frac{\partial}{\partial t} \left(\rho\, {\theta}\right) +
+  \frac{\partial}{\partial x_j} \left(\rho\, {u}_j {\theta} \right) = - \frac{\partial}{\partial x_j} \hat{q}_j \label{eqn:pot-temp-les}
 \end{align}
@@
 \end{align}
-Furthermore, ignoring the pressure and viscous work terms in
-Eq.~\ref{eqn:pot-temp-les}, for incompressible flows, it can be shown that
-solving the enthalpy equation is equivalent to solving the potential temperature
-equation. The enthalpy equation solved in Nalu-Wind for wind energy problems is
-shown below
+Furthermore, ignoring the pressure and viscous work terms, for incompressible
+flows, it can be shown that solving the enthalpy equation is equivalent to
+solving the potential temperature equation. The enthalpy equation solved in
+Nalu-Wind for wind energy problems is shown below
 \begin{align}
-  \frac{\partial}{\partial t} \left(\bar{\rho}\, \widetilde{h}\right) +
-  \frac{\partial}{\partial x_j} \left(\bar{\rho}\, \widetilde{u}_j \widetilde{h} \right) = - \frac{\partial}{\partial x_j} q_j . \label{eqn:enthalpy-les}
+  \frac{\partial}{\partial t} \left(\rho\, {h}\right) +
+  \frac{\partial}{\partial x_j} \left(\rho\, {u}_j {h} \right) = - \frac{\partial}{\partial x_j} q_j . \label{eqn:enthalpy-les}
 \end{align}
@@
 \begin{align}
-  \frac{\partial}{\partial t}\left(\bar{\rho} k \right) + \frac{\partial}{\partial x_j} \bar{\rho} k \widetilde{u_j} &= \frac{\partial}{\partial x_j} \left (2 \nu_t \frac{\partial k}{\partial x_j} \right) - 2 \nu_t \widetilde{S_{ij}} \widetilde{S_{ij}} + \frac{g}{\theta_\circ} \tau_{\theta_i} - C_{\epsilon} \frac{k^{3/2}}{l} \label{eqn:ksgs-les}
+  \frac{\partial}{\partial t}\left(\rho k \right) + \frac{\partial}{\partial x_j} \rho k {u_j} &= \frac{\partial}{\partial x_j} \left (2 \nu_t \frac{\partial k}{\partial x_j} \right) - 2 \nu_t {S_{ij}} {S_{ij}} + \frac{g}{\theta_\circ} \tau_{\theta_i} - C_{\epsilon} \frac{k^{3/2}}{l} \label{eqn:ksgs-les}
 \end{align}
 where
-\begin{align}
+\begin{align*}
   C_\epsilon &= 0.93 & \nu_t &= C_\epsilon l \sqrt{k} \\
-  \tau_{\theta i} &= - 2\ \frac{\nu_t}{\mathrm{Pr}_t}\ \frac{\partial \widetilde{\theta}}{\partial x_i} & \mathrm{Pr}_t &= \left( 1 + \frac{2l}{\Delta} \right)^{-1} \\
-\end{align}
+  \tau_{\theta i} &= - 2\ \frac{\nu_t}{\mathrm{Pr}_t}\ \frac{\partial {\theta}}{\partial x_i} & \mathrm{Pr}_t &= \left( 1 + \frac{2l}{\Delta} \right)^{-1}
+\end{align*}
 The choice of the length scale ($l$) depends on whether the stratification is positive
@@
   \begin{cases}
-    \Delta = \sqrt[3]{\Delta_x \Delta_y \Delta_z}, & \frac{\partial \widetilde{\theta}}{\partial z} < 0 , \\
-    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial \widetilde{\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial \widetilde{\theta}}{\partial z} > 0 .\\
+    \Delta = \sqrt[3]{\Delta_x \Delta_y \Delta_z}, & \frac{\partial {\theta}}{\partial z} < 0 , \\
+    0.76\, \sqrt{k}\, \frac{g}{\theta_\circ}\, \left( \frac{\partial {\theta}}{\partial z}\right)^{-1/2}, &  \frac{\partial {\theta}}{\partial z} > 0 .\\
   \end{cases}
@@
 \begin{align}
- (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{V_1 \average{\widetilde{u}_1} + \average{V_1} (\widetilde{u}_1 - \average{\widetilde{u}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
- (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{V_1 \average{\widetilde{v}_1} + \average{V_1} (\widetilde{v}_1 - \average{\widetilde{v}_1} ) }{ \average{V_1} \sqrt{\average{\widetilde{u}_1}^2 + \average{\widetilde{v}_1}^2 } } , \\
-  (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{V_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{V_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{V_1} ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) },
+ (\tau_{xz})_0 &= \average{\tau_{xz}}_0 \frac{V_1 \average{{u}_1} + \average{V_1} ({u}_1 - \average{{u}_1} ) }{ \average{V_1} \sqrt{\average{{u}_1}^2 + \average{{v}_1}^2 } } , \\
+ (\tau_{yz})_0 &= \average{\tau_{yz}}_0 \frac{V_1 \average{{v}_1} + \average{V_1} ({v}_1 - \average{{v}_1} ) }{ \average{V_1} \sqrt{\average{{u}_1}^2 + \average{{v}_1}^2 } } , \\
+  (\tau_{\theta z})_0 &= \average{\tau_{\theta z}}_0 \frac{V_1 ( \average{{\theta}_1} - \theta_{\circ} ) + \average{V_1} ({\theta}_1 - \average{{\theta}_1} ) }{ \average{V_1} ( \average{{\theta}_1} - \theta_{\circ} ) },
 \end{align}
@@
 potentially experience a singularity when the mean resolved potential
-temperature at the first grid level $\average{\widetilde{\theta}_1}$ crosses the
+temperature at the first grid level $\average{{\theta}_1}$ crosses the
 reference temperature $\theta_{\circ}$. Hence the model for the sub-filter
@@
 \begin{equation}
-(\tau_{\theta z})_0 = \left ( \frac{u_{\tau} \kappa}{ \phi_h} \right ) \frac{V_1 ( \average{\widetilde{\theta}_1} - \theta_{\circ} ) + \average{V_1} (\widetilde{\theta}_1 - \average{\widetilde{\theta}_1} ) }{ \average{V_1} },
+(\tau_{\theta z})_0 = \left ( \frac{u_{\tau} \kappa}{ \phi_h} \right ) \frac{V_1 ( \average{{\theta}_1} - \theta_{\circ} ) + \average{V_1} ({\theta}_1 - \average{{\theta}_1} ) }{ \average{V_1} },
 \end{equation}

### 2020-12-08 Paper/main.tex
More nomenclature

--- 2020-12-07 Paper/main.tex
@@
 $\tau_{ij}$ & Stress tensor \\
+$\theta$  & Potential temperature \\
+$T$       & Absolute temperature \\
 $TI$      & Turbulence intensity \\

### 2020-12-08 Paper/main.tex
Added comments/caveats about mesh anisoptropy

@@
 In addition to these simulations, we also examined the domain and mesh
-requirements necessary for the stable offshore boundary layers
-considered here.  Based on the calculated turbulent integral
-length scale, horizontal domain sizes of 750 m $\times$ 750 m were found
-to be necessary for these simulations.  Various mesh resolutions were
-also considered for the stable runs, and it was determined that the
-finest resolution of $\Delta_x$=2.5 m was able to resolve the longitudinal
-length scales and highest temporal frequencies, but inadequate for
-resolving the turbulence in the lateral direction.  Further study is
-warranted to comprehensively determine the impact of stable
-stratification on the required mesh resolution.
+requirements necessary to capture important physical features of the
+stable offshore boundary layers.  Based on the calculated turbulent
+integral length scale, horizontal domain sizes of 750 m $\times$ 750 m
+were found to be necessary for these simulations.  Various horizontal
+mesh resolutions were also considered for the stable runs, and it was
+determined that the finest resolution of $\Delta_x$=2.5 m was able to
+resolve the longitudinal length scales and highest temporal
+frequencies, but inadequate for resolving the turbulence in the
+lateral direction.  However, the possible effects of mesh anisotropy
+on the one equation turbulence model and the wall function treatment
+are not included in this work, and could be important for future
+simulations.  We believe that further study is warranted to
+comprehensively determine the impact of stable stratification on the
+required mesh resolution.
 

### 2020-12-09 Paper/methodology.tex

@@
 the North Sea \cite{taylor2001dependence}, which found values of $z_0$
-ranging from $5 \times 10^{-5}$m to $5\times 10^{-3}$ m.
+ranging from $5 \times 10^{-5}$ m to $5\times 10^{-3}$ m.
 

### 2020-12-09 Paper/results.tex

@@
 
-\subsection{\label{sec:gridstudy}Domain and grid resolution study}
+\subsection{\label{sec:gridstudy}Domain and mesh resolution study}
 
@@
 $\Delta_z$=2.5 m and the same vertical extent of 1 km.
+
+Note that in this paper, we focus our attention on the horizontal
+resolution required to resolve key physical features in the SBL, and
+some additional impacts deserve additional study.  For instance, the
+impact of non-isotropic meshes with the k-sgs turbulence model and
+wall function treatment is not addressed here and worthy of additional
+attention.
 
